### 2025-02-15 ca.stereo.qmd
make it so

---
title: "CA of Music Genre Stereotypes"
author: "Omar Lizardo"
date: "`r Sys.Date()`"
execute: 
  eval: true
  echo: true
  output: true
  warning: false
  message: false
---

```{r setup, include=FALSE}
   library(conflicted)
   library(haven)
   library(here)
   library(dplyr)
```

```{r import data and select genre stereotype variables}
   #importing data
   dat <- read_dta("C:/Users/Omar Lizardo/Google Drive/MISC DATA SOURCES/SSI-2012/SSI2012.dta")
   #replacing ids with character names
   dat <- bind_cols(tibble(id_char = paste("id", sapply(dat[, 1], as.character), sep = "_")), dat) %>% 
   select(id_char, classicalfemale:hvymtluc, -ends_with("none")) %>%  #selecting relevant columns
   na.omit() #removing missing values
   head(dat)
```

```{r}
   make.mat <- function(x) {
      matrix(as.numeric(x), 20, 15, byrow = TRUE)
   }
   r.proj <- function(x) {
      x %*% t(x)
   }
   c.proj <- function(x) {
      t(x) %*% x
   }
   ind.list <- split(dat[, 2:301], seq(nrow(dat)))
   ind.mat <- lapply(ind.list, make.mat)
   ind.row <- lapply(ind.mat, r.proj)
   ind.col <- lapply(ind.mat, c.proj)
```

### 2025-02-15 create-match.qmd
make it so

---
title: "Jilbert's Distinction Centrality"
author: "Omar Lizardo"
date: "`r Sys.Date()`"
execute: 
  eval: true
  echo: true
  output: true
  warning: false
  message: false
---

```{r setup, include=FALSE}
   library(conflicted)
   library(haven)
   library(here)
   library(dplyr)
```
```{r import data and select genre stereotype variables}
   #importing data
   dat <- read_dta("C:/Users/Omar Lizardo/Google Drive/MISC DATA SOURCES/SSI-2012/SSI2012.dta")
   #replacing ids with character names
   dat <- bind_cols(tibble(id_char = paste("id", sapply(dat[, 1], as.character), sep = "_")), dat) %>% 
   select(id_char, classicalfemale:hvymtluc, -ends_with("none")) %>%  #selecting relevant columns
   na.omit() #removing missing values
   head(dat)
```

```{r creating match matrix}
   n <- nrow(dat)
   match <- matrix(0, n, n)
   for (i in 1:n) {
      for (j in 1:n) {
         if (i < j) {
            match[i, j] <- 300 - (sum(abs(dat[i, 2:301] - dat[j, 2:301])))
            print(i)
            print(j)
         }
      }
   }
```

```{r}
   match.f <- match
   match.f[lower.tri(match.f)] <- t(match)[lower.tri(match)]
   match.s <- (2*(match.f/300) - 1)
   save(match.f, match.s, file = "match.rda")
```

### 2025-05-03 ca.stereo.qmd
a buncha stuff

@@
    library(conflicted)
+   library(dplyr)
+   library(FactoMineR)
+   library(ggplot2)
+   library(ggrepel)
+   library(ggridges)
    library(haven)
    library(here)
-   library(dplyr)
+   library(paletteer)
+   cols <- paletteer_dynamic("cartography::multi.pal", 20)
+   conflicts_prefer(dplyr::filter)
 ```
@@
 
-```{r}
-   make.mat <- function(x) {
-      matrix(as.numeric(x), 20, 15, byrow = TRUE)
-   }
-   r.proj <- function(x) {
+```{r Creating individual matrices}
+   row.breiger <- function(x) {
       x %*% t(x)
       }
-   c.proj <- function(x) {
+   col.breiger <- function(x) {
       t(x) %*% x
       }
-   ind.list <- split(dat[, 2:301], seq(nrow(dat)))
-   ind.mat <- lapply(ind.list, make.mat)
-   ind.row <- lapply(ind.mat, r.proj)
-   ind.col <- lapply(ind.mat, c.proj)
+   row.sim <- function(x) {
+      a <- rowSums(x)
+      b <- a %*% t(a)
+      c <- x %*% t(x)
+      d <- c/b
+      }
+   col.sim <- function(x) {
+      a <- colSums(x)
+      b <- a %*% t(a)
+      c <- t(x) %*% x 
+      d <- c/b
+      }
+   den <- rowSums(dat[,2:301])/300
+   bad.den <- which(den > .9 | den < 0.1)
+   dat2 <- dat[-c(bad.den), 2:301]
+   ind.list <- split(dat2, seq(nrow(dat2))) # splitting each row of data frame into list objects
+   ind.mat <- lapply(ind.list, function(x) {matrix(as.numeric(x), 20, 15, byrow = TRUE)}) # creating individual two mode network of genre by labels
+   r <- c("Classical", "Opera", "Jazz", "Broadway", "Easy", "Big_Band", "Oldies", "Country", "Bluegrass", "Folk", "Gospel", "Latin", "Rap", "Blues", "Reggae", "Pop", "Rock", "AltRock", "Dance", "Metal")
+       c <- c("Female", "Male", "White", "Black", "Hispanic", "Asian", "College", "No_College", "Young", "Mid_Age", "Old", "Lower_Class", "Working_Class", "Middle_Class", "Upper_Class")
+   ind.mat <- lapply(ind.mat, function(x) {rownames(x) <- r; x}) # naming individual rows
+   ind.mat <- lapply(ind.mat, function(x) {colnames(x) <- c; x}) # naming individual columns
+   ind.row <- lapply(ind.mat, row.breiger) # individual genre projection
+   ind.col <- lapply(ind.mat, col.breiger) # individual label projection
+   #ind.row <- lapply(ind.mat, row.sim) # individual genre projection
+   #ind.col <- lapply(ind.mat, col.sim) # individual label projection
+   row.stack <- matrix(unlist(ind.row), ncol = 20, byrow = TRUE) # genre stacked matrix
+   col.stack <- matrix(unlist(ind.col), ncol = 15, byrow = TRUE) # label stacked matrix
+   colnames(row.stack) <- r # naming genre stacked matrix columns
+   colnames(col.stack) <- c # naming label stacked matrix columns
+   rownames(row.stack) <- rep(r, nrow(dat2)) # naming genre stacked matrix rows
+   rownames(col.stack) <- rep(c, nrow(dat2)) # naming label stacked matrix rows
+   zero.rows.r <- which(rowSums(row.stack) == 0) # which genre stacked matrix rows sum to zero?
+   zero.rows.c <- which(rowSums(col.stack) == 0) # which label stacked matrix rows sum to zero?
 ```
+
+```{r CA Musical Genres}
+   row.stack.d <- data.frame(row.stack)
+   row.stack.d$genre <- rep(r, nrow(dat2))
+   row.stack.d$id <- rep(dat$id_char[-bad.den], each = 20)
+   CA.r <- CA(row.stack.d, graph = FALSE, row.sup = zero.rows.r, quali.sup = c(21, 22))
+```
+
+```{r CA Social Labels}
+   col.stack.d <- data.frame(col.stack)
+   col.stack.d$label <- rep(c, nrow(dat2))
+   col.stack.d$id <- rep(dat$id_char[-bad.den], each = 15)
+   CA.c <- CA(col.stack.d, graph = FALSE, row.sup = zero.rows.c, quali.sup = c(16, 17))
+```
+
+```{r Extracting column and supplementary scores for genres and labels}
+   plot.dat1 <-  data.frame(CA.r$col$coord) #genre column scores
+   plot.dat2 <-  data.frame(CA.c$col$coord) #label column scores
+   plot.dat3 <- data.frame(CA.r$quali.sup$coord)[1:20, ] #genre supp. scores
+   rownames(plot.dat3) <- gsub("genre.", "", rownames(plot.dat3))
+   plot.dat4 <- data.frame(CA.c$quali.sup$coord)[1:15, ] #genre label scores
+   rownames(plot.dat4) <- gsub("label.", "", rownames(plot.dat4))
+```
+
+```{r Prepping stacked CA data for plotting}
+   make.plot.dat <- function(x) { 
+      w <-  data.frame(rbind(x)) %>% 
+      mutate(col.obj = gsub("\\..*","",rownames(x))) 
+      rownames(w) <- 1:nrow(x)
+      return(w)
+      }
+   plot.dat.g <- make.plot.dat(CA.r$row$coord)
+   plot.dat.l <- make.plot.dat(CA.c$row$coord)
+```
+
+```{r Column Score Similarity Plots}
+   h <- 625
+   w <- 750
+   source(here("make.sim.plot.R"))
+   #genre plots
+   png(file = here("Plots", "ca-genre-col12.png"), width=w, height=h)
+   make.plot(plot.dat1, 1, 2, "blue")
+   dev.off()
+   png(file = here("Plots", "ca-genre-col13.png"), width=w, height=h)
+   make.plot(plot.dat1, 1, 3, "blue")
+   dev.off()
+   png(file = here("Plots", "ca-genre-col14.png"), width=w, height=h)
+   make.plot(plot.dat1, 1, 4, "blue")
+   dev.off()
+   # label plots
+   png(file = here("Plots", "ca-label-col12.png"), width=w, height=h)
+   make.plot(plot.dat2, 1, 2, "red")
+   dev.off()
+   png(file = here("Plots", "ca-label-col13.png"), width=w, height=h)
+   make.plot(plot.dat2, 1, 3, "red")
+   dev.off()
+   png(file = here("Plots", "ca-label-col14.png"), width=w, height=h)
+   make.plot(plot.dat2, 1, 4, "red")
+   dev.off()
+```
+
+```{r}
+      p <- ggplot(data = plot.dat.g, aes(x = Dim.1, y = Dim.3))
+      p <- p + geom_vline(xintercept = 0, color = "gray")
+      p <- p + geom_hline(yintercept = 0, color = "gray")
+      p <- p +   stat_density_2d(geom = "polygon", 
+                                 aes(alpha=..level.., fill = col.obj), 
+                                 bins = 2, color = "white")  
+      p <- p + theme_minimal()
+      p <- p + guides(color = "none", shape = "none", fill = "none")
+      p <- p +   scale_alpha(range = c(0, .35), guide = "none") 
+      p <- p + geom_text_repel(data = plot.dat3, 
+                               aes(label = rownames(plot.dat3)), 
+                               size = 3, 
+                               color = "black", 
+                               fontface = "bold")
+      p
+```
+
+      p <- p + geom_jitter(aes(shape = col.obj), alpha = 0.15, size = 2)
+      p <- p + geom_text(data = w, aes(x = w[, d1], w[, d2], label = rownames(w)), 
+                         color = "black", fontface = "bold", size = 5)
+      p <- p + xlim(-lim, lim) + ylim(-lim, lim) 
+      p <- p + labs(x = paste("Dim.", d1), y = paste("Dim", d2))
+      set.seed(seed)
+      p <- p + scale_color_manual(values = sample(cols, length(objs)))
+      p <- p + scale_fill_manual(values = sample(cols, length(objs)))
+      p <- p + theme_minimal() 
+      p <- p + theme(axis.text = element_text(size = 20), 
+                     axis.title = element_text(size = 24),
+                     legend.position = "none")
+```
+
+```{r Comparing Genre Scores to Cloud Centroids}
+   source(here("make.fuzz.plot.R"))
+   h <- 625
+   w <- 750
+   # genre plots
+   png(file = here("Plots", "genre-proto12.png"), width=w, height=h)
+      make.fuzz.plot(plot.dat.g, plot.dat3, 1, 2, c("Folk", "Rap", "Classical"))
+   dev.off()
+   png(file = here("Plots", "genre-proto13.png"), width=w, height=h)
+      make.fuzz.plot(plot.dat.g, plot.dat3, 1, 3, c("AltRock", "Opera", "Gospel"))
+   dev.off()
+   png(file = here("Plots", "genre-proto14.png"), width=w, height=h)
+      make.fuzz.plot(plot.dat.g, plot.dat3, 1, 4, c("Reggae", "Easy", "Classical"))
+   dev.off()
+   # label plots
+   png(file = here("Plots", "label-proto12-1.png"), width=w, height=h)
+      make.fuzz.plot(plot.dat.l, plot.dat4, 1, 2, c("Asian", "Female", "College"), lim = 1)
+   dev.off()  
+   png(file = here("Plots", "label-proto12-2.png"), width=w, height=h)
+      make.fuzz.plot(plot.dat.l, plot.dat4, 1, 2, c("Hispanic", "Black", "No_College"), lim = 1)
+   dev.off()  
+   png(file = here("Plots", "label-proto13.png"), width=w, height=h)
+      make.fuzz.plot(plot.dat.l, plot.dat4, 1, 3, c("Upper_Class", "Male", "No_College", "Asian"), lim = 1)
+   dev.off() 
+   png(file = here("Plots", "label-proto14.png"), width=w, height=h)
+      make.fuzz.plot(plot.dat.l, plot.dat4, 1, 4, c("Lower_Class", "White", "College"), lim = 1)
+   dev.off()
+```
+
+```{r Genre Ridge Plots}
+      make.ridge.dat <- function(col.dat, ca.rows) {
+        b <- col.dat %>% 
+         rename(Prot.1 = Dim.1, Prot.2 = Dim.2, Prot.3 = Dim.3) %>% 
+         mutate(col.obj = rownames(col.dat)) 
+      x <-  data.frame(rbind(ca.rows)) %>% 
+         mutate(col.obj = gsub("\\..*","",rownames(ca.rows))) %>% 
+         select(-c("Dim.4", "Dim.5")) %>% 
+         right_join(b) 
+      return(x)
+      }
+      make.ridge.plot <- function(x, d1, d2, lim = 1) {
+      p <- ggplot(data = x, aes(x = x[, d1], 
+                                y = reorder(col.obj, x[, d2]),
+                                group = col.obj, fill = col.obj, color = col.obj))
+      p <- p + geom_density_ridges(alpha = .2, point_alpha = .2, jittered_points = TRUE)
+      p <- p + guides(fill = "none", color = "none")
+      p <- p + geom_vline(xintercept = 0, color = "black", linewidth = 1.25)
+      p <- p + scale_color_manual(values = cols)
+      p <- p + theme(axis.text = element_text(size = 20), 
+                     axis.title = element_text(size = 24))
+      p <- p + labs(x = paste("Dim.", d1))
+      p <- p + theme_ridges() + xlim(-lim, lim) + labs(y = "") 
+      return(p)
+      }
+   # genres
+   ridge.dat.g <- make.ridge.dat(plot.dat1, CA.r$row$coord)
+   png(file = here("Plots", "genre-ridge-dim1.png"), width=w, height=h)
+   make.ridge.plot(ridge.dat.g, 1, 5)
+   dev.off()
+   png(file = here("Plots", "genre-ridge-dim2.png"), width=w, height=h)
+   make.ridge.plot(ridge.dat.g, 2, 6)
+   dev.off()
+   png(file = here("Plots", "genre-ridge-dim3.png"), width=w, height=h)
+   make.ridge.plot(ridge.dat.g, 3, 7)
+   dev.off()
+   #labels
+   ridge.dat.l <- make.ridge.dat(plot.dat2, CA.c$row$coord)
+   png(file = here("Plots", "label-ridge-dim1.png"), width=w, height=h)
+   make.ridge.plot(ridge.dat.l, 1, 5)
+   dev.off()
+   png(file = here("Plots", "label-ridge-dim2.png"), width=w, height=h)
+   make.ridge.plot(ridge.dat.l, 2, 6)
+   dev.off()
+   png(file = here("Plots", "label-ridge-dim3.png"), width=w, height=h)
+   make.ridge.plot(ridge.dat.l, 3, 7)
+   dev.off()
+```

### 2025-05-03 create-match.qmd
a buncha stuff

@@
 ---
-title: "Jilbert's Distinction Centrality"
+title: "Creating Genre Stereotype Match Matrix"
 author: "Omar Lizardo"
@@
 ```
+
 ```{r import data and select genre stereotype variables}
@@
    match.s <- (2*(match.f/300) - 1)
+   match.c <- cor(match.s)
    save(match.f, match.s, file = "match.rda")
+   save(match.f, match.s, match.c, file = "match.rda")
 ```

### 2025-05-03 heidelberg-slides.qmd
a buncha stuff

---
title: "Musical Genres as Fuzzy Categories"
subtitle: ""
author: "Omar Lizardo"
institute: "*University of California, Los Angeles*"
date: "`r Sys.Date()`"
format:
  revealjs:
    incremental: false 
    theme: simple 
    smaller: true
    slide-number: true
    slide-level: 2
    progress: true
    footer: "https://github.com/olizardo/cultural-consensus-musical-genres"
---

##

## Data
- We can treat the association data provided by respondents as **cognitive two-mode data**
  - In analogy with Krackhardt-style data for one-mode networks
  - Persons provide *perceived* associations between genres and social labels

## Average Perceptions
![](lizardo-skiles-tab3.png){width="85%"}

:::aside
Lizardo, O. and Skiles, S., 2016. Cultural objects as prisms: Perceived audience composition of musical genres as a resource for symbolic exclusion. *Socius*, 2, p.2378023116641695.
:::

## Stacked CA Analyses
- Three sets of scores:
  - row-scores are **person-specific** judgments of the relative similarity of genres and labels
  - column-scores represent the **aggregate judgment** of the relative similarity of genres (with respect to labels) and labels (with respect to genres)
  - Supplementary scores for genres and labels represent the **centroid** of the cloud of person-specific judgments

## Correspondence Plot of Genre Column Scores
![First and Second Dimensions](Plots/ca-genre-col12.png)

## Correspondence Plot of Genre Column Scores
![First and Third Dimensions](Plots/ca-genre-col13.png)

## Correspondence Plot of Genre Column Scores
![First and Fourth Dimensions](Plots/ca-genre-col14.png)

## Correspondence Plot of Label Column Scores
![First and Second Dimensions](Plots/ca-label-col12.png)

## Correspondence Plot of Label Column Scores
![First and Third Dimensions](Plots/ca-label-col13.png)

## Correspondence Plot of Label Column Scores
![First and Fourth Dimensions](Plots/ca-label-col14.png)

## Correspondence Plot of Genre Column Scores
![First and Second Dimensions](Plots/genre-sim-dens12.png)

## Correspondence Plot of Label Column Scores
![First and Second Dimensions](Plots/label-sim-dens12.png)

## Correspondence Plot of Genre Clouds
![First and Second Dimensions](Plots/genre-proto12.png)

## Correspondence Plot of Genre Clouds
![First and Third Dimensions](Plots/genre-proto13.png)

## Correspondence Plot of Genre Clouds
![First and Fourth Dimensions](Plots/genre-proto14.png)

## Correspondence Plot of Label Clouds
![First and Second Dimensions](Plots/label-proto12-1.png)

## Correspondence Plot of Label Clouds
![First and Second Dimensions](Plots/label-proto12-2.png)

## Correspondence Plot of Label Clouds
![First and Third Dimensions](Plots/label-proto13.png)

## Correspondence Plot of Label Clouds
![First and Fourth Dimensions](Plots/label-proto14.png)

## Genre Ridge Plot
![First Dimension](Plots/genre-ridge-dim1.png)

## Genre Ridge Plot
![Second Dimension](Plots/genre-ridge-dim2.png)

## Genre Ridge Plot
![Third Dimension](Plots/genre-ridge-dim3.png)

## Label Ridge Plot
![First Dimension](Plots/label-ridge-dim1.png)

## Label Ridge Plot
![Second Dimension](Plots/label-ridge-dim2.png)

## Label Ridge Plot
![Third Dimension](Plots/label-ridge-dim3.png)

### 2025-05-03 make.fuzz.plot.R

@@ -1,0 +1,27 @@
+make.fuzz.plot <- function(x, w, d1, d2, objs, lim = .5, seed = 3456) {
+   x <- filter(x, col.obj %in% objs) 
+   w$col.obj <- rownames(w)
+   w <- filter(w, col.obj %in% objs) 
+   p <- ggplot(data = x, aes(x = x[, d1], x[, d2], 
+                             group = col.obj, 
+                             fill = col.obj,
+                             color = col.obj))
+   p <- p + geom_vline(xintercept = 0, color = "gray")
+   p <- p + geom_hline(yintercept = 0, color = "gray")
+   p <- p + stat_density_2d(geom = "polygon", aes(alpha=..level..^2))
+   p <- p + geom_jitter(aes(shape = col.obj), alpha = 0.15, size = 2)
+   p <- p + geom_text(data = w, aes(x = w[, d1], w[, d2], label = rownames(w)), 
+                      color = "black", fontface = "bold", size = 5)
+   p <- p + xlim(-lim, lim) + ylim(-lim, lim) 
+   p <- p + labs(x = paste("Dim.", d1), y = paste("Dim", d2))
+   set.seed(seed)
+   p <- p + scale_color_manual(values = sample(cols, length(objs)))
+   p <- p + scale_fill_manual(values = sample(cols, length(objs)))
+   p <- p + theme_minimal() 
+   p <- p + theme(axis.text = element_text(size = 20), 
+                  axis.title = element_text(size = 24),
+                  legend.position = "none")
+   p <- p + guides(color = "none", shape = "none", fill = "none")
+   p <- p +   scale_alpha(range = c(0, 1), guide = "none") 
+   return(p)
+}

### 2025-05-03 make.sim.plot.R

@@ -1,0 +1,16 @@
+make.sim.plot <- function(x, d1, d2, c = "black", l = 0.6, s = 6) {
+   p <- ggplot(data = x, aes(x = x[, d1], y = x[, d2]))
+   p <- p + geom_vline(xintercept = 0, color = "gray")
+   p <- p + geom_hline(yintercept = 0, color = "gray")
+   p <- p + geom_text_repel(aes(label = rownames(x)), 
+                            size = s, 
+                            color = c, 
+                            fontface = "bold", 
+                            max.overlaps = 20)
+   p <- p + theme_minimal() 
+   p <- p + theme(axis.text = element_text(size = 20), 
+                  axis.title = element_text(size = 24))
+   p <- p + labs(x = paste("Dim.", d1), y = paste("Dim", d2))
+   p <- p + ylim(-l, l) + xlim(-l, l)
+   return(p)
+}

### 2025-05-05 analysis-noproj.qmd
a buncha

---
title: "CA of Music Genre Stereotypes"
author: "Omar Lizardo"
date: "`r Sys.Date()`"
execute: 
  eval: true
  echo: true
  output: true
  warning: false
  message: false
---

```{r setup, include=FALSE}
   library(conflicted)
   library(dplyr)
   library(FactoMineR)
   library(ggplot2)
   library(ggrepel)
   library(corrplot)
   library(ggridges)
   library(haven)
   library(here)
   library(paletteer)
   cols <- paletteer_dynamic("cartography::multi.pal", 20)
   conflicts_prefer(dplyr::filter)
   conflicts_prefer(dplyr::select)
```

```{r import data and select genre stereotype variables}
   #importing data
   dat <- read_dta("C:/Users/Omar Lizardo/Google Drive/MISC DATA SOURCES/SSI-2012/SSI2012.dta")
   #replacing ids with character names
   dat <- bind_cols(tibble(id_char = paste("id", sapply(dat[, 1], as.character), sep = "_")), dat) %>% 
   select(id_char, classicalfemale:hvymtluc, -ends_with("none")) %>%  #selecting relevant columns
   na.omit() #removing missing values
   head(dat)
```

```{r Creating individual matrices}
      r <- c("Classical", "Opera", "Jazz", "Broadway", "Easy", "Big_Band", "Classic_Rock", "Country", "Bluegrass", "Folk", "Gospel", "Latin", "Rap", "Blues", "Reggae", "Pop", "Contemp_Rock", "AltRock", "Dance", "Metal")
       c <- c("Female", "Male", "White", "Black", "Hispanic", "Asian", "College", "No_College", "Young", "Mid_Age", "Old", "Lower_Class", "Working_Class", "Middle_Class", "Upper_Class")
   den <- rowSums(dat[,2:301])/300
   bad.den <- which(den > .95 | den < 0.05)
   dat2 <- dat[-c(bad.den), 2:301]
   ind.list <- split(dat2, seq(nrow(dat2))) # splitting each row of data frame into list objects
   ind.mat <- lapply(ind.list, function(x) {matrix(as.numeric(x), 20, 15, byrow = TRUE)}) # creating individual two mode network of genre by labels
   ind.mat.t <- lapply(ind.list, function(x) {matrix(as.numeric(x), 20, 15, byrow = TRUE)}) # creating individual two mode network of genre by labels
   ind.mat.t <- lapply(ind.mat.t, function(x) {t(x)})
   ind.mat <- lapply(ind.mat, function(x) {rownames(x) <- r; x}) # naming individual rows
   ind.mat <- lapply(ind.mat, function(x) {colnames(x) <- c; x}) # naming individual columns
   ind.mat.t <- lapply(ind.mat.t, function(x) {rownames(x) <- c; x}) # naming individual transposed rows
   ind.mat.t <- lapply(ind.mat.t, function(x) {colnames(x) <- r; x}) # naming individual transposed columns
   names(ind.mat) <- dat$id_char[-c(bad.den)]
   names(ind.mat.t) <- dat$id_char[-c(bad.den)]
   row.stack <- matrix(unlist(ind.mat), ncol = 15, byrow = TRUE) # genre stacked matrix
   col.stack <- matrix(unlist(ind.mat.t), ncol = 20, byrow = TRUE) # label stacked matrix
   colnames(row.stack) <- c # naming genre stacked matrix columns
   colnames(col.stack) <- r # naming label stacked matrix columns
   rownames(row.stack) <- rep(r, nrow(dat2)) # naming genre stacked matrix rows
   rownames(col.stack) <- rep(c, nrow(dat2)) # naming label stacked matrix rows
   zero.rows.r <- which(rowSums(row.stack) == 0) # which genre stacked matrix rows sum to zero?
   zero.rows.c <- which(rowSums(col.stack) == 0) # which label stacked matrix rows sum to zero?
```

```{r Data Examples (Two Mode)}
   png(file = here("Plots", "data-ex1.png"), width=700, height=700)
      corrplot(ind.mat[["id_65"]], is.corr = FALSE, method = "color", 
         tl.col = "black", tl.cex = 1, tl.srt = 45,
         addCoef.col = "black", cl.pos = "n",
         number.cex = 1.75, number.digits = 0, addgrid.col = "darkgray",
         col=colorRampPalette(c("white","white","red"))(200))
   dev.off()
   png(file = here("Plots", "data-ex2.png"), width=700, height=700)
      corrplot(ind.mat[["id_236"]], is.corr = FALSE, method = "color", 
         tl.col = "black", tl.cex = 1, tl.srt = 45,
         addCoef.col = "black", cl.pos = "n",
         number.cex = 1.75, number.digits = 0, addgrid.col = "darkgray",
         col=colorRampPalette(c("white","white","red"))(200))
   dev.off()
   png(file = here("Plots", "data-ex3.png"), width=700, height=700)
      corrplot(ind.mat[["id_1114"]], is.corr = FALSE, method = "color", 
         tl.col = "black", tl.cex = 1, tl.srt = 45,
         addCoef.col = "black", cl.pos = "n",
         number.cex = 1.75, number.digits = 0, addgrid.col = "darkgray",
         col=colorRampPalette(c("white","white","red"))(200))
   dev.off()
   png(file = here("Plots", "data-ex4.png"), width=700, height=700)
      corrplot(ind.mat[["id_2002"]], is.corr = FALSE, method = "color", 
         tl.col = "black", tl.cex = 1, tl.srt = 45,
         addCoef.col = "black", cl.pos = "n",
         number.cex = 1.75, number.digits = 0, addgrid.col = "darkgray",
         col=colorRampPalette(c("white","white","red"))(200))
   dev.off()

   ex.stack <- rbind(ind.mat[["id_65"]], ind.mat[["id_236"]])
   ex.stack.t <- rbind(t(ind.mat[["id_1114"]]), t(ind.mat[["id_2002"]]))
   png(file = here("Plots", "data-ex-stack.png"), width=700, height=700)
      corrplot(ex.stack, is.corr = FALSE, method = "color", 
         tl.col = "black", tl.cex = 0.75, tl.srt = 45,
         addCoef.col = "black", cl.pos = "n",
         number.cex = 1, number.digits = 0, addgrid.col = "darkgray",
         col=colorRampPalette(c("white","white","red"))(200))
   dev.off()
   png(file = here("Plots", "data-ex-stack-t.png"), width=700, height=700)
      corrplot(ex.stack.t, is.corr = FALSE, method = "color", 
         tl.col = "black", tl.cex = 0.75, tl.srt = 45,
         addCoef.col = "black", cl.pos = "n",
         number.cex = 1, number.digits = 0, addgrid.col = "darkgray",
         col=colorRampPalette(c("white","white","red"))(200))
   dev.off()
```

```{r CA}
   #genres
   row.stack.d <- data.frame(row.stack)
   row.stack.d$genre <- rep(r, nrow(dat2))
   row.stack.d$id <- rep(dat$id_char[-bad.den], each = 20)
   CA.r <- CA(row.stack.d, graph = FALSE, row.sup = zero.rows.r, quali.sup = c(16, 17))
   #labels
   col.stack.d <- data.frame(col.stack)
   col.stack.d$label <- rep(c, nrow(dat2))
   col.stack.d$id <- rep(dat$id_char[-bad.den], each = 15)
   CA.c <- CA(col.stack.d, graph = FALSE, row.sup = zero.rows.c, quali.sup = c(21, 22))
```

```{r Plot Data}
     make.plot.dat <- function(x) { 
         w <-  data.frame(x) %>% 
         mutate(col.obj = gsub("\\..*","",rownames(x))) 
         rownames(w) <- 1:nrow(x)
         return(w)
         }
      col.lab.dat <-  data.frame(CA.r$col$coord) #genre column scores
      col.gen.dat <-  data.frame(CA.c$col$coord) #label column scores
      sup.gen.dat <- CA.r$quali.sup$coord[1:20, ] 
      sup.lab.dat <- CA.c$quali.sup$coord[1:15, ] 
      sup.gen.dat <- data.frame(sup.gen.dat, 
                                col.obj = gsub("genre.", "", rownames(sup.gen.dat)))
      rownames(sup.gen.dat) <- sup.gen.dat$col.obj
      sup.lab.dat <- data.frame(sup.lab.dat, 
                                col.obj = gsub("label.", "", rownames(sup.lab.dat)))
      rownames(sup.lab.dat) <- sup.lab.dat$col.obj
      row.gen.dat <- make.plot.dat(CA.r$row$coord) #genre row scores
      row.lab.dat <- make.plot.dat(CA.c$row$coord) #label row scores
```

```{r Column and Supplementary Score Similarity Plots}
   h <- 625
   w <- 750
   source(here("make.sim.plot.R"))
   #genres
   png(file = here("Plots", "ca-genre-col12.png"), width=w, height=h)
   make.sim.plot(col.gen.dat, 1, 2, "red", l = 1)
   dev.off()
   png(file = here("Plots", "ca-genre-sup12.png"), width=w, height=h)
   make.sim.plot(sup.gen.dat, 1, 2, "red", l = .6)
   dev.off()
   # labels
   png(file = here("Plots", "ca-label-col12.png"), width=w, height=h)
   make.sim.plot(col.lab.dat, 1, 2, "blue", l = 1)
   dev.off()
   png(file = here("Plots", "ca-label-sup12.png"), width=w, height=h)
   make.sim.plot(sup.lab.dat, 1, 2, "blue", l = .6)
   dev.off()
```

```{r Genre Cloud Plots}
   source(here("make.fuzz.plot.R"))
   h <- 625
   w <- 750
   png(file = here("Plots", "genre-proto-ex1.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, sup.gen.dat, seed = 23456,
                     1, 2, xl = 2, yl = 2, pa = .05,
                     c("Folk", "Contemp_Rock", "Big_Band", "Classic_Rock"))
   dev.off()
   png(file = here("Plots", "genre-proto-ex2.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, sup.gen.dat, seed = 234,
                     1, 2, xl = 2, yl = 2, pa = .05,
                     c("Reggae", "Opera", "Rap", "Opera"))
   dev.off()
   png(file = here("Plots", "genre-proto-ex3.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, sup.gen.dat, seed = 234,
                     1, 2, xl = 2, yl = 1.5, pa = .05,
                     c("Gospel", "Latin", "Easy"))
   dev.off()
```

```{r Label Cloud Plots}
   source(here("make.fuzz.plot.R"))
   h <- 625
   w <- 750
   png(file = here("Plots", "label-proto-ex1.png"), width=w, height=h)
      make.fuzz.plot(row.lab.dat, sup.lab.dat, seed = 234,
                     1, 2, xl = 2, yl = 2, pa = .05,
                     c("College", "Male", "Upper_Class"))
   dev.off()
   png(file = here("Plots", "label-proto-ex2.png"), width=w, height=h)
      make.fuzz.plot(row.lab.dat, sup.lab.dat, seed = 234,
                     1, 2, xl = 2, yl = 2, pa = .05,
                     c("Female", "No_College", "White"))
   dev.off()
   png(file = here("Plots", "label-proto-ex3.png"), width=w, height=h)
      make.fuzz.plot(row.lab.dat, sup.lab.dat, seed = 234,
                     1, 2, xl = 2, yl = 2.5, pa = .05,
                     c("Asian", "Working_Class", "Hispanic"))
   dev.off()
```

```{r Genre Ridge Plots}
      make.ridge.dat <- function(col.dat, ca.rows) {
        b <- col.dat %>% 
         rename(Prot.1 = Dim.1, Prot.2 = Dim.2, Prot.3 = Dim.3) %>% 
         mutate(col.obj = rownames(col.dat)) 
      x <-  data.frame(rbind(ca.rows)) %>% 
         mutate(col.obj = gsub("\\..*","",rownames(ca.rows))) %>% 
         select(-c("Dim.4", "Dim.5")) %>% 
         right_join(b) 
      return(x)
      }
      make.ridge.plot <- function(x, d1, d2, lim = 1) {
      p <- ggplot(data = x, aes(x = x[, d1], 
                                y = reorder(col.obj, x[, d2]),
                                group = col.obj, fill = col.obj, color = col.obj))
      p <- p + geom_density_ridges(alpha = .2, point_alpha = .2, jittered_points = TRUE)
      p <- p + guides(fill = "none", color = "none")
      p <- p + geom_vline(xintercept = 0, color = "black", linewidth = 1.25)
      p <- p + scale_color_manual(values = cols)
      p <- p + theme(axis.text = element_text(size = 20), 
                     axis.title = element_text(size = 24))
      p <- p + labs(x = paste("Dim.", d1))
      p <- p + theme_ridges() + xlim(-lim, lim) + labs(y = "") 
      return(p)
      }
   # genres
   ridge.dat.g <- make.ridge.dat(plot.dat1, CA.r$row$coord)
   png(file = here("Plots", "genre-ridge-dim1.png"), width=w, height=h)
   make.ridge.plot(ridge.dat.g, 1, 5)
   dev.off()
   png(file = here("Plots", "genre-ridge-dim2.png"), width=w, height=h)
   make.ridge.plot(ridge.dat.g, 2, 6)
   dev.off()
   png(file = here("Plots", "genre-ridge-dim3.png"), width=w, height=h)
   make.ridge.plot(ridge.dat.g, 3, 7)
   dev.off()
   #labels
   ridge.dat.l <- make.ridge.dat(plot.dat2, CA.c$row$coord)
   png(file = here("Plots", "label-ridge-dim1.png"), width=w, height=h)
   make.ridge.plot(ridge.dat.l, 1, 5)
   dev.off()
   png(file = here("Plots", "label-ridge-dim2.png"), width=w, height=h)
   make.ridge.plot(ridge.dat.l, 2, 6)
   dev.off()
   png(file = here("Plots", "label-ridge-dim3.png"), width=w, height=h)
   make.ridge.plot(ridge.dat.l, 3, 7)
   dev.off()
```

### 2025-05-05 analysis-proj.qmd
a buncha

---
title: "CA of Music Genre Stereotypes"
author: "Omar Lizardo"
date: "`r Sys.Date()`"
execute: 
  eval: true
  echo: true
  output: true
  warning: false
  message: false
---

```{r setup, include=FALSE}
   library(conflicted)
   library(dplyr)
   library(FactoMineR)
   library(ggplot2)
   library(ggrepel)
   library(corrplot)
   library(ggridges)
   library(haven)
   library(here)
   library(paletteer)
   cols <- paletteer_dynamic("cartography::multi.pal", 20)
   conflicts_prefer(dplyr::filter)
   conflicts_prefer(dplyr::select)
```

```{r import data and select genre stereotype variables}
   #importing data
   dat <- read_dta("C:/Users/Omar Lizardo/Google Drive/MISC DATA SOURCES/SSI-2012/SSI2012.dta")
   #replacing ids with character names
   dat <- bind_cols(tibble(id_char = paste("id", sapply(dat[, 1], as.character), sep = "_")), dat) %>% 
   select(id_char, classicalfemale:hvymtluc, -ends_with("none")) %>%  #selecting relevant columns
   na.omit() #removing missing values
   head(dat)
```

```{r Creating individual matrices}
   row.breiger <- function(x) {
      x %*% t(x)
      }
   col.breiger <- function(x) {
      t(x) %*% x
      }
   den <- rowSums(dat[,2:301])/300
   bad.den <- which(den > .95 | den < 0.05)
   dat2 <- dat[-c(bad.den), 2:301]
   ind.list <- split(dat2, seq(nrow(dat2))) # splitting each row of data frame into list objects
   ind.mat <- lapply(ind.list, function(x) {matrix(as.numeric(x), 20, 15, byrow = TRUE)}) # creating individual two mode network of genre by labels
      r <- c("Classical", "Opera", "Jazz", "Broadway", "Easy", "Big_Band", "Classic_Rock", "Country", "Bluegrass", "Folk", "Gospel", "Latin", "Rap", "Blues", "Reggae", "Pop", "Contemp_Rock", "Alt_Rock", "Dance", "Metal")
       c <- c("Female", "Male", "White", "Black", "Hispanic", "Asian", "College", "No_College", "Young", "Mid_Age", "Old", "Lower_Class", "Working_Class", "Middle_Class", "Upper_Class")
   ind.mat <- lapply(ind.mat, function(x) {rownames(x) <- r; x}) # naming individual rows
   ind.mat <- lapply(ind.mat, function(x) {colnames(x) <- c; x}) # naming individual columns
   names(ind.mat) <- dat$id_char[-c(bad.den)]
   ind.row <- lapply(ind.mat, row.breiger) # individual genre projection
   ind.col <- lapply(ind.mat, col.breiger) # individual label projection
   row.stack <- matrix(unlist(ind.row), ncol = 20, byrow = TRUE) # genre stacked matrix
   col.stack <- matrix(unlist(ind.col), ncol = 15, byrow = TRUE) # label stacked matrix
   colnames(row.stack) <- r # naming genre stacked matrix columns
   colnames(col.stack) <- c # naming label stacked matrix columns
   rownames(row.stack) <- rep(r, nrow(dat2)) # naming genre stacked matrix rows
   rownames(col.stack) <- rep(c, nrow(dat2)) # naming label stacked matrix rows
   zero.rows.r <- which(rowSums(row.stack) == 0) # which genre stacked matrix rows sum to zero?
   zero.rows.c <- which(rowSums(col.stack) == 0) # which label stacked matrix rows sum to zero?
   names(ind.row) <- dat$id_char[-c(bad.den)]
   names(ind.col) <- dat$id_char[-c(bad.den)]
```

```{r Data Examples (Two Mode)}
   png(file = here("Plots", "data-ex1.png"), width=700, height=700)
      corrplot(ind.mat[["id_65"]], is.corr = FALSE, method = "color", 
         tl.col = "black", tl.cex = 1, tl.srt = 45,
         addCoef.col = "black", cl.pos = "n",
         number.cex = 1.75, number.digits = 0, addgrid.col = "darkgray",
         col=colorRampPalette(c("white","white","red"))(200))
   dev.off()
   png(file = here("Plots", "data-ex2.png"), width=700, height=700)
      corrplot(ind.mat[["id_236"]], is.corr = FALSE, method = "color", 
         tl.col = "black", tl.cex = 1, tl.srt = 45,
         addCoef.col = "black", cl.pos = "n",
         number.cex = 1.75, number.digits = 0, addgrid.col = "darkgray",
         col=colorRampPalette(c("white","white","red"))(200))
   dev.off()
   png(file = here("Plots", "data-ex3.png"), width=700, height=700)
      corrplot(ind.mat[["id_1114"]], is.corr = FALSE, method = "color", 
         tl.col = "black", tl.cex = 1, tl.srt = 45,
         addCoef.col = "black", cl.pos = "n",
         number.cex = 1.75, number.digits = 0, addgrid.col = "darkgray",
         col=colorRampPalette(c("white","white","red"))(200))
   dev.off()
   png(file = here("Plots", "data-ex4.png"), width=700, height=700)
      corrplot(ind.mat[["id_2002"]], is.corr = FALSE, method = "color", 
         tl.col = "black", tl.cex = 1, tl.srt = 45,
         addCoef.col = "black", cl.pos = "n",
         number.cex = 1.75, number.digits = 0, addgrid.col = "darkgray",
         col=colorRampPalette(c("white","white","red"))(200))
   dev.off()
```

```{r Data Examples (Projections)}
   png(file = here("Plots", "data-ex1-rp.png"), width=700, height=700)
      m <- max(ind.row[["id_65"]])
     corrplot(ind.row[["id_65"]], is.corr = FALSE, method = "color", 
         tl.col = "black", tl.cex = 1, tl.srt = 45,
         addCoef.col = "black", cl.pos = "n", cl.lim = c(0, m),
         number.cex = 1.5, number.digits = 0, addgrid.col = "darkgray",
         col=colorRampPalette(c("lightblue","pink","red"))(200))
   dev.off()
   png(file = here("Plots", "data-ex1-cp.png"), width=700, height=700)
      m <- max(ind.col[["id_65"]])
     corrplot(ind.col[["id_65"]], is.corr = FALSE, method = "color", 
         tl.col = "black", tl.cex = 1, tl.srt = 45,
         addCoef.col = "black", cl.pos = "n", cl.lim = c(0, m),
         number.cex = 1.5, number.digits = 0, addgrid.col = "darkgray",
         col=colorRampPalette(c("lightblue","pink","red"))(200))
   dev.off()
   png(file = here("Plots", "data-ex2-rp.png"), width=700, height=700)
      m <- max(ind.row[["id_236"]])
     corrplot(ind.row[["id_236"]], is.corr = FALSE, method = "color", 
         tl.col = "black", tl.cex = 1, tl.srt = 45,
         addCoef.col = "black", cl.pos = "n", cl.lim = c(0, m),
         number.cex = 1.5, number.digits = 0, addgrid.col = "darkgray",
         col=colorRampPalette(c("lightblue","pink","red"))(200))
   dev.off()
   png(file = here("Plots", "data-ex2-cp.png"), width=700, height=700)
      m <- max(ind.col[["id_236"]])
     corrplot(ind.col[["id_236"]], is.corr = FALSE, method = "color", 
         tl.col = "black", tl.cex = 1, tl.srt = 45,
         addCoef.col = "black", cl.pos = "n", cl.lim = c(0, m),
         number.cex = 1.5, number.digits = 0, addgrid.col = "darkgray",
         col=colorRampPalette(c("lightblue","pink","red"))(200))
   dev.off()
   a <- rbind(ind.row[["id_65"]], ind.row[["id_236"]])
   b <- rbind(ind.col[["id_65"]], ind.col[["id_236"]])
   png(file = here("Plots", "data-ex-stack1.png"), width=700, height=700)
     corrplot(a, is.corr = FALSE, method = "color", 
         tl.col = "black", tl.cex = 1, tl.srt = 45,
         addCoef.col = "black", cl.pos = "n", cl.lim = c(0, max(a)),
         number.cex = 1, number.digits = 0, addgrid.col = "darkgray",
         col=colorRampPalette(c("lightblue","pink","red"))(200))
   dev.off()
   png(file = here("Plots", "data-ex-stack2.png"), width=700, height=700)
     corrplot(b, is.corr = FALSE, method = "color", 
         tl.col = "black", tl.cex = 1, tl.srt = 45,
         addCoef.col = "black", cl.pos = "n", cl.lim = c(0, max(b)),
         number.cex = 1, number.digits = 0, addgrid.col = "darkgray",
         col=colorRampPalette(c("lightblue","pink","red"))(200))
   dev.off()
```

```{r CA Musical Genres}
   row.stack.d <- data.frame(row.stack)
   row.stack.d$genre <- rep(r, nrow(dat2))
   row.stack.d$id <- rep(dat$id_char[-bad.den], each = 20)
   CA.r <- CA(row.stack.d, graph = FALSE, row.sup = zero.rows.r, quali.sup = c(21, 22))
```

```{r CA Social Labels}
   col.stack.d <- data.frame(col.stack)
   col.stack.d$label <- rep(c, nrow(dat2))
   col.stack.d$id <- rep(dat$id_char[-bad.den], each = 15)
   CA.c <- CA(col.stack.d, graph = FALSE, row.sup = zero.rows.c, quali.sup = c(16, 17))
```

```{r Plot Data}
     make.plot.dat <- function(x) { 
         w <-  data.frame(x) %>% 
         mutate(col.obj = gsub("\\..*","",rownames(x))) 
         rownames(w) <- 1:nrow(x)
         return(w)
         }
      col.gen.dat <-  data.frame(CA.r$col$coord) %>% 
         mutate(col.obj = rownames(CA.r$col$coord)) #genre column scores
      col.lab.dat <-  data.frame(CA.c$col$coord) %>% 
         mutate(col.obj = rownames(CA.c$col$coord)) #label column scores
      sup.gen.dat <- CA.r$quali.sup$coord[1:20, ] 
      sup.lab.dat <- CA.c$quali.sup$coord[1:15, ] 
      sup.gen.dat <- data.frame(sup.gen.dat, 
                                col.obj = gsub("genre.", "", rownames(sup.gen.dat)))
      rownames(sup.gen.dat) <- sup.gen.dat$col.obj
      sup.lab.dat <- data.frame(sup.lab.dat, 
                                col.obj = gsub("label.", "", rownames(sup.lab.dat)))
      rownames(sup.lab.dat) <- sup.lab.dat$col.obj
      row.gen.dat <- make.plot.dat(CA.r$row$coord) #genre row scores
      row.lab.dat <- make.plot.dat(CA.c$row$coord) #label row scores
```

```{r Column Score Similarity Plots}
   h <- 625
   w <- 750
   source(here("make.sim.plot.R"))
   #genres
   png(file = here("Plots", "ca-genre-col12.png"), width=w, height=h)
   make.sim.plot(col.gen.dat, 1, 2, "red", l = .5)
   dev.off()
   png(file = here("Plots", "ca-genre-col13.png"), width=w, height=h)
   make.sim.plot(col.gen.dat, 1, 3, "red", l = .5)
   dev.off()
   # labels
   png(file = here("Plots", "ca-label-col12.png"), width=w, height=h)
   make.sim.plot(col.lab.dat, 1, 2, "blue", l = .75)
   dev.off()
   png(file = here("Plots", "ca-label-col13.png"), width=w, height=h)
   make.sim.plot(col.lab.dat, 1, 3, "blue", l = .75)
   dev.off()
```

```{r Genre Cloud Plots}
   source(here("make.fuzz.plot.R"))
   h <- 625
   w <- 750
   png(file = here("Plots", "genre-proto-ex1.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, sup.gen.dat, seed = 125,
                     1, 2, xl = .5, yl = .5, pa = .15,
                     c("Folk", "Rap", "Opera"))
   dev.off()
   png(file = here("Plots", "genre-proto-ex2.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, sup.gen.dat, seed = 125,
                     1, 2, xl = .5, yl = .5, pa = .15,
                     c("Latin", "Bluegrass", "Classical"))
   dev.off()
   png(file = here("Plots", "genre-proto-ex3.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, sup.gen.dat, seed = 125,
                     1, 3, xl = .5, yl = .5, pa = .15,
                     c("Alt_Rock", "Reggae", "Broadway"))
   dev.off()
```

```{r Label Cloud Plots}
   source(here("make.fuzz.plot.R"))
   h <- 625
   w <- 750
   png(file = here("Plots", "label-proto-ex1.png"), width=w, height=h)
      make.fuzz.plot(row.lab.dat, sup.lab.dat, 1, 2, ylb = 0.5,
                     c("White", "Asian", "Black", "Hispanic"))
   dev.off()
   png(file = here("Plots", "label-proto-ex2.png"), width=w, height=h)
      make.fuzz.plot(row.lab.dat, sup.lab.dat, 1, 3,
                     c("Old", "Mid_Age", "Young"))
   dev.off()
   png(file = here("Plots", "label-proto-ex3.png"), width=w, height=h)
      make.fuzz.plot(row.lab.dat, sup.lab.dat, 1, 3,
                     c("Upper_Class", "Lower_Class", "Middle_Class"))
   dev.off()
   png(file = here("Plots", "label-proto-ex4.png"), width=w, height=h)
      make.fuzz.plot(row.lab.dat, sup.lab.dat, 1, 3, xlb = 0.5, xlt = 0.5,
                     c("College", "No_College"))
   dev.off()
```

### 2025-05-05 heidelberg-slides.qmd
a buncha

@@
 
-## Correspondence Plot of Genre Column Scores
-![First and Second Dimensions](Plots/ca-genre-col12.png)
+## Mondo Breiger Approach
 
-## Correspondence Plot of Genre Column Scores
-![First and Third Dimensions](Plots/ca-genre-col13.png)
+- Each individual provides a "personal" two mode network of genres by social labels with corresponding affiliation matrix $\mathbf{A}(p)$
+  - $a^{(p)}_{gl} = 1$ if individual $p$ associates genre $g$ with label $l$
+- The personal genre projection is given by:
+  - $\mathbf{G}(p) = \mathbf{A}(p)\mathbf{A}(p)^T$
+  - $g^{(p)}_{ij}$ records the $p^{th}$ individual's perceived similarity between genres $i$ and $j$ based on their shared labels
+  - $g^{(p)}_{ii}$ records the number of times individual $p$ associates genre $i$ with a label
 
-## Correspondence Plot of Genre Column Scores
-![First and Fourth Dimensions](Plots/ca-genre-col14.png)
+## Mondo Breiger Approach
+
+- Each individual provides a "personal" two mode network of genres by social labels with corresponding affiliation matrix $\mathbf{A}(p)$
+  - $a^{(p)}_{gl} = 1$ if individual $p$ associates genre $g$ with label $l$
+- The personal label projection is given by:
+  - $\mathbf{L}(p) = \mathbf{A}(p)^T\mathbf{A}(p)$
+  - $l^{(p)}_{kl}$ records the $p^{th}$ individual's perceived similarity between labels $k$ and $l$ based on their shared genres
+  - $l^{(p)}_{kk}$ records the number of times individual $p$ associates genre $i$ with a label
+
+## Individual Matrix Examples (Two Mode)
+:::: {.columns}
+::: {.column width="50%"}
+![id_65](Plots/data-ex1.png)
+:::
+::: {.column width="50%"}
+![id_236](Plots/data-ex2.png)
+:::
+::::
+
+## Individual Matrix Examples (Two Mode)
+:::: {.columns}
+::: {.column width="50%"}
+![id_1114](Plots/data-ex3.png)
+:::
+::: {.column width="50%"}
+![id_2002](Plots/data-ex4.png)
+:::
+::::
+
+## Example Row Projection
+:::: {.columns}
+::: {.column width="50%"}
+![id_65](Plots/data-ex1.png)
+:::
+::: {.column width="50%"}
+![id_65](Plots/data-ex1-rp.png)
+:::
+::::
+
+##  Example Column Projection
+:::: {.columns}
+::: {.column width="50%"}
+![id_65](Plots/data-ex1.png)
+:::
+::: {.column width="50%"}
+![id_65](Plots/data-ex1-cp.png)
+:::
+::::
+
+##  Example Row Projection
+:::: {.columns}
+::: {.column width="50%"}
+![id_236](Plots/data-ex2.png)
+:::
+::: {.column width="50%"}
+![id_236](Plots/data-ex2-rp.png)
+:::
+::::
+
+##  Example Column Projection
+:::: {.columns}
+::: {.column width="50%"}
+![id_65](Plots/data-ex2.png)
+:::
+::: {.column width="50%"}
+![id_65](Plots/data-ex2-cp.png)
+:::
+::::
+
+##  Stacked Matrices Examples
+:::: {.columns}
+::: {.column width="50%"}
+![id_65 and id_236 (Rows)](Plots/data-ex-stack1.png)
+:::
+::: {.column width="50%"}
+![id_65 and id_236 (Columns)](Plots/data-ex-stack2.png)
+:::
+::::
 
@@
 
-## Correspondence Plot of Label Column Scores
-![First and Fourth Dimensions](Plots/ca-label-col14.png)
+## Correspondence Plot of Genre Column Scores
+![First and Second Dimensions](Plots/ca-genre-col12.png)
 
 ## Correspondence Plot of Genre Column Scores
-![First and Second Dimensions](Plots/genre-sim-dens12.png)
-
-## Correspondence Plot of Label Column Scores
-![First and Second Dimensions](Plots/label-sim-dens12.png)
+![First and Third Dimensions](Plots/ca-genre-col13.png)
 
 ## Correspondence Plot of Genre Clouds
-![First and Second Dimensions](Plots/genre-proto12.png)
+![First and Second Dimensions](Plots/genre-proto-ex1.png)
 
 ## Correspondence Plot of Genre Clouds
-![First and Third Dimensions](Plots/genre-proto13.png)
+![First and Second Dimensions](Plots/genre-proto-ex2.png)
 
 ## Correspondence Plot of Genre Clouds
-![First and Fourth Dimensions](Plots/genre-proto14.png)
+![First and Second Dimensions](Plots/genre-proto-ex3.png)
 
 ## Correspondence Plot of Label Clouds
-![First and Second Dimensions](Plots/label-proto12-1.png)
+![First and Second Dimensions](Plots/label-proto-ex1.png)
 
 ## Correspondence Plot of Label Clouds
-![First and Second Dimensions](Plots/label-proto12-2.png)
+![First and Second Dimensions](Plots/label-proto-ex2.png)
 
 ## Correspondence Plot of Label Clouds
-![First and Third Dimensions](Plots/label-proto13.png)
+![First and Second Dimensions](Plots/label-proto-ex3.png)
 
 ## Correspondence Plot of Label Clouds
-![First and Fourth Dimensions](Plots/label-proto14.png)
-
-## Genre Ridge Plot
-![First Dimension](Plots/genre-ridge-dim1.png)
-
-## Genre Ridge Plot
-![Second Dimension](Plots/genre-ridge-dim2.png)
-
-## Genre Ridge Plot
-![Third Dimension](Plots/genre-ridge-dim3.png)
-
-## Label Ridge Plot
-![First Dimension](Plots/label-ridge-dim1.png)
-
-## Label Ridge Plot
-![Second Dimension](Plots/label-ridge-dim2.png)
-
-## Label Ridge Plot
-![Third Dimension](Plots/label-ridge-dim3.png)
+![First and Second Dimensions](Plots/label-proto-ex4.png)

### 2025-05-05 make.fuzz.plot.R

@@ -1,27 +1,27 @@
-make.fuzz.plot <- function(x, w, d1, d2, objs, lim = .5, seed = 3456) {
+make.fuzz.plot <- function(x, w, d1, d2, objs,  
+                           xlt = 1.25, xlb = 1.25, ylt = 1.25, ylb = 1.25, 
+                           pa = 0.15, ls = 4,
+                           seed = 125) {
    x <- filter(x, col.obj %in% objs) 
-   w$col.obj <- rownames(w)
    w <- filter(w, col.obj %in% objs) 
-   p <- ggplot(data = x, aes(x = x[, d1], x[, d2], 
-                             group = col.obj, 
-                             fill = col.obj,
-                             color = col.obj))
+   p <- ggplot(data = x, aes(x[, d1], x[, d2]))
    p <- p + geom_vline(xintercept = 0, color = "gray")
    p <- p + geom_hline(yintercept = 0, color = "gray")
-   p <- p + stat_density_2d(geom = "polygon", aes(alpha=..level..^2))
-   p <- p + geom_jitter(aes(shape = col.obj), alpha = 0.15, size = 2)
-   p <- p + geom_text(data = w, aes(x = w[, d1], w[, d2], label = rownames(w)), 
-                      color = "black", fontface = "bold", size = 5)
-   p <- p + xlim(-lim, lim) + ylim(-lim, lim) 
+   p <- p + stat_density_2d(geom = "polygon", 
+                            aes(alpha=after_stat(level), fill = col.obj, color = col.obj))
+   p <- p + geom_jitter(aes(fill = col.obj, color = col.obj), alpha = pa, size = 2)    
+   p <- p + geom_text_repel(data = w, aes(w[, d1], w[, d2]),
+                      label = rownames(w), color = "darkblue", fontface = "bold", size = ls)
+   p <- p + xlim(-xlb, xlt) + ylim(-ylb, ylt) 
    p <- p + labs(x = paste("Dim.", d1), y = paste("Dim", d2))
    set.seed(seed)
-   p <- p + scale_color_manual(values = sample(cols, length(objs)))
-   p <- p + scale_fill_manual(values = sample(cols, length(objs)))
+   c <- sample(cols, length(objs))
+   p <- p + scale_color_manual(values = c)
+   p <- p + scale_fill_manual(values = c)
    p <- p + theme_minimal() 
    p <- p + theme(axis.text = element_text(size = 20), 
                   axis.title = element_text(size = 24),
[…]

### 2025-05-05 old-stuff-slide.R

@@ -1,0 +1,64 @@
+<!--
+   
+   ## Correspondence Plot of Genre Column Scores
+   ![First and Second Dimensions](Plots/ca-genre-col12.png)
+
+## Correspondence Plot of Genre Column Scores
+![First and Third Dimensions](Plots/ca-genre-col13.png)
+
+## Correspondence Plot of Genre Column Scores
+![First and Fourth Dimensions](Plots/ca-genre-col14.png)
+
+## Correspondence Plot of Label Column Scores
+![First and Second Dimensions](Plots/ca-label-col12.png)
+
+## Correspondence Plot of Label Column Scores
+![First and Third Dimensions](Plots/ca-label-col13.png)
+
+## Correspondence Plot of Label Column Scores
+![First and Fourth Dimensions](Plots/ca-label-col14.png)
+
+## Correspondence Plot of Genre Column Scores
+![First and Second Dimensions](Plots/genre-sim-dens12.png)
+
+## Correspondence Plot of Label Column Scores
+![First and Second Dimensions](Plots/label-sim-dens12.png)
+
+
+## Correspondence Plot of Genre Clouds
+![First and Third Dimensions](Plots/genre-proto13.png)
+
+## Correspondence Plot of Genre Clouds
+![First and Fourth Dimensions](Plots/genre-proto14.png)
+
+## Correspondence Plot of Label Clouds
+![First and Second Dimensions](Plots/label-proto12-1.png)
+
+## Correspondence Plot of Label Clouds
+![First and Second Dimensions](Plots/label-proto12-2.png)
+
+## Correspondence Plot of Label Clouds
+![First and Third Dimensions](Plots/label-proto13.png)
+
+## Correspondence Plot of Label Clouds
+![First and Fourth Dimensions](Plots/label-proto14.png)
+
+## Genre Ridge Plot
+![First Dimension](Plots/genre-ridge-dim1.png)
+
+## Genre Ridge Plot
+![Second Dimension](Plots/genre-ridge-dim2.png)
+
+## Genre Ridge Plot
+![Third Dimension](Plots/genre-ridge-dim3.png)
+
+## Label Ridge Plot
+![First Dimension](Plots/label-ridge-dim1.png)
+
+## Label Ridge Plot
+![Second Dimension](Plots/label-ridge-dim2.png)
+
+## Label Ridge Plot
+![Third Dimension](Plots/label-ridge-dim3.png)
+
+-->

### 2025-05-05 old-stuff1.R

@@ -1,0 +1,342 @@
+```{r Data Examples (Two Mode)}
+id1 <- "id_236"
+id2 <- "id_1114"
+id3 <- "id_2002"
+ex.A <- ind.mat[[id1]]
+p <- ggcorrplot(t(ex.A), lab = TRUE, lab_size = 6)
+p <- p + theme(legend.position = "none", 
+               axis.text.x = element_text(hjust = -0.2, size = 16),
+               axis.text.y = element_text(size = 16))  
+p <- p + scale_x_discrete(position = "top") + scale_y_discrete(limits=rev)
+p <- p + ggtitle(id1)
+p <- p + theme(title = element_text(size = 24))
+png(file = here("Plots", "data-ex1.png"), width=700, height=700)
+p
+dev.off()
+
+ex.A <- ind.mat[[id2]]
+p <- ggcorrplot(t(ex.A), lab = TRUE, lab_size = 6)
+p <- p + theme(legend.position = "none", 
+               axis.text.x = element_text(hjust = -0.2, size = 16),
+               axis.text.y = element_text(size = 16))  
+p <- p + scale_x_discrete(position = "top") + scale_y_discrete(limits=rev)
+p <- p + ggtitle(id2)
+p <- p + theme(title = element_text(size = 24))
+png(file = here("Plots", "data-ex2.png"), width=700, height=700)
+p
+dev.off()
+ex.A <- ind.mat[[id3]]
+p <- ggcorrplot(t(ex.A), lab = TRUE, lab_size = 6)
+p <- p + theme(legend.position = "none", 
+               axis.text.x = element_text(hjust = -0.2, size = 16),
+               axis.text.y = element_text(size = 16))  
+p <- p + scale_x_discrete(position = "top") + scale_y_discrete(limits=rev)
+p <- p + ggtitle(id3)
+p <- p + theme(title = element_text(size = 24))
+png(file = here("Plots", "data-ex3.png"), width=700, height=700)
+p
+dev.off()
+```
+
+
+```{r Data Examples (Genre Projections)}
+ex.A <- filter(row.stack.d, id == id1) %>% 
+   select(-c(id, genre))  
+rownames(ex.A) <- gsub(".184", "", rownames(ex.A))
+p <- ggcorrplot(t(ex.A), lab = TRUE, lab_size = 6,
+                ggtheme = ggplot2::theme_minimal(), colors = rep("white", 3))
+p <- p + theme(legend.position = "none", 
[…]

### 2025-05-06 Old/analysis-proj.qmd
do it

--- 2025-05-05 analysis-proj.qmd
@@
    na.omit() #removing missing values
-   head(dat)
 ```

### 2025-05-06 analysis-bb.qmd
do it

---
title: "CA of Music Genre Stereotypes"
author: "Omar Lizardo"
date: "`r Sys.Date()`"
execute: 
  eval: true
  echo: true
  output: true
  warning: false
  message: false
---

```{r setup, include=FALSE}
   library(conflicted)
   library(dplyr)
   library(FactoMineR)
   library(factoextra)
   library(ggplot2)
   library(ggrepel)
   library(corrplot)
   library(ggridges)
   library(haven)
   library(here)
   library(paletteer)
   cols <- paletteer_dynamic("cartography::multi.pal", 20)
   conflicts_prefer(dplyr::filter)
   conflicts_prefer(dplyr::select)
   source(here("make.sim.plot.R"))
   source(here("make.fuzz.plot.R"))
```

```{r import data and select genre stereotype variables}
   #importing data
   dat <- read_dta("C:/Users/Omar Lizardo/Google Drive/MISC DATA SOURCES/SSI-2012/SSI2012.dta")
   #replacing ids with character names
   dat <- bind_cols(tibble(id_char = paste("id", sapply(dat[, 1], as.character), sep = "_")), dat) %>% 
   select(id_char, classicalfemale:hvymtluc, -ends_with("none")) %>%  #selecting relevant columns
   na.omit() #removing missing values
```

```{r Creating individual matrices}
   row.breiger <- function(x) {
      x %*% t(x)
      }
   col.breiger <- function(x) {
      t(x) %*% x
      }
   bb <- function(x) {
      x <- suppressMessages(disparity(x, alpha = 0.25, narrative = FALSE))
      return(x)
      }
   den <- rowSums(dat[,2:301])/300
   bad.den <- which(den > .95 | den < 0.05)
   dat2 <- dat[-c(bad.den), 2:301]
   ind.list <- split(dat2, seq(nrow(dat2))) # splitting each row of data frame into list objects
   ind.mat <- lapply(ind.list, function(x) {matrix(as.numeric(x), 20, 15, byrow = TRUE)}) # creating individual two mode network of genre by labels
      r <- c("Classical", "Opera", "Jazz", "Broadway", "Easy", "Big_Band", "Classic_Rock", "Country", "Bluegrass", "Folk", "Gospel", "Latin", "Rap", "Blues", "Reggae", "Pop", "Contemp_Rock", "Alt_Rock", "Dance", "Metal")
       c <- c("Female", "Male", "White", "Black", "Hispanic", "Asian", "College", "No_College", "Young", "Mid_Age", "Old", "Lower_Class", "Working_Class", "Middle_Class", "Upper_Class")
   ind.mat <- lapply(ind.mat, function(x) {rownames(x) <- r; x}) # naming individual rows
   ind.mat <- lapply(ind.mat, function(x) {colnames(x) <- c; x}) # naming individual columns
   names(ind.mat) <- dat$id_char[-c(bad.den)]
   ind.row <- lapply(ind.mat, row.breiger) # individual genre projection
   ind.col <- lapply(ind.mat, col.breiger) # individual label projection
   row.bb <- lapply(ind.row, bb)
   col.bb <- lapply(ind.col, bb)
   row.stack <- matrix(unlist(row.bb), ncol = 20, byrow = TRUE) # genre stacked matrix
   col.stack <- matrix(unlist(col.bb), ncol = 15, byrow = TRUE) # label stacked matrix
   colnames(row.stack) <- r # naming genre stacked matrix columns
   colnames(col.stack) <- c # naming label stacked matrix columns
   rownames(row.stack) <- rep(r, nrow(dat2)) # naming genre stacked matrix rows
   rownames(col.stack) <- rep(c, nrow(dat2)) # naming label stacked matrix rows
   zero.rows.r <- which(rowSums(row.stack) == 0) # which genre stacked matrix rows sum to zero?
   zero.rows.c <- which(rowSums(col.stack) == 0) # which label stacked matrix rows sum to zero?
   names(ind.row) <- dat$id_char[-c(bad.den)]
   names(ind.col) <- dat$id_char[-c(bad.den)]
   names(row.bb) <- dat$id_char[-c(bad.den)]
   names(col.bb) <- dat$id_char[-c(bad.den)]
```

```{r Stacked CA}
   #genres
   row.stack.d <- data.frame(row.stack)
   row.stack.d$genre <- rep(r, nrow(dat2))
   row.stack.d$id <- rep(dat$id_char[-bad.den], each = 20)
   CA.r <- CA(row.stack.d, graph = FALSE, row.sup = zero.rows.r, quali.sup = c(21, 22))
   #labels
   col.stack.d <- data.frame(col.stack)
   col.stack.d$label <- rep(c, nrow(dat2))
   col.stack.d$id <- rep(dat$id_char[-bad.den], each = 15)
   CA.c <- CA(col.stack.d, graph = FALSE, row.sup = zero.rows.c, quali.sup = c(16, 17))
```

```{r CA Statistics}
   stuff <- theme(axis.text = element_text(size = 18),
                  axis.title = element_text(size = 22))
   png(file = here("Plots", "scree-genres.png"), width=300, height=600)
   fviz_eig(CA.r, ncp = 6) + stuff + ggtitle("") + ylim(0, 12) + 
      labs(y = "Explained Var. %")
   dev.off()
   png(file = here("Plots", "scree-labels.png"), width=300, height=600)
   fviz_eig(CA.c, ncp = 6) + stuff + ggtitle("") + ylim(0, 12) + 
      labs(y = "Explained Var. %")
   dev.off()
```

```{r Plot Data}
     make.plot.dat <- function(x) { 
         w <-  data.frame(x) %>% 
         mutate(col.obj = gsub("\\..*","",rownames(x))) 
         rownames(w) <- 1:nrow(x)
         return(w)
         }
      col.gen.dat <-  data.frame(CA.r$col$coord) %>% 
         mutate(col.obj = rownames(CA.r$col$coord)) #genre column scores
      col.lab.dat <-  data.frame(CA.c$col$coord) %>% 
         mutate(col.obj = rownames(CA.c$col$coord)) #label column scores
      sup.gen.dat <- CA.r$quali.sup$coord[1:20, ] 
      sup.lab.dat <- CA.c$quali.sup$coord[1:15, ] 
      sup.gen.dat <- data.frame(sup.gen.dat, 
                                col.obj = gsub("genre.", "", rownames(sup.gen.dat)))
      rownames(sup.gen.dat) <- sup.gen.dat$col.obj
      sup.lab.dat <- data.frame(sup.lab.dat, 
                                col.obj = gsub("label.", "", rownames(sup.lab.dat)))
      rownames(sup.lab.dat) <- sup.lab.dat$col.obj
      row.gen.dat <- make.plot.dat(CA.r$row$coord) #genre row scores
      row.lab.dat <- make.plot.dat(CA.c$row$coord) #label row scores
```

```{r Data Examples}
   make.aff.plot <- function(x) {
      p <- corrplot(x, is.corr = FALSE, method = "color", 
         tl.col = "black", tl.cex = 1, tl.srt = 45,
         addCoef.col = "black", cl.pos = "n",
         number.cex = 1.75, number.digits = 0, addgrid.col = "darkgray",
         col=colorRampPalette(c("white","white","red"))(200))
      return(p)
      }
   make.proj.plot <- function(x) {
     p <- corrplot(x, is.corr = FALSE, method = "color", 
         tl.col = "black", tl.cex = 1, tl.srt = 45,
         addCoef.col = "black", cl.pos = "n", cl.lim = c(0, max(x)),
         number.cex = 1.5, number.digits = 0, addgrid.col = "darkgray",
         col=colorRampPalette(c("lightblue","pink","red"))(200))
         return(p)
         }
   k = 1
   for (id in c("id_65", "id_236", "id_1114", "id_2002")) {
      plot.name <- paste(paste("data-ex-af", k, sep = ""), ".png", sep = "")
      png(file = here("Plots", plot.name), width=700, height=700)
      make.aff.plot(ind.mat[[id]])
      dev.off()
      plot.name <- paste(paste("data-ex-rp", k, sep = ""), ".png", sep = "")
      png(file = here("Plots", plot.name), width=800, height=700)
      make.proj.plot(ind.row[[id]])
      dev.off()
      plot.name <- paste(paste("data-ex-cp", k, sep = ""), ".png", sep = "")
      png(file = here("Plots", plot.name), width=800, height=700)
      make.proj.plot(ind.col[[id]])
      dev.off()
      plot.name <- paste(paste("data-ex-rbb", k, sep = ""), ".png", sep = "")
      png(file = here("Plots", plot.name), width=800, height=700)
      make.aff.plot(row.bb[[id]])
      dev.off()
      plot.name <- paste(paste("data-ex-cbb", k, sep = ""), ".png", sep = "")
      png(file = here("Plots", plot.name), width=800, height=700)
      make.aff.plot(col.bb[[id]])
      dev.off()
      k <- k + 1
      }
   a <- rbind(row.bb[["id_65"]], row.bb[["id_236"]])
   b <- rbind(col.bb[["id_65"]], col.bb[["id_236"]])
   png(file = here("Plots", "data-ex-stack1.png"), width=800, height=1000)
   make.aff.plot(a)
   dev.off()
   png(file = here("Plots", "data-ex-stack2.png"), width=800, height=1000)
   make.aff.plot(b)
   dev.off()
```

```{r Column Score Similarity Plots}
   make.col.plot <- function(x, d1, d2)  {
      p <- fviz_ca_col(x, axes = c(d1, d2),  
                        col.col = "contrib", labelsize = 6,
                        gradient.cols = c("#C555CBFF", "#722E41FF", "#502E71FF"),
                        repel = TRUE)
      p <- p + theme(legend.position = "bottom",
                     axis.text = element_text(size = 18),
                     axis.title = element_text(size = 22),
                     legend.title = element_blank())
      p <- p + ggtitle("")
      return(p)
   }
   h <- 625
   w <- 750
   #genres
   png(file = here("Plots", "ca-genre-col12.png"), width=w, height=h)
   make.col.plot(CA.r, 1, 2)
   dev.off()
   png(file = here("Plots", "ca-genre-col13.png"), width=w, height=h)
   make.col.plot(CA.r, 1, 3)
   dev.off()
   png(file = here("Plots", "ca-label-col12.png"), width=w, height=h)
   make.col.plot(CA.c, 1, 2)
   dev.off()
   png(file = here("Plots", "ca-label-col13.png"), width=w, height=h)
   make.col.plot(CA.c, 1, 3)
   dev.off()
```

```{r Genre Cloud Plots}
   source(here("make.fuzz.plot.R"))
   h <- 625
   w <- 750
   png(file = here("Plots", "genre-proto-ex1.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, col.gen.dat, sup.gen.dat, 
                     seed = 125, ls = 5,
                     1, 2, pa = .35,  t = 3, b = 3, l = 2, r = 3,
                     c("Rap", "Folk", "Classical"))
   dev.off()
   png(file = here("Plots", "genre-proto-ex2.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, col.gen.dat, sup.gen.dat,
                     seed = 125, ls = 5,
                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3,
                     c("Alt_Rock", "Gospel", "Opera"))
   dev.off()
   png(file = here("Plots", "genre-proto-ex3.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, col.gen.dat, sup.gen.dat,
                     seed = 125, ls = 5,
                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 5,
                     c("Metal", "Bluegrass", "Broadway"))
   dev.off()
   png(file = here("Plots", "genre-proto-ex4.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, col.gen.dat, sup.gen.dat,
                     seed = 125, ls = 5,
                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 4,
                     c("Jazz", "Reggae", "Blues", "Rap", "Classical"))
   dev.off()
   png(file = here("Plots", "genre-proto-ex5.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, col.gen.dat, sup.gen.dat,
                     seed = 125, ls = 5,
                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 4,
                     c("Country", "Bluegrass", "Classic_Rock", "Folk"))
   dev.off()
   png(file = here("Plots", "genre-proto-ex6.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, col.gen.dat, sup.gen.dat,
                     seed = 125, ls = 5,
                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 4,
                     c("Alt_Rock", "Contemp_Rock", "Classic_Rock", "Metal"))
   dev.off()
   png(file = here("Plots", "genre-proto-ex7.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, col.gen.dat, sup.gen.dat,
                     seed = 125, ls = 5,
                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 4,
                     c("Broadway", "Classical", "Opera", "Easy", "Jazz"))
   dev.off()
```

```{r Label Cloud Plots}
   source(here("make.fuzz.plot.R"))
   h <- 625
   w <- 750
   png(file = here("Plots", "label-proto-ex1.png"), width=w, height=h)
      make.fuzz.plot(row.lab.dat, sup.lab.dat, bns = 6, ls = 6,
                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 2,
                     c("White", "Asian", "Black", "Hispanic"))
   dev.off()
   png(file = here("Plots", "label-proto-ex2.png"), width=w, height=h)
      make.fuzz.plot(row.lab.dat, sup.lab.dat, bns = 6, ls = 6,
                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 2,
                     c("Old", "Mid_Age", "Young"))
   dev.off()
   png(file = here("Plots", "label-proto-ex3.png"), width=w, height=h)
      make.fuzz.plot(row.lab.dat, sup.lab.dat, bns = 6, ls = 6,
                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 2,
                     c("Upper_Class", "Lower_Class", "Working_Class", "Middle_Class"))
   dev.off()
   png(file = here("Plots", "label-proto-ex4.png"), width=w, height=h)
      make.fuzz.plot(row.lab.dat, sup.lab.dat, bns = 6, ls = 6,
                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 2,
                     c("College", "No_College"))
   dev.off()

   png(file = here("Plots", "label-proto-ex5.png"), width=w, height=h)
      make.fuzz.plot(row.lab.dat, sup.lab.dat, bns = 6, ls = 6,
                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 2,
                     c("Male", "Female"))
   dev.off()
```

```{r Genre Ridge Plots}
   make.ridge.dat <- function(x, w) {
      x <- rename(x, Prot.1 = Dim.1, Prot.2 = Dim.2, Prot.3 = Dim.3, Prot.4 = Dim.4, Prot.5 = Dim.5) 
      x <- left_join(w, x) 
      return(x)
      }
   make.ridge.plot <- function(x, d1, d2, lim = 1) {
      p <- ggplot(data = x, aes(x = x[, d1], 
                                y = reorder(col.obj, x[, d2]),
                                group = col.obj, fill = col.obj, color = col.obj))
      p <- p + geom_density_ridges(alpha = .2, point_alpha = .2, jittered_points = TRUE)
      p <- p + guides(fill = "none", color = "none")
      p <- p + geom_vline(xintercept = 0, color = "black", linewidth = 1.25)
      p <- p + scale_color_manual(values = cols)
      p <- p + theme_ridges()
      p <- p + theme(axis.text = element_text(size = 22), 
                     axis.title = element_text(size = 22))
      p <- p + labs(x = "", y = "")
      return(p)
      }
   w <- 1000
   h <- 1000
   # genres
   ridge.dat.g <- make.ridge.dat(col.gen.dat, row.gen.dat)
   png(file = here("Plots", "genre-ridge-dim1.png"), width=w, height=h)
   make.ridge.plot(ridge.dat.g, 1, 7)
   dev.off()
   png(file = here("Plots", "genre-ridge-dim2.png"), width=w, height=h)
   make.ridge.plot(ridge.dat.g, 2, 8)
   dev.off()
   png(file = here("Plots", "genre-ridge-dim3.png"), width=w, height=h)
   make.ridge.plot(ridge.dat.g, 3, 9)
   dev.off()
   #labels
   ridge.dat.l <- make.ridge.dat(col.lab.dat, row.lab.dat)
   png(file = here("Plots", "label-ridge-dim1.png"), width=w, height=h)
   make.ridge.plot(ridge.dat.l, 1, 7)
   dev.off()
   png(file = here("Plots", "label-ridge-dim2.png"), width=w, height=h)
   make.ridge.plot(ridge.dat.l, 2, 8)
   dev.off()
   png(file = here("Plots", "label-ridge-dim3.png"), width=w, height=h)
   make.ridge.plot(ridge.dat.l, 3, 9)
   dev.off()
```

```{r Genre and Label Subcloud Variance}
   w <- 600
   h <- 700
   var.g <- make.ridge.dat(sup.gen.dat, row.gen.dat) %>% 
      mutate(dist.cent.1 = (Dim.1 - Prot.1)^2) %>% 
      mutate(dist.cent.2 = (Dim.2 - Prot.2)^2) %>% 
      mutate(dist.cent.3 = (Dim.3 - Prot.3)^2) %>% 
      mutate(var = dist.cent.1 + dist.cent.2 + dist.cent.3) %>% 
      mutate(std = sqrt(var)) %>% 
      select(c("var", "std", "col.obj")) %>% 
      group_by(col.obj) %>% 
      summarize(across(c(var), mean))
   var.l <- make.ridge.dat(sup.lab.dat, row.lab.dat) %>% 
      mutate(dist.cent.1 = (Dim.1 - Prot.1)^2) %>% 
      mutate(dist.cent.2 = (Dim.2 - Prot.2)^2) %>% 
      mutate(dist.cent.3 = (Dim.3 - Prot.3)^2) %>% 
      mutate(var = dist.cent.1 + dist.cent.2 + dist.cent.3) %>% 
      mutate(std = sqrt(var)) %>% 
      select(c("var", "std", "col.obj")) %>% 
      group_by(col.obj) %>% 
      summarize(across(c(var), mean))
   make.bar.plot <- function(w) {
      p <- ggplot(data = w, aes(y = reorder(col.obj, var), 
                                x = var, color = col.obj, group = col.obj))
      p <- p + geom_point(stat = "identity", size = 8)
      p <- p + scale_color_manual(values = cols)
      p <- p + guides(color = "none")
      p <- p + theme_ridges() + labs(y = "", x = "")
      p <- p + theme(axis.text = element_text(size = 18))
      p
      }
   png(file = here("Plots", "genre-var.png"), width=w, height=h)
   make.bar.plot(var.g) + xlim(0.75, 1.75)
   dev.off()
   png(file = here("Plots", "label-var.png"), width=w, height=h)
   make.bar.plot(var.l) + xlim(0.75, 1.75)
   dev.off()
```

```{r skew and kurtosis data}
   library(moments)
   dat <- c()
   for (g in sup.gen.dat$col.obj) {
      d <- filter(row.gen.dat, col.obj == g) %>% 
         select(Dim.1) 
      s <- round(skewness(d), 4)
      k <- round(kurtosis(d), 4)
      b <- round((s^2+1)/k, 4)
      dat <- rbind(dat, c(s, k, b))
      }
   dat.g1 <- data.frame(sup.gen.dat$col.obj, dat) %>% 
      rename(col.obj = sup.gen.dat.col.obj, skew = Dim.1, kurt = Dim.1.1, bm = Dim.1.2) %>% 
      mutate(kurt = kurt - 3)
   dat <- c()
   for (g in sup.gen.dat$col.obj) {
      d <- filter(row.gen.dat, col.obj == g) %>% 
         select(Dim.2) 
      s <- round(skewness(d), 4)
      k <- round(kurtosis(d), 4)
      b <- round((s^2+1)/k, 4)
      dat <- rbind(dat, c(s, k, b))
      }
   dat.g2 <- data.frame(sup.gen.dat$col.obj, dat) %>% 
      rename(col.obj = sup.gen.dat.col.obj, skew = Dim.2, kurt = Dim.2.1, bm = Dim.2.2) %>% 
      mutate(kurt = kurt - 3)
   dat <- c()
   for (l in sup.lab.dat$col.obj) {
      d <- filter(row.lab.dat, col.obj == l) %>% 
         select(Dim.1) 
      s <- round(skewness(d), 4)
      k <- round(kurtosis(d), 4)
      b <- round((s^2+1)/k, 4)
      dat <- rbind(dat, c(s, k, b))
      }
   dat.l1 <- data.frame(sup.lab.dat$col.obj, dat) %>% 
      rename(col.obj = sup.lab.dat.col.obj, skew = Dim.1, kurt = Dim.1.1, bm = Dim.1.2) %>% 
      mutate(kurt = kurt - 3)
   dat <- c()
   for (l in sup.lab.dat$col.obj) {
      d <- filter(row.lab.dat, col.obj == l) %>% 
         select(Dim.2) 
      s <- round(skewness(d), 4)
      k <- round(kurtosis(d), 4)
      b <- round((s^2+1)/k, 4)
      dat <- rbind(dat, c(s, k, b))
      }
   dat.l2 <- data.frame(sup.lab.dat$col.obj, dat) %>% 
      rename(col.obj = sup.lab.dat.col.obj, skew = Dim.2, kurt = Dim.2.1, bm = Dim.2.2) %>% 
      mutate(kurt = kurt - 3)
```

```{r skew and kurtosis plots}
   #gennres
   png(file = here("Plots", "genre-skew1.png"), width=w, height=h)
   d <- dat.g1 %>% 
      rename(var = skew)
   make.bar.plot(d) 
   dev.off()
   png(file = here("Plots", "genre-skew2.png"), width=w, height=h)
   d <- dat.g2 %>% 
      rename(var = skew)
   make.bar.plot(d) 
   dev.off()
   png(file = here("Plots", "genre-kurt1.png"), width=w, height=h)
   d <- dat.g1 %>% 
      rename(var = kurt)
   make.bar.plot(d)    
   dev.off()
   png(file = here("Plots", "genre-kurt2.png"), width=w, height=h)
   d <- dat.g2 %>% 
      rename(var = kurt)
   make.bar.plot(d) 
   dev.off()
   #labels
   png(file = here("Plots", "label-skew1.png"), width=w, height=h)
   d <- dat.l1 %>% 
      rename(var = skew)
   make.bar.plot(d) 
   dev.off()
   png(file = here("Plots", "label-skew2.png"), width=w, height=h)
   d <- dat.l2 %>% 
      rename(var = skew)
   make.bar.plot(d) 
   dev.off()
   png(file = here("Plots", "label-kurt1.png"), width=w, height=h)
   d <- dat.l1 %>% 
      rename(var = kurt)
   make.bar.plot(d)    
   dev.off()
   png(file = here("Plots", "label-kurt2.png"), width=w, height=h)
   d <- dat.l2 %>% 
      rename(var = kurt)
   make.bar.plot(d) 
   dev.off()
```

```{r}
   source(here("demog.dat.R"))
   demog.dat <- demog.dat() 
   demog.dat <- bind_cols(tibble(id_char = paste("id", sapply(demog.dat[, 1], as.character), sep = "_")), demog.dat)
   head(demog.dat) 
   row.gen.dat.id <- cbind(row.gen.dat, id_char = row.stack.d$id[-zero.rows.r])
   classical.cloud <- filter(row.gen.dat.id, col.obj == "Classical")
   classical.dat <- left_join(classical.cloud, row.gen.dat.id)
   classical.dat <- left_join(classical.dat, demog.dat)
```

```{r}
   p <- ggplot(data = classical.dat, aes(Dim.1, Dim.2))
   p <- p + stat_density_2d(geom = "polygon", 
                            aes(alpha=after_stat(level)), bins = 5)
   p
```

### 2025-05-06 heidelberg-slides.qmd
do it

@@
 
-## Individual Matrix Examples (Two Mode)
+## Individual Matrix Examples 
 :::: {.columns}
 ::: {.column width="50%"}
-![id_65](Plots/data-ex1.png)
+![id_65 Affiliation Matrix](Plots/data-ex-af1.png)
 :::
 ::: {.column width="50%"}
-![id_236](Plots/data-ex2.png)
+![id_236 Affiliation Matrix](Plots/data-ex-af2.png)
 :::
@@
 
-## Individual Matrix Examples (Two Mode)
+## Individual Matrix Examples 
 :::: {.columns}
 ::: {.column width="50%"}
-![id_1114](Plots/data-ex3.png)
+![id_1114 Affiliation Matrix](Plots/data-ex-af3.png)
 :::
 ::: {.column width="50%"}
-![id_2002](Plots/data-ex4.png)
+![id_2002 Affiliation Matrix](Plots/data-ex-af4.png)
 :::
@@
 ::: {.column width="50%"}
-![id_65](Plots/data-ex1.png)
+![id_65 Affiliation Matrix](Plots/data-ex-af1.png)
 :::
 ::: {.column width="50%"}
-![id_65](Plots/data-ex1-rp.png)
+![id_65 Row Projection](Plots/data-ex-rp1.png)
 :::
@@
 ::: {.column width="50%"}
-![id_65](Plots/data-ex1.png)
+![id_65 Affiliation Matrix](Plots/data-ex-af1.png)
 :::
 ::: {.column width="50%"}
-![id_65](Plots/data-ex1-cp.png)
+![id_65 Column Projection](Plots/data-ex-cp1.png)
 :::
@@
 ::: {.column width="50%"}
-![id_236](Plots/data-ex2.png)
+![id_236 Affiliation Matrix](Plots/data-ex-af2.png)
 :::
 ::: {.column width="50%"}
-![id_236](Plots/data-ex2-rp.png)
+![id_236 Row Projection](Plots/data-ex-rp2.png)
 :::
@@
 ::: {.column width="50%"}
-![id_65](Plots/data-ex2.png)
+![id_236 Affiliation Matrix](Plots/data-ex-af2.png)
 :::
 ::: {.column width="50%"}
-![id_65](Plots/data-ex2-cp.png)
+![id_236 Column Projection](Plots/data-ex-cp2.png)
+:::
+::::
+
+##  Example Row Backbone
+:::: {.columns}
+::: {.column width="50%"}
+![id_65 Row Projection](Plots/data-ex-rp1.png)
+:::
+::: {.column width="50%"}
+![id_65 Row Backbone](Plots/data-ex-rbb1.png)
+:::
+::::
+
+##  Example Row Backbone
+:::: {.columns}
+::: {.column width="50%"}
+![id_236 Row Projection](Plots/data-ex-rp2.png)
+:::
+::: {.column width="50%"}
+![id_236 Row Backbone](Plots/data-ex-rbb2.png)
+:::
+::::
+
+##  Example Column Backbone
+:::: {.columns}
+::: {.column width="50%"}
+![id_65 Column Projection](Plots/data-ex-cp1.png)
+:::
+::: {.column width="50%"}
+![id_65 Column Backbone](Plots/data-ex-cbb1.png)
+:::
+::::
+
+##  Example Column Backbone
+:::: {.columns}
+::: {.column width="50%"}
+![id_236 Column Projection](Plots/data-ex-cp2.png)
+:::
+::: {.column width="50%"}
+![id_236 Column Backbone](Plots/data-ex-cbb2.png)
 :::
@@
 
-## Correspondence Plot of Label Column Scores
-![First and Second Dimensions](Plots/ca-label-col12.png)
-
-## Correspondence Plot of Label Column Scores
-![First and Third Dimensions](Plots/ca-label-col13.png)
+## CA Eigenvalue Scree Plot
+:::: {.columns}
+::: {.column width="50%"}
+![Stacked Genres](Plots/scree-genres.png)
+:::
+::: {.column width="50%"}
+![Stacked Labels](Plots/scree-labels.png)
+:::
+::::
 
@@
 ![First and Third Dimensions](Plots/ca-genre-col13.png)
+
+## Correspondence Plot of Label Column Scores
+![First and Second Dimensions](Plots/ca-label-col12.png)
+
+## Correspondence Plot of Label Column Scores
+![First and Third Dimensions](Plots/ca-label-col13.png)
 
@@
 ![First and Second Dimensions](Plots/genre-proto-ex3.png)
+
+## Correspondence Plot of Genre Clouds
+![First and Second Dimensions](Plots/genre-proto-ex4.png)
+
+## Correspondence Plot of Genre Clouds
+![First and Second Dimensions](Plots/genre-proto-ex5.png)
+
+## Correspondence Plot of Genre Clouds
+![First and Second Dimensions](Plots/genre-proto-ex6.png)
+
+## Correspondence Plot of Genre Clouds
+![First and Second Dimensions](Plots/genre-proto-ex7.png)
 
@@
 ![First and Second Dimensions](Plots/label-proto-ex4.png)
+
+## Correspondence Plot of Label Clouds
+![First and Second Dimensions](Plots/label-proto-ex5.png)
+
+## Ridge Plot of Genre Clouds
+![First Dimension](Plots/genre-ridge-dim1.png)
+
+## Ridge Plot of Genre Clouds
+![Second Dimension](Plots/genre-ridge-dim2.png)
+
+## Ridge Plot of Genre Clouds
+![Third Dimension](Plots/genre-ridge-dim3.png)
+
+## Ridge Plot of Label Clouds
+![First Dimension](Plots/label-ridge-dim1.png)
+
+## Ridge Plot of Label Clouds
+![Second Dimension](Plots/label-ridge-dim2.png)
+
+## Ridge Plot of Label Clouds
+![Third Dimension](Plots/label-ridge-dim3.png)
+
+## Cloud Variance
+:::: {.columns}
+::: {.column width="47%"}
+![Genres](Plots/genre-var.png)
+:::
+::: {.column width="47%"}
+![Labels](Plots/label-var.png)
+:::
+::::
+
+## Cloud Skewness
+:::: {.columns}
+::: {.column width="47%"}
+![Skewness of Genres (Dim 1)](Plots/genre-skew1.png)
+:::
+::: {.column width="47%"}
+![Skewness of Genres (Dim 2)](Plots/genre-skew2.png)
+:::
+::::
+
+## Cloud Kurtosis
+:::: {.columns}
+::: {.column width="47%"}
+![Kurtosis of Genres (Dim 1)](Plots/genre-kurt1.png)
+:::
+::: {.column width="47%"}
+![Kurtosis of Genres (Dim 2)](Plots/genre-kurt2.png)
+:::
+::::
+::::
+
+## Cloud Skewness
+:::: {.columns}
+::: {.column width="47%"}
+![Skewness of Labels (Dim 1)](Plots/label-skew1.png)
+:::
+::: {.column width="47%"}
+![Skewness of Labels (Dim 2)](Plots/label-skew2.png)
+:::
+::::
+
+## Cloud Kurtosis
+:::: {.columns}
+::: {.column width="47%"}
+![Kurtosis of Labels (Dim 1)](Plots/label-kurt1.png)
+:::
+::: {.column width="47%"}
+![Kurtosis of Labels (Dim 2)](Plots/label-kurt2.png)
+:::
+::::
+::::

### 2025-05-06 Old/make.sim.plot.R

@@ -1,4 +1,5 @@
-make.sim.plot <- function(x, d1, d2, c = "black", l = 0.6, s = 6) {
+make.sim.plot <- function(x, d1, d2, c = "black", 
+                          l = 1, r = 1, t = 1, b = 1, s = 6) {
    p <- ggplot(data = x, aes(x = x[, d1], y = x[, d2]))
    p <- p + geom_vline(xintercept = 0, color = "gray")
    p <- p + geom_hline(yintercept = 0, color = "gray")
@@ -11,6 +12,6 @@ make.sim.plot <- function(x, d1, d2, c = "black", l = 0.6, s = 6) {
    p <- p + theme(axis.text = element_text(size = 20), 
                   axis.title = element_text(size = 24))
    p <- p + labs(x = paste("Dim.", d1), y = paste("Dim", d2))
-   p <- p + ylim(-l, l) + xlim(-l, l)
+   p <- p + ylim(-b, t) + xlim(-l, r)
    return(p)
 }

### 2025-05-06 demog.dat.R

@@ -1,0 +1,98 @@
+demog.dat <- function() {
+   library(haven)
+   x <- read_dta("C:/Users/Omar Lizardo/Google Drive/MISC DATA SOURCES/SSI-2012/SSI2012.dta", col_select = c("id", "nodipdeg", "hsged", "somcol", "aadeg", 
+                                "bach", "ma", "docprof", "raceeth", 
+                                "female", "age", "percclass", "incmid",
+                                "region", "parented", "empstat")) %>% 
+      rename(parcoll = parented) %>% 
+      mutate(educ = case_when(nodipdeg == 1 ~ 0 ,                          
+                              hsged == 1 ~ 1,
+                              aadeg == 1 ~ 2,
+                              somcol == 1 ~ 3,
+                              bach == 1 ~ 4,
+                              ma == 1 ~ 5,
+                              docprof == 1 ~ 6),
+             region = case_when(region == 1 ~ 1,
+                                region == 2 ~ 1,
+                                region == 3 ~ 2,
+                                region == 4 ~ 3,
+                                region == 5 ~ 4,
+                                region == 6 ~ 4,
+                                region == 7 ~ 4,
+                                region == 8 ~ 5,
+                                region == 9 ~ 6),
+             race = factor(raceeth, labels = c("Asian", 
+                                               "Black", 
+                                               "Hisp.", 
+                                               "White", 
+                                               "Mult.", 
+                                               "Other")),
+             age = factor(age, labels = c("18 – 19",
+                                          "20 – 24",
+                                          "25 – 29",
+                                          "30 – 34",
+                                          "35 – 39",
+                                          "40 – 44",
+                                          "45 – 49",
+                                          "50 – 54",
+                                          "55 – 59",
+                                          "60 – 64",
+                                          "65 – 69",
+                                          "70 – 74",
+                                          "75 – 79",
+                                          "80+"), ordered = TRUE),
+             subjclass = factor(percclass, labels = c("Lower",
+                                                    "Working",
+                                                    "Middle",
+                                                    "Upper")),
+             objclass = case_when(incmid == 5000 | incmid == 15000 ~ 1,
+                                  incmid == 25000 | incmid == 35000 ~ 2, 
+                                  incmid == 45000 | incmid == 55000 | 
+                                  incmid == 65000 ~ 3,
+                                  incmid == 75000 | incmid == 85000 | 
[…]

### 2025-05-06 make.fuzz.plot.R

@@ -1,27 +1,35 @@
-make.fuzz.plot <- function(x, w, d1, d2, objs,  
-                           xlt = 1.25, xlb = 1.25, ylt = 1.25, ylb = 1.25, 
-                           pa = 0.15, ls = 4,
+make.fuzz.plot <- function(x, w, z, d1, d2, objs,  
+                           l = 1.25, r = 1.25, t = 1.25, b = 1.25, 
+                           pa = 0.15, ls = 4, bns = 4,
                            seed = 125) {
    x <- filter(x, col.obj %in% objs) 
-   w <- filter(w, col.obj %in% objs) 
+   w <- filter(w, col.obj %in% objs)
+   z <- filter(z, col.obj %in% objs) 
    p <- ggplot(data = x, aes(x[, d1], x[, d2]))
    p <- p + geom_vline(xintercept = 0, color = "gray")
    p <- p + geom_hline(yintercept = 0, color = "gray")
+   p <- p + geom_jitter(aes(fill = col.obj, color = col.obj), 
+                        alpha = pa, size = 1)  
    p <- p + stat_density_2d(geom = "polygon", 
-                            aes(alpha=after_stat(level), fill = col.obj, color = col.obj))
-   p <- p + geom_jitter(aes(fill = col.obj, color = col.obj), alpha = pa, size = 2)    
+                            aes(alpha=after_stat(level), 
+                                fill = col.obj, color = col.obj), bins = bns)
    p <- p + geom_text_repel(data = w, aes(w[, d1], w[, d2]),
-                      label = rownames(w), color = "darkblue", fontface = "bold", size = ls)
-   p <- p + xlim(-xlb, xlt) + ylim(-ylb, ylt) 
+                      label = rownames(w),  color = "darkblue",
+                      fontface = "bold", size = ls)
+   p <- p + geom_point(data = z, aes(z[, d1], z[, d2], shape = col.obj), 
+                       size = 4, color = "darkred")
+   p <- p + ylim(-b, t) + xlim(-l, r)
    p <- p + labs(x = paste("Dim.", d1), y = paste("Dim", d2))
    set.seed(seed)
    c <- sample(cols, length(objs))
    p <- p + scale_color_manual(values = c)
    p <- p + scale_fill_manual(values = c)
    p <- p + theme_minimal() 
+   p <- p + guides(color = "none", shape = "none", alpha = "none")
    p <- p + theme(axis.text = element_text(size = 20), 
                   axis.title = element_text(size = 24),
-                  legend.position = "none")
[…]

### 2025-05-06 old-stuff-slide.R

@@ -1,64 +1,0 @@
-<!--
-   
-   ## Correspondence Plot of Genre Column Scores
-   ![First and Second Dimensions](Plots/ca-genre-col12.png)
-
-## Correspondence Plot of Genre Column Scores
-![First and Third Dimensions](Plots/ca-genre-col13.png)
-
-## Correspondence Plot of Genre Column Scores
-![First and Fourth Dimensions](Plots/ca-genre-col14.png)
-
-## Correspondence Plot of Label Column Scores
-![First and Second Dimensions](Plots/ca-label-col12.png)
-
-## Correspondence Plot of Label Column Scores
-![First and Third Dimensions](Plots/ca-label-col13.png)
-
-## Correspondence Plot of Label Column Scores
-![First and Fourth Dimensions](Plots/ca-label-col14.png)
-
-## Correspondence Plot of Genre Column Scores
-![First and Second Dimensions](Plots/genre-sim-dens12.png)
-
-## Correspondence Plot of Label Column Scores
-![First and Second Dimensions](Plots/label-sim-dens12.png)
-
-
-## Correspondence Plot of Genre Clouds
-![First and Third Dimensions](Plots/genre-proto13.png)
-
-## Correspondence Plot of Genre Clouds
-![First and Fourth Dimensions](Plots/genre-proto14.png)
-
-## Correspondence Plot of Label Clouds
-![First and Second Dimensions](Plots/label-proto12-1.png)
-
-## Correspondence Plot of Label Clouds
-![First and Second Dimensions](Plots/label-proto12-2.png)
-
-## Correspondence Plot of Label Clouds
-![First and Third Dimensions](Plots/label-proto13.png)
-
-## Correspondence Plot of Label Clouds
-![First and Fourth Dimensions](Plots/label-proto14.png)
-
-## Genre Ridge Plot
-![First Dimension](Plots/genre-ridge-dim1.png)
-
-## Genre Ridge Plot
-![Second Dimension](Plots/genre-ridge-dim2.png)
-
-## Genre Ridge Plot
-![Third Dimension](Plots/genre-ridge-dim3.png)
-
-## Label Ridge Plot
-![First Dimension](Plots/label-ridge-dim1.png)
-
-## Label Ridge Plot
-![Second Dimension](Plots/label-ridge-dim2.png)
-
-## Label Ridge Plot
-![Third Dimension](Plots/label-ridge-dim3.png)
-
--->

### 2025-05-06 old-stuff1.R

@@ -1,342 +1,0 @@
-```{r Data Examples (Two Mode)}
-id1 <- "id_236"
-id2 <- "id_1114"
-id3 <- "id_2002"
-ex.A <- ind.mat[[id1]]
-p <- ggcorrplot(t(ex.A), lab = TRUE, lab_size = 6)
-p <- p + theme(legend.position = "none", 
-               axis.text.x = element_text(hjust = -0.2, size = 16),
-               axis.text.y = element_text(size = 16))  
-p <- p + scale_x_discrete(position = "top") + scale_y_discrete(limits=rev)
-p <- p + ggtitle(id1)
-p <- p + theme(title = element_text(size = 24))
-png(file = here("Plots", "data-ex1.png"), width=700, height=700)
-p
-dev.off()
-
-ex.A <- ind.mat[[id2]]
-p <- ggcorrplot(t(ex.A), lab = TRUE, lab_size = 6)
-p <- p + theme(legend.position = "none", 
-               axis.text.x = element_text(hjust = -0.2, size = 16),
-               axis.text.y = element_text(size = 16))  
-p <- p + scale_x_discrete(position = "top") + scale_y_discrete(limits=rev)
-p <- p + ggtitle(id2)
-p <- p + theme(title = element_text(size = 24))
-png(file = here("Plots", "data-ex2.png"), width=700, height=700)
-p
-dev.off()
-ex.A <- ind.mat[[id3]]
-p <- ggcorrplot(t(ex.A), lab = TRUE, lab_size = 6)
-p <- p + theme(legend.position = "none", 
-               axis.text.x = element_text(hjust = -0.2, size = 16),
-               axis.text.y = element_text(size = 16))  
-p <- p + scale_x_discrete(position = "top") + scale_y_discrete(limits=rev)
-p <- p + ggtitle(id3)
-p <- p + theme(title = element_text(size = 24))
-png(file = here("Plots", "data-ex3.png"), width=700, height=700)
-p
-dev.off()
-```
-
-
-```{r Data Examples (Genre Projections)}
-ex.A <- filter(row.stack.d, id == id1) %>% 
-   select(-c(id, genre))  
-rownames(ex.A) <- gsub(".184", "", rownames(ex.A))
-p <- ggcorrplot(t(ex.A), lab = TRUE, lab_size = 6,
-                ggtheme = ggplot2::theme_minimal(), colors = rep("white", 3))
-p <- p + theme(legend.position = "none", 
[…]

### 2025-05-08 analysis-bb.qmd
do it

@@
 ```{r setup, include=FALSE}
+   library(backbone)
    library(conflicted)
@@
    library(paletteer)
+   library(stringr)
    cols <- paletteer_dynamic("cartography::multi.pal", 20)
@@
    conflicts_prefer(dplyr::select)
-   source(here("make.sim.plot.R"))
    source(here("make.fuzz.plot.R"))
@@
    den <- rowSums(dat[,2:301])/300
-   bad.den <- which(den > .95 | den < 0.05)
+   bad.den <- which(den > .9 | den < 0.1)
    dat2 <- dat[-c(bad.den), 2:301]
@@
                   axis.title = element_text(size = 22))
-   png(file = here("Plots", "scree-genres.png"), width=300, height=600)
+   png(file = here("Plots", "scree-genres.png"), width=500, height=600)
    fviz_eig(CA.r, ncp = 6) + stuff + ggtitle("") + ylim(0, 12) + 
@@
    dev.off()
-   png(file = here("Plots", "scree-labels.png"), width=300, height=600)
+   png(file = here("Plots", "scree-labels.png"), width=500, height=600)
    fviz_eig(CA.c, ncp = 6) + stuff + ggtitle("") + ylim(0, 12) + 
@@
       row.lab.dat <- make.plot.dat(CA.c$row$coord) #label row scores
+   ind.gen.sup <- CA.r$quali.sup$coord %>% 
+      data.frame() %>% 
+      slice(21:nrow(CA.r$quali.sup$coord)) 
+   ind.gen.sup$id_char <- str_sub(rownames(ind.gen.sup), 4, -1)
+   ind.lab.sup <- CA.c$quali.sup$coord %>% 
+      data.frame() %>% 
+      slice(21:nrow(CA.c$quali.sup$coord)) 
+   ind.lab.sup$id_char <- str_sub(rownames(ind.lab.sup), 4, -1)
 ```
@@
       plot.name <- paste(paste("data-ex-af", k, sep = ""), ".png", sep = "")
-      png(file = here("Plots", plot.name), width=700, height=700)
+      png(file = here("Plots", plot.name), width=800, height=700)
       make.aff.plot(ind.mat[[id]])
@@
    png(file = here("Plots", "label-proto-ex1.png"), width=w, height=h)
-      make.fuzz.plot(row.lab.dat, sup.lab.dat, bns = 6, ls = 6,
+      make.fuzz.plot(row.lab.dat, col.lab.dat, sup.lab.dat, bns = 6, ls = 6,
                      1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 2,
@@
    png(file = here("Plots", "label-proto-ex2.png"), width=w, height=h)
-      make.fuzz.plot(row.lab.dat, sup.lab.dat, bns = 6, ls = 6,
+      make.fuzz.plot(row.lab.dat, col.lab.dat, sup.lab.dat, bns = 6, ls = 6,
                      1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 2,
@@
    png(file = here("Plots", "label-proto-ex3.png"), width=w, height=h)
-      make.fuzz.plot(row.lab.dat, sup.lab.dat, bns = 6, ls = 6,
+      make.fuzz.plot(row.lab.dat, col.lab.dat, sup.lab.dat, bns = 6, ls = 6,
                      1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 2,
@@
    png(file = here("Plots", "label-proto-ex4.png"), width=w, height=h)
-      make.fuzz.plot(row.lab.dat, sup.lab.dat, bns = 6, ls = 6,
+      make.fuzz.plot(row.lab.dat, col.lab.dat, sup.lab.dat, bns = 6, ls = 6,
                      1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 2,
@@
    png(file = here("Plots", "label-proto-ex5.png"), width=w, height=h)
-      make.fuzz.plot(row.lab.dat, sup.lab.dat, bns = 6, ls = 6,
+      make.fuzz.plot(row.lab.dat, col.lab.dat, sup.lab.dat, bns = 6, ls = 6,
                      1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 2,
@@
 ```{r Genre and Label Subcloud Variance}
-   w <- 600
-   h <- 700
-   var.g <- make.ridge.dat(sup.gen.dat, row.gen.dat) %>% 
+   w <- 800
+   h <- 800
+   make.var.dat <- function(x, w) {
+      z <- make.ridge.dat(x, w) %>% 
       mutate(dist.cent.1 = (Dim.1 - Prot.1)^2) %>% 
@@
       summarize(across(c(var), mean))
-   var.l <- make.ridge.dat(sup.lab.dat, row.lab.dat) %>% 
-      mutate(dist.cent.1 = (Dim.1 - Prot.1)^2) %>% 
-      mutate(dist.cent.2 = (Dim.2 - Prot.2)^2) %>% 
-      mutate(dist.cent.3 = (Dim.3 - Prot.3)^2) %>% 
-      mutate(var = dist.cent.1 + dist.cent.2 + dist.cent.3) %>% 
-      mutate(std = sqrt(var)) %>% 
-      select(c("var", "std", "col.obj")) %>% 
-      group_by(col.obj) %>% 
-      summarize(across(c(var), mean))
-   make.bar.plot <- function(w) {
+      return(z)
+      }
+   make.var.plot <- function(w, ps = 8, seed = 125) {
       p <- ggplot(data = w, aes(y = reorder(col.obj, var), 
@@
       p <- p + theme_ridges() + labs(y = "", x = "")
-      p <- p + theme(axis.text = element_text(size = 18))
+      p <- p + theme(axis.text = element_text(size = 20))
+      set.seed(seed)
+      colors <- sample(cols, length(unique(w$col.obj)))
+      p <- p + scale_color_manual(values = colors)
+      p <- p + scale_fill_manual(values = colors)
       p
    }   
+   make.var.plot.demog <- function(w, ps = 8, seed = 125) {
+      p <- ggplot(data = w, aes(y = col.obj, 
+                                x = var, color = col.obj, group = col.obj))
+      p <- p + geom_point(stat = "identity", size = 8)
+      p <- p + scale_color_manual(values = cols)
+      p <- p + guides(color = "none")
+      p <- p + theme_ridges() + labs(y = "", x = "")
+      p <- p + theme(axis.text = element_text(size = 20))
+      set.seed(seed)
+      colors <- sample(cols, length(unique(w$col.obj)))
+      p <- p + scale_color_manual(values = colors)
+      p <- p + scale_fill_manual(values = colors)
+      p
+      } 
+   var.g <- make.var.dat(sup.gen.dat, row.gen.dat) 
+   var.l <- make.var.dat(sup.lab.dat, row.lab.dat) 
    png(file = here("Plots", "genre-var.png"), width=w, height=h)
-   make.bar.plot(var.g) + xlim(0.75, 1.75)
+   make.var.plot(var.g, ps = 10) + xlim(0.75, 1.75)
    dev.off()
    png(file = here("Plots", "label-var.png"), width=w, height=h)
-   make.bar.plot(var.l) + xlim(0.75, 1.75)
+   make.var.plot(var.l, ps = 10) + xlim(0.75, 1.75)
    dev.off()
@@
       rename(var = skew)
-   make.bar.plot(d) 
+   make.var.plot(d) 
    dev.off()
@@
       rename(var = kurt)
-   make.bar.plot(d)    
+   make.var.plot(d)    
    dev.off()
@@
       rename(var = kurt)
-   make.bar.plot(d) 
+   make.var.plot(d) 
    dev.off()
@@
 
-```{r}
+```{r Comparing Individual Matrices Based on Typicality}
+   library(stringr)
+   w <- 800
+   h <- 700
+   make.var.row.dat  <- function(x, w) {
+      z <- make.ridge.dat(x, w) %>% 
+      mutate(dist.cent.1 = (Dim.1 - Prot.1)^2) %>% 
+      mutate(dist.cent.2 = (Dim.2 - Prot.2)^2) %>% 
+      mutate(dist.cent.3 = (Dim.3 - Prot.3)^2) %>% 
+      mutate(var = dist.cent.1 + dist.cent.2 + dist.cent.3) %>% 
+      mutate(std = sqrt(var))
+      return(z)
+      }
+
+   ex.ind.dat <- function(x, w, z, q, p, id) {
+      a <- make.var.row.dat(x, w) %>% 
+      mutate(id_char = q$id[-p]) %>% 
+      left_join(z)
+      a <- filter(a, id_char == id) %>% 
+         select(c("col.obj", "var"))
+      return(a)
+      }
+   get.ind.var <- function(id) {
+      a <- ex.ind.dat(sup.gen.dat, row.gen.dat, ind.gen.sup, 
+                          row.stack.d, zero.rows.r,
+                          id)
+      b <- make.var.row.dat(sup.gen.dat, row.gen.dat) %>% 
+         select(c("var", "std", "col.obj")) %>% 
+         group_by(col.obj) %>% 
+         summarize(m.var =  median(var)) %>% 
+         right_join(a)
+      return(b)
+      }
+   #l.id <- ex.ind.dat(sup.lab.dat, row.lab.dat, ind.lab.sup, 
+    #                   col.stack.d, zero.rows.c,
+     #                  id.num)
+   #var.l.m <- make.var.row.dat(sup.lab.dat, row.lab.dat) %>% 
+    #  select(c("var", "std", "col.obj")) %>% 
+     # group_by(col.obj) %>% 
+      #summarize(m.var =  median(var)) %>% 
+      #right_join(l.id)
+   make.ind.var.plot <- function(w) {
+      p <- ggplot(data = w, aes(y = reorder(col.obj, var), 
+                                x = var, color = col.obj, group = col.obj))
+      p <- p + geom_point(stat = "identity", size = 8)
+      p <- p + geom_point(aes(x = m.var),
+                          stat = "identity", size = 6, shape = 3,
+                          color = "red")
+      p <- p + scale_color_manual(values = cols)
+      p <- p + guides(color = "none")
+      p <- p + theme_ridges() + labs(y = "", x = "")
+      p <- p + theme(axis.text = element_text(size = 18))
+      p
+      } 
+   png(file = here("Plots", "genre-var-id_ex1.png"), width=w, height=h)
+   make.ind.var.plot(get.ind.var("id_65"))
+   dev.off()
+   png(file = here("Plots", "data-ex-rbb-id2.png"), width=w, height=h)
+   make.aff.plot(row.bb[["id_2"]])
+   dev.off()
+   png(file = here("Plots", "genre-var-id_ex-id2.png"), width=w, height=h)
+   make.ind.var.plot(get.ind.var("id_2"))
+   dev.off()
+```
+
+```{r Demographic Data}
       source(here("demog.dat.R"))
@@
       row.gen.dat.id <- cbind(row.gen.dat, id_char = row.stack.d$id[-zero.rows.r])
-   classical.cloud <- filter(row.gen.dat.id, col.obj == "Classical")
-   classical.dat <- left_join(classical.cloud, row.gen.dat.id)
-   classical.dat <- left_join(classical.dat, demog.dat)
+      row.lab.dat.id <- cbind(row.lab.dat, id_char = col.stack.d$id[-zero.rows.c])
+   make.demog.dat <- function(w, g, d) {
+      a <- select(demog.dat, c("id_char", d))
+      b <- filter(w, col.obj == g) %>% 
+         left_join(a) 
+      return(b)
+      }
 ```
 
-```{r}
-   p <- ggplot(data = classical.dat, aes(Dim.1, Dim.2))
-   p <- p + stat_density_2d(geom = "polygon", 
-                            aes(alpha=after_stat(level)), bins = 5)
-   p
+```{r Demographic Cloud-Specific Plots}
+   source(here("make.demog.plot.R"))
+   w <- 900
+   h <- 800
+   # Education
+   png(file = here("Plots", "demog-classical-educ.png"), width=w, height=h)
+   make.demog.plot(make.demog.dat(row.gen.dat.id, "Classical", "educ.f"), 
+                    "Classical", "educ.f", r = 3)
+   dev.off()
+   png(file = here("Plots", "demog-jazz-educ.png"), width=w, height=h)
+   make.demog.plot(make.demog.dat(row.gen.dat.id, "Jazz", "educ.f"), 
+                    "Jazz", "educ.f", r = 3)
+   dev.off()
+   png(file = here("Plots", "demog-opera-educ.png"), width=w, height=h)
+   make.demog.plot(make.demog.dat(row.gen.dat.id, "Opera", "educ.f"), 
+                    "Opera", "educ.f", r = 3)
+   dev.off()
+
+   # Race
+   png(file = here("Plots", "demog-rap-race.png"), width=w, height=h)
+   make.demog.plot(make.demog.dat(row.gen.dat.id, "Rap", "race"), 
+                    "Rap", "race", r = 3)
+   dev.off()
+   png(file = here("Plots", "demog-jazz-race.png"), width=w, height=h)
+   make.demog.plot(make.demog.dat(row.gen.dat.id, "Jazz", "race"), 
+                    "Jazz", "race", r = 3)
+   dev.off()
+   png(file = here("Plots", "demog-folk-race.png"), width=w, height=h)
+   make.demog.plot(make.demog.dat(row.gen.dat.id, "Folk", "race"), 
+                    "Folk", "race", r = 3, b = 3)
+   dev.off()
+
+   # Age
+   png(file = here("Plots", "demog-rap-age.png"), width=w, height=h)
+   make.demog.plot(make.demog.dat(row.gen.dat.id, "Rap", "age"), 
+                    "Rap", "age", r = 3)   
+   dev.off()
+   png(file = here("Plots", "demog-metal-age.png"), width=w, height=h)
+   make.demog.plot(make.demog.dat(row.gen.dat.id, "Metal", "age"), 
+                    "Metal", "age", r = 3)   
+   dev.off()
+   png(file = here("Plots", "demog-altrock-age.png"), width=w, height=h)
+   make.demog.plot(make.demog.dat(row.gen.dat.id, "Alt_Rock", "age"), 
+                    "Alt_Rock", "age", r = 3)   
+   dev.off()
+
+   # Class
+   png(file = here("Plots", "demog-lower-subjclass.png"), width=w, height=h)
+   make.demog.plot(make.demog.dat(row.lab.dat.id, "Lower_Class", "subjclass"), 
+                    "Lower_Class", "subjclass", r = 3)   
+   dev.off()
+   png(file = here("Plots", "demog-working-subjclass.png"), width=w, height=h)
+   make.demog.plot(make.demog.dat(row.lab.dat.id, "Working_Class", "subjclass"), 
+                    "Working_Class", "subjclass", r = 3)   
+   dev.off()
+   png(file = here("Plots", "demog-middle-subjclass.png"), width=w, height=h)
+   make.demog.plot(make.demog.dat(row.lab.dat.id, "Middle_Class", "subjclass"), 
+                    "Middle_Class", "subjclass", r = 3)   
+   dev.off()
+   png(file = here("Plots", "demog-upper-subjclass.png"), width=w, height=h)
+   make.demog.plot(make.demog.dat(row.lab.dat.id, "Upper_Class", "subjclass"), 
+                    "Upper_Class", "subjclass", r = 3)   
+   dev.off()
 ```
+
+```{r Demographic Specific Cloud Variance Plots}
+   h <- 700
+   w <- 700
+   make.demog.var.dat <- function(w, g, d) {
+      a <- make.demog.dat(w, g, d) 
+      b <- a %>% 
+         group_by_at(8) %>% 
+         summarize(across(1:3, mean)) %>% 
+         rename(Prot.1 = Dim.1, Prot.2 = Dim.2, Prot.3 = Dim.3) %>% 
+         right_join(a) %>% 
+         mutate(dist.cent.1 = (Dim.1 - Prot.1)^2) %>% 
+         mutate(dist.cent.2 = (Dim.2 - Prot.2)^2) %>% 
+         mutate(dist.cent.3 = (Dim.3 - Prot.3)^2) %>% 
+         mutate(var = dist.cent.1 + dist.cent.2 + dist.cent.3) %>% 
+         group_by_at(1) %>% 
+         summarize(var = mean(var)) %>% 
+         rename(col.obj = 1)
+      return(b)
+   }
+   # Education
+   png(file = here("Plots", "demog-classical-educ-var.png"), width=w, height=h)
+   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id, 
+                                          "Classical", "educ.f"), ps = 12) 
+   dev.off()
+   png(file = here("Plots", "demog-jazz-educ-var.png"), width=w, height=h)
+   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id,
+                                          "Jazz", "educ.f"), ps = 12) 
+   dev.off()
+   png(file = here("Plots", "demog-opera-educ-var.png"), width=w, height=h)
+   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id, 
+                                          "Opera", "educ.f"), ps = 12) 
+   dev.off()
+   # Race
+   png(file = here("Plots", "demog-jazz-race-var.png"), width=w, height=h)
+   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id, 
+                                          "Jazz", "race"), ps = 12) 
+   dev.off()
+   png(file = here("Plots", "demog-rap-race-var.png"), width=w, height=h)
+   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id, 
+                                          "Rap", "race"), ps = 12) 
+   dev.off()
+   png(file = here("Plots", "demog-folk-race-var.png"), width=w, height=h)
+   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id, 
+                                          "Folk", "race"), ps = 12) 
+   dev.off()
+   # Age
+   png(file = here("Plots", "demog-metal-age-var.png"), width=w, height=h)
+   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id, 
+                                          "Metal", "age"), ps = 12) 
+   dev.off()
+   png(file = here("Plots", "demog-rap-age-var.png"), width=w, height=h)
+   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id, 
+                                          "Rap", "age"), ps = 12) 
+   dev.off()
+   png(file = here("Plots", "demog-altrock-age-var.png"), width=w, height=h)
+   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id, 
+                                          "Alt_Rock", "age"), ps = 12) 
+   dev.off()
+   # Class
+   png(file = here("Plots", "demog-lower-subjclass-var.png"), width=w, height=h)
+   make.var.plot.demog(make.demog.var.dat(row.lab.dat.id, 
+                                          "Lower_Class", "subjclass"), ps = 12) 
+   dev.off()
+   png(file = here("Plots", "demog-working-subjclass-var.png"), width=w, height=h)
+   make.var.plot.demog(make.demog.var.dat(row.lab.dat.id, 
+                                          "Working_Class", "subjclass"), ps = 12) 
+   dev.off()
+   png(file = here("Plots", "demog-middle-subjclass-var.png"), width=w, height=h)
+   make.var.plot.demog(make.demog.var.dat(row.lab.dat.id, 
+                                          "Middle_Class", "subjclass"), ps = 12) 
+   dev.off()
+   png(file = here("Plots", "demog-upper-subjclass-var.png"), width=w, height=h)
+   make.var.plot.demog(make.demog.var.dat(row.lab.dat.id, 
+                                          "Upper_Class", "subjclass"), ps = 12) 
+   dev.off()
+```

### 2025-05-08 heidelberg-slides.qmd
do it

@@
 ---
-title: "Musical Genres as Fuzzy Categories"
+title: "Musical Genres and Socio-Demographic Labels as Fuzzy Categories"
 subtitle: ""
@@
 
-##
+## Genres and Categories
+
+- Notion of Genre Fundamental to the Sociology of Taste
+- Perennially Contested Category
+- Basic Problem:
+  - Our intuitions imply **fuzziness** and **distributional** thinking
+  - But our methods mostly rely on **crisp** classifications and **central tendencies**
+
+:::aside
+DiMaggio, P. (1987). Classification in art. *American Sociological Review*, 440-455.
+
+Lena, J. C. (2015). Genre: Relational approaches to the sociology of music. In *The Routledge International Handbook of the Sociology of Art and Culture* (pp. 149-160). Routledge.
+:::
+
+## Genres and Categories
+
+- Notion of **Genre** Fundamental to the Sociology of Taste
+- Perennially Contested Category
+- Recent work on **Measuring Culture** has begun to make headway on the issue
+  - Relational approaches applying network methods
+    - Focus on fuzziness and overlapping categories
+  - **Geometric Data Analysis**
+    - Focus on distributions of judgments in a relational space
+
+:::aside
+Le Roux, B., & Rouanet, H. (2004). *Geometric Data Analysis*. Springer Science & Business Media.
+
+Vlegels, J., & Lievens, J. (2017). Music classification, genres, and taste patterns: A ground-up network analysis on the clustering of artist preferences. *Poetics*, 60, 76-89.
+
+Lizardo, O. (2024). From Macrogenres to microgenres via relationality. *Poetics*, 102, 101868.
+:::
+
+## Categories as Clusters of Associations
+
+- Recent conceptual and methodological work uses relational imagery to deconstruct categories as clusters of associations between elements
+  - **Relational Class Analysis**
+  - **Correlational Class Analysis**
+  - Measuring **Schemas** from Survey and Discourse Data
+- Folk categories are revealed by measuring "what goes with what" at the level of personal culture
+- Focus on *heterogeneity* across clusters of individuals and items
+
+:::aside
+Boutyline, A., & Soter, L. K. (2021). Cultural schemas: What they are, how to find them, and what to do once you’ve caught one. *American Sociological Review*, 86(4), 728-758.
+
+Hunzaker, M. F., & Valentino, L. (2019). Mapping cultural schemas: From theory to method. *American Sociological Review*, 84(5), 950-981.
+
+Goldberg, A., & Singell, M. H. (2024). The sociology of interpretation. *Annual Review of Sociology*, 50.
+:::
+
+## The sociology of Taste
+-  Focused on the dual linkage between two systems of categories:
+  - Genre categories developed in fields of cultural production (scenes, industries)
+  - Social categories endowed with ritual potency and social validity constitutive of status orders 
+- Basic intuition:
+  - Genres are defined by the categories of people who choose them
+  - Categories of persons are defined by the genres they choose
+- Duality!
+
+:::aside
+Breiger, R. L. (1974). The duality of persons and groups. *Social Forces*, 53(2), 181-190.
+
+Bryson, B. (1996). " Anything but heavy metal": Symbolic exclusion and musical dislikes. *American Sociological Review*, 884-899.
+
+Lizardo, O. and Skiles, S., 2016. Cultural objects as prisms: Perceived audience composition of musical genres as a resource for symbolic exclusion. *Socius*, 2, p.2378023116641695.
+:::
+
+## The sociology of Taste
+- We can apply lessons learned from the **relational**, **geometric**, and **schematic** turns in measuring culture to the problem of genre in the sociology of taste
+- Investigate folk schemas regarding the (explicit) associations between genre categories and categories of people
+- Focus on heterogeneity and the distribution of judgments across the social space
 
 ## Data
+- Data on cultural tastes among a weighted representative sample of Americans collected in Summer of 2012
+  - $N = 2,250$
+- Like GSS 1993 survey included items assessing respondents’ likes and dislikes for 20 categories of musical style**
+  -  Inclusion of a **perceptual** module
+  - Which of these characteristics describe the typical fans of [genre category] music? Choose all that apply.
+
+:::aside
+  ** Classical/symphony and chamber, opera/operetta, jazz, Broadway Musicals/Show tunes, Mood/Easy Listening, Big Band/Swing, Classic Rock/Oldies, Country, Bluegrass, Folk, Hymns/Gospel, Latin/Spanish/Salsa, Rap/Hip Hop, Blues/R&B, Reggae, Pop/Top 40, Contemporary Rock, Indie/Alternative Rock, EDM, and Heavy Metal
+:::
+
+## Data
+- Data on cultural tastes among a (weighted) representative sample of Americans collected in Summer of 2012
+  - $N = 2,250$
+- Like GSS 1993 survey included items assessing respondents’ likes and dislikes for 20 categories of musical style**
+  -  Inclusion of a **perceptual** module
+  - Which of these characteristics describe the typical fans of [genre category] music? Choose all that apply.***
+
+:::aside
+  *** Male, Female, Young, Middle-aged, Old, College Educated, No College Degree, Asian, Black, Hispanic, White, Lower Class, Working Class, Middle Class, and Upper Class
+:::
+
+## Approach
 - We can treat the association data provided by respondents as **cognitive two-mode data**
   - In analogy with Krackhardt-style data for one-mode networks
-  - Persons provide *perceived* associations between genres and social labels
+  - Persons provide *perceived* associations between **musical genres** and **social labels**
+- Use relational techniques to extract the "backbone" of the perceived associations
+  - Dual Projection**
+  - Backbone extraction***
+
+:::aside
+** Everett, M. G., & Borgatti, S. P. (2013). The dual-projection approach for two-mode networks. *Social Networks*, 35(2), 204-210.
+
+*** Neal, Z. (2014). The backbone of bipartite projections: Inferring relationships from co-authorship, co-sponsorship, co-attendance and other co-behaviors. *Social Networks*, 39, 84-97.
+:::
+
+## Approach
+- We can treat the association data provided by respondents as **cognitive two-mode data**
+  - In analogy with Krackhardt-style data for one-mode networks
+  - Persons provide *perceived* associations between **musical genres** and **social labels**
+- Model the backbone of the person-specific projected networks jointly using: 
+  - Stacked **Correspondence Analysis****
+  - Geometric Data Analysis of the various **clouds of individuals*****
+
+:::aside
+** Batchelder, W. H., Kumbasar, E., & Boyd, J. P. (1997). Consensus analysis of three‐way social network data. *Journal of Mathematical Sociology*, 22(1), 29-58.
+
+*** Le Roux, B., & Rouanet, H. (2004). *Geometric Data Analysis*. Springer Science & Business Media.
+
+:::
 
@@
 ## Stacked CA Analyses
-- Three sets of scores:
+- Three sets of **scores**:
   - row-scores are **person-specific** judgments of the relative similarity of genres and labels
@@
 
-## Mondo Breiger Approach
+## Stacked CA Analyses
+- Three sets of **scores**:
+  - row-scores are **person-specific** judgments of the relative similarity of genres and labels
+  - column-scores represent the **aggregate judgment** of the relative similarity of genres (with respect to labels) and labels (with respect to genres)
+  - Supplementary scores for genres and labels represent the **centroid** of the cloud of person-specific judgments
+- Multiple **clouds of individuals**
+  - Projected into genre space (one cloud per genre)
+  - Projected into label space (one cloud per label)
+    - Individual specific clouds (across all genres and labels)
+    - Sub-clouds in each space based on individual characteristics
+
+## Mondo Breiger Approach**
 
@@
 
-## Mondo Breiger Approach
+:::aside
+Lee, M., & Martin, J. L. (2018). Doorway to the dharma of duality. *Poetics*, 68, 18-30.
+:::
+
+## Mondo Breiger Approach**
 
@@
   - $l^{(p)}_{kk}$ records the number of times individual $p$ associates genre $i$ with a label
+
+:::aside
+Lee, M., & Martin, J. L. (2018). Doorway to the dharma of duality. *Poetics*, 68, 18-30.
+:::
+
+## Mondo Breiger Approach**
+
+- Each individual provides a "personal" two mode network of genres by social labels with corresponding affiliation matrix $\mathbf{A}(p)$
+  - $a^{(p)}_{gl} = 1$ if individual $p$ associates genre $g$ with label $l$
+- We take each dual projection and transform them:
+  - $\mathbf{G}(p) \rightarrow \mathbf{G}^{*}(p)$
+  - $\mathbf{L}(p) \rightarrow \mathbf{L}^{*}(p)$
+- Where $\mathbf{G}(p)^{*}$ and $\mathbf{L}(p)^{*}$ are the (binarized) **backbone of the network projections**** using the **disparity filter*****
+
+:::aside
+*** Neal, Z. (2014). The backbone of bipartite projections: Inferring relationships from co-authorship, co-sponsorship, co-attendance and other co-behaviors. *Social Networks*, 39, 84-97.
+
+*** Serrano, M. Á., Boguná, M., & Vespignani, A. (2009). Extracting the multiscale backbone of complex weighted networks. *Proceedings of the National Academy of Sciences*, 106(16), 6483-6488.
+
+***
+:::
 
@@
 
-##  Stacked Matrices Examples
+## 
 :::: {.columns}
 ::: {.column width="50%"}
-![id_65 and id_236 (Rows)](Plots/data-ex-stack1.png)
+![id_65 and id_236 (Stacked Rows)](Plots/data-ex-stack1.png)
 :::
 ::: {.column width="50%"}
-![id_65 and id_236 (Columns)](Plots/data-ex-stack2.png)
+![id_65 and id_236 (Stacked Columns)](Plots/data-ex-stack2.png)
 :::
@@
 
+##
+![Mondo Breiger Workflow](mondo-workflow.png)
+
 ## CA Eigenvalue Scree Plot
 :::: {.columns}
-::: {.column width="50%"}
-![Stacked Genres](Plots/scree-genres.png)
+::: {.column width="45%"}
+![Genres](Plots/scree-genres.png)
 :::
-::: {.column width="50%"}
-![Stacked Labels](Plots/scree-labels.png)
+::: {.column width="45%"}
+![Labels](Plots/scree-labels.png)
 :::
@@
 ::::
+
+## Individual Genre Cloud Typicality
+:::: {.columns}
+::: {.column width="50%"}
+![Affiliation Matrix for id_63](Plots/data-ex-rbb1.png)
+:::
+::: {.column width="50%"}
+![Genre Profile Distance from Centroid for id_63](Plots/genre-var-id_ex1.png)
+:::
 ::::
+
+## Individual Genre Cloud Typicality
+:::: {.columns}
+::: {.column width="50%"}
+![Affiliation Matrix for id_2](Plots/data-ex-rbb-id2.png)
+:::
+::: {.column width="50%"}
+![Genre Profile Distance from Centroid for id_2](Plots/genre-var-id_ex-id2.png)
+:::
+::::
+
+## Group-Specific Genre Clouds
+:::: {.columns}
+::: {.column width="55%"}
+![](Plots/demog-classical-educ.png)
+:::
+::: {.column width="45%"}
+![Variance of Education Clouds](Plots/demog-classical-educ-var.png)
+:::
+::::
+
+## Group-Specific Genre Clouds
+:::: {.columns}
+::: {.column width="55%"}
+![](Plots/demog-opera-educ.png)
+:::
+::: {.column width="45%"}
+![Variance of Education Clouds](Plots/demog-opera-educ-var.png)
+:::
+::::
+
+## Group-Specific Genre Clouds
+:::: {.columns}
+::: {.column width="55%"}
+![](Plots/demog-jazz-educ.png)
+:::
+::: {.column width="45%"}
+![Variance of Education Clouds](Plots/demog-jazz-educ-var.png)
+:::
+::::
+
+## Group-Specific Genre Clouds
+:::: {.columns}
+::: {.column width="55%"}
+![](Plots/demog-jazz-race.png)
+:::
+::: {.column width="45%"}
+![Variance of Race/Ethnic I.D. Clouds](Plots/demog-jazz-race-var.png)
+:::
+::::
+
+## Group-Specific Genre Clouds
+:::: {.columns}
+::: {.column width="55%"}
+![](Plots/demog-rap-race.png)
+:::
+::: {.column width="45%"}
+![Variance of Race/Ethnic I.D. Clouds](Plots/demog-rap-race-var.png)
+:::
+::::
+
+## Group-Specific Genre Clouds
+:::: {.columns}
+::: {.column width="55%"}
+![](Plots/demog-folk-race.png)
+:::
+::: {.column width="45%"}
+![Variance of Race/Ethnic I.D. Clouds](Plots/demog-folk-race-var.png)
+:::
+::::
+
+## Group-Specific Genre Clouds
+:::: {.columns}
+::: {.column width="55%"}
+![](Plots/demog-rap-age.png)
+:::
+::: {.column width="45%"}
+![Variance of Age Clouds](Plots/demog-rap-age-var.png)
+:::
+::::
+
+## Group-Specific Genre Clouds
+:::: {.columns}
+::: {.column width="55%"}
+![](Plots/demog-metal-age.png)
+:::
+::: {.column width="45%"}
+![Variance of Age Clouds](Plots/demog-metal-age-var.png)
+:::
+::::
+
+## Group-Specific Genre Clouds
+:::: {.columns}
+::: {.column width="55%"}
+![](Plots/demog-altrock-age.png)
+:::
+::: {.column width="45%"}
+![Variance of Age Clouds](Plots/demog-altrock-age-var.png)
+:::
+::::
+
+## Group-Specific Genre Clouds
+:::: {.columns}
+::: {.column width="55%"}
+![](Plots/demog-lower-subjclass.png)
+:::
+::: {.column width="45%"}
+![Variance of Age Clouds](Plots/demog-lower-subjclass-var.png)
+:::
+::::
+
+## Group-Specific Genre Clouds
+:::: {.columns}
+::: {.column width="55%"}
+![](Plots/demog-working-subjclass.png)
+:::
+::: {.column width="45%"}
+![Variance of Age Clouds](Plots/demog-working-subjclass-var.png)
+:::
+::::
+
+## Group-Specific Genre Clouds
+:::: {.columns}
+::: {.column width="55%"}
+![](Plots/demog-middle-subjclass.png)
+:::
+::: {.column width="45%"}
+![Variance of Age Clouds](Plots/demog-middle-subjclass-var.png)
+:::
+::::
+
+## Group-Specific Genre Clouds
+:::: {.columns}
+::: {.column width="55%"}
+![](Plots/demog-upper-subjclass.png)
+:::
+::: {.column width="45%"}
+![Variance of Age Clouds](Plots/demog-upper-subjclass-var.png)
+:::
+::::

### 2025-05-08 demog.dat.R

@@ -77,7 +77,7 @@ demog.dat <- function() {
                                               "Some Coll.", 
                                               "Bachelors", 
                                               "Prof.Deg",
-                                              "PhD"), ordered = FALSE),
+                                              "PhD"), ordered = TRUE),
              college = if_else(educ >= 4, 1, 0),
              working = if_else(empstat == 1, 1, 0),
              student = if_else(empstat == 3, 1, 0),
@@ -90,9 +90,6 @@ demog.dat <- function() {
              mid.c = if_else(percclass == 3, 1, 0),
              lo.inc = if_else(incmid <= 25000, 1, 0)
              ) %>% 
-      dplyr::select(c("id", "educ.f", "gender", "age", "parcoll", 
-                      "incmid", "college", "working", "wrk.c", "mid.c",
-                      "student", "retired", "region.f", "lo.inc",
-                      "asn", "blk", "his", "mro"))
+      dplyr::select(c("id", "educ.f", "age", "race", "subjclass"))
    return(x)
 }

### 2025-05-08 make.demog.plot.R

@@ -1,0 +1,25 @@
+make.demog.plot <- function(x, g, d, d1 = 1, d2 = 2, seed = 125, 
+                            l = 2, r = 2, t = 2, b = 2) {
+   p <- ggplot(data = x, aes(x[, d1], x[, d2], color = x[, 8], fill = x[, 8]))
+   p <- p + geom_vline(xintercept = 0, color = "gray")
+   p <- p + geom_hline(yintercept = 0, color = "gray")
+   p <- p + geom_jitter(alpha = 0.35)
+   p <- p + stat_density_2d(geom = "polygon", aes(alpha=after_stat(level)), 
+                            bins = 6)
+   p <- p + theme_minimal()
+   p <- p + ylim(-b, t) + xlim(-l, r)
+   p <- p + labs(x = paste("Dim.", d1), y = paste("Dim", d2))
+   set.seed(seed)
+   colors <- sample(cols, length(unique(x[,8])))
+   p <- p + scale_color_manual(values = colors)
+   p <- p + scale_fill_manual(values = colors)
+   p <- p + guides(color = "none", alpha = "none")
+   p <- p + theme(axis.text = element_text(size = 20), 
+                  axis.title = element_text(size = 24),
+                  legend.position = "bottom", 
+                  legend.text = element_text(size = 18),
+                  legend.title = element_blank(),
+                  title = element_text(size = 26))
+   p <- p + ggtitle(g)
+   return(p)
+}

### 2025-05-09 analysis-bb.qmd
new stuff

@@
    dev.off()
+
+   # Education
+   png(file = here("Plots", "demog-college-educ.png"), width=w, height=h)
+   make.demog.plot(make.demog.dat(row.lab.dat.id, "College", "educ.f"), 
+                    "College", "educ.f", r = 3)   
+   dev.off()
+   png(file = here("Plots", "demog-nocollege-educ.png"), width=w, height=h)
+   make.demog.plot(make.demog.dat(row.lab.dat.id, "No_College", "educ.f"), 
+                    "No_College", "educ.f", r = 3)   
+   dev.off()
 ```
@@
    dev.off()
+
+   # Education
+   png(file = here("Plots", "demog-college-educ-var.png"), width=w, height=h)
+   make.var.plot.demog(make.demog.var.dat(row.lab.dat.id, 
+                                          "College", "educ.f"), ps = 12) 
+   dev.off()
+   png(file = here("Plots", "demog-nocollege-educ-var.png"), width=w, height=h)
+   make.var.plot.demog(make.demog.var.dat(row.lab.dat.id, 
+                                          "No_College", "educ.f"), ps = 12) 
+   dev.off()
 ```

### 2025-06-19 manuscript.tex

\documentclass[12pt]{article}
\usepackage[left=1.15in, right=1.15in, top=1in, bottom=1.5in]{geometry}
\usepackage{natbib}
\usepackage{verbatim}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{subcaption}
\bibpunct[: ]{(}{)}{;}{a}{}{,} 
\usepackage{authblk}
\renewcommand\Authfont{\normalsize}
\renewcommand\Affilfont{\footnotesize}

\begin{document}
\title{Revealing Folk Schemas of Musical Genre and Social Category Associations via Relational and Geometric Methods\thanks{Reserved for acknowledgments}}
\author[1]{Omar Lizardo\thanks{olizardo@soc.ucla.edu}}
\affil[1]{Department of Sociology, UCLA}

\renewcommand\Authands{ and }

\date{\normalsize \today}	
\maketitle

\newpage
\begin{abstract}
\end{abstract}
\newpage
\section*{Introduction}
The notion of musical genre stands as a fundamental concept within the Sociology of Taste, operating as a key organizing principle in understanding cultural consumption and preference \citep{dimaggio1987classification-758, lena2012banding-4b5, lena2008classification-1d7}. Despite its centrality, genre remains a perennially contested category \citep{lena2015relational-21f, vlegels2017music-360}. A core challenge lies in the disparity between intuitive understanding, which suggests that genres are fuzzy, overlapping, and problematic in their boundaries \citep{lizardo2024from-ddd, goldberg2016what-4e3}, and traditional sociological methodologies that often rely on crisp classifications of genre boundaries and measurements of central tendencies \citep{monk2022inequality-699}. This inherent tension has previously led to calls for either outright rejection or radical revision of the genre concept itself \citep{lena2015relational-21f}.

Recent advancements in the field of culture measurement have begun to provide promising avenues for addressing this conundrum. Specifically, relational approaches utilizing network methods and Geometric Data Analysis have emerged, focusing on the inherent fuzziness and overlapping nature of categories \citep{lizardo2024from-ddd}. These methodologies shift the analytical focus towards the distributions of judgments within a relational space \citep{puetz2017fields-f30}. Conceptually, this work employs relational imagery to deconstruct categories as clusters of associations between elements \citep{mcdonnell2024making-b02}, thereby revealing ``folk categories'' by empirically measuring what elements are perceived to ``go with what'' at the level of individual cultural understanding \citep{goldberg2018beyond-f2f}. A key benefit of these approaches is their ability to illuminate heterogeneity across clusters of individuals and cultural items \citep{goldberg2011mapping-77a, vlegels2017music-360}.

Historically, the sociology of taste has concentrated on the objective dual linkage between two primary systems of categories: Genre categories, as developed within cultural production fields like scenes and industries, and social categories, endowed with ritual potency and constitutive of status orders \citep{bourdieu1984distinction-835, bourdieu1993field-8ad, dimaggio1987classification-758, lena2012banding-4b5}. This framework operates on the basic intuition that genres are defined by the types of people who prefer them, and, conversely, categories of people are defined by the genres they choose \citep{breiger2000tool-db3, lizardo2016cultural-aaa}. However, a less common focus in research has been the direct examination of folk construals of these dual linkages, that is, how individuals subjectively perceive the connections between musical genres and social groups \citep{lizardo2016cultural-aaa}.

This paper applies insights derived from the relational, geometric, and schematic turns in measuring culture \citep{goldberg2011mapping-77a, rouanet2000geometric-a44} to the enduring problem of genre within the sociology of taste. My primary objective is to transition analytical perspectives from crisp definitions to fuzzy categories, emphasizing heterogeneity and the distribution of judgments across the social space \citep{romney1986culture-aaa}. Beyond the exclusive focus on objective linkages between genre categories and socio-demographic positions, I aim to investigate folk schemas concerning the subjective folk construals of the link between genre categories and categories of people. By exploiting the sociological duality of genres and social labels \citep{basov2017duality-24b, breiger1974duality-1d0}, I seek to extract detailed associational schemas for both. This involves combining network-analytic and geometric methods to simultaneously examine both central tendencies (centroids) and heterogeneity (variance) in these perceived associations across multiple analytical levels: individual, category, group (demographics), and the broader system.

\section*{Data and Analytic Approach}
To achieve these objectives, I analyze a comprehensive dataset on cultural tastes, collected in the Summer of 2012 from a weighted representative sample of Americans (N = 2,250) \citep{lizardo2016cultural-aaa, lizardo2015musical-8c6, lizardo2024from-ddd}. This dataset, similar to the GSS 1993 survey, includes items assessing respondents' likes, dislikes, and frequency of consumption across twenty distinct musical style categories. Crucially, this dataset incorporates a \textit{perceptual} module that prompted respondents to identify characteristics describing the typical fans of each genre category, allowing them to select all applicable traits from a predefined list of socio-demographic labels (e.g., Male, Female, Young, College Educated, Asian, Black, Hispanic, White, and various social classes).

\begin{table}
    \caption{.}
    \centering
    \includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Tabs/zinf-reg.png}
    \label{tab:zinf}
\end{table}

Our methodological approach treats this rich association data as cognitive two-mode data, conceptually analogous to Krackhardt-style data used in one-mode networks \citep{batchelder1997consensus-f5c, kumbasar1994systematic-213}, where each person provides their perceived associations between musical genres and social labels. I use relational techniques, including Dual Projection and Backbone extraction \citep{everett2013dual-projection-c89, neal2014backbone-b29}, to distill and isolate the most significant perceived associations from the raw data. Subsequently, the backbone of these person-specific projected networks is jointly modeled using Stacked Correspondence Analysis and Geometric Data Analysis \citep{roux2004geometric-65c}.

This analytical framework generates three sets of scores: person-specific judgments of the relative similarity of genres and labels (row scores), aggregate judgments of genre and label similarity (column scores), and supplementary scores for genres and labels representing the centroid of the cloud of person-specific judgments. Ultimately, this allows me to examine heterogeneity in folk understandings by observing how multiple clouds of individuals (projected into both genre and social label spaces) distribute themselves along principal axes, providing critical insights into the variation in meaning consensus across different levels of analysis.

\section*{Workflow Illustration}

\section*{Results}

\section*{Discussion and Conclusions}

\newpage
\bibliography{references}
\bibliographystyle{apalike}
\end{document}

### 2025-06-20 analysis-bb-new.qmd
new bb who dis

--- 2025-05-09 analysis-bb.qmd
@@
    na.omit() #removing missing values
+      r <- c("Classical", "Opera", "Jazz", "Broadway", "Easy", "Big_Band", "Classic_Rock", "Country", "Bluegrass", "Folk", "Gospel", "Latin", "Rap", "Blues", "Reggae", "Pop", "Contemp_Rock", "Alt_Rock", "Dance", "Metal")
+       c <- c("Female", "Male", "White", "Black", "Hispanic", "Asian", "College", "No_College", "Young", "Mid_Age", "Old", "Lower_Class", "Working_Class", "Middle_Class", "Upper_Class")
+```
+
+```{r Summary Table of Averaged Perceptions}
+   tab <- colSums(dat[,2:301])/nrow(dat)
+   tab <- matrix(tab, nrow = 20,  byrow = TRUE)
+   colnames(tab) <- c
+   rownames(tab) <- r
+   png(file = here("Plots", "main.png"), width=1000, height=700)
+   corrplot(tab, is.corr = FALSE, method = "color", 
+      tl.col = "black", tl.cex = 1, tl.srt = 45,
+      addCoef.col = "black", cl.pos = "n", cl.lim = c(0, max(tab)),
+      number.cex = 1, number.digits = 2, addgrid.col = "darkgray",
+      col=colorRampPalette(c("lightblue","orange","red"))(200))
+   dev.off()
 ```
@@
 ```{r Creating individual matrices}
-   row.breiger <- function(x) {
-      x %*% t(x)
+   make.mat <- function(x) {
+      x <- matrix(as.numeric(x), 20, 15, byrow = TRUE)
+      return(x)
       }
-   col.breiger <- function(x) {
-      t(x) %*% x
-      }
-   bb <- function(x) {
-      x <- suppressMessages(disparity(x, alpha = 0.25, narrative = FALSE))
-      return(x)
+   bb.sdsm <- function(x) {
+     tryCatch({
+         w <- sdsm(x, alpha = 0.25, narrative = FALSE)
+         return(w)
+            }, error = function(e) {return(NULL)})
       }
@@
    ind.list <- split(dat2, seq(nrow(dat2))) # splitting each row of data frame into list objects
-   ind.mat <- lapply(ind.list, function(x) {matrix(as.numeric(x), 20, 15, byrow = TRUE)}) # creating individual two mode network of genre by labels
-      r <- c("Classical", "Opera", "Jazz", "Broadway", "Easy", "Big_Band", "Classic_Rock", "Country", "Bluegrass", "Folk", "Gospel", "Latin", "Rap", "Blues", "Reggae", "Pop", "Contemp_Rock", "Alt_Rock", "Dance", "Metal")
-       c <- c("Female", "Male", "White", "Black", "Hispanic", "Asian", "College", "No_College", "Young", "Mid_Age", "Old", "Lower_Class", "Working_Class", "Middle_Class", "Upper_Class")
+   ind.mat <- lapply(ind.list, make.mat) # creating individual two mode network of genre by labels
    ind.mat <- lapply(ind.mat, function(x) {rownames(x) <- r; x}) # naming individual rows
@@
    names(ind.mat) <- dat$id_char[-c(bad.den)]
-   ind.row <- lapply(ind.mat, row.breiger) # individual genre projection
-   ind.col <- lapply(ind.mat, col.breiger) # individual label projection
-   row.bb <- lapply(ind.row, bb)
-   col.bb <- lapply(ind.col, bb)
+   ind.mat.t <- lapply(ind.mat, function(x) {t(x)})
+   row.bb <- lapply(ind.mat, bb.sdsm)
+   col.bb <- lapply(ind.mat.t, bb.sdsm)
+   null.rows <- which(as.numeric(unlist(lapply(row.bb, is.null))) == 1)
+   null.cols <- which(as.numeric(unlist(lapply(col.bb, is.null))) == 1)
+   row.bb <- row.bb[-null.rows]
+   col.bb <- col.bb[-null.cols]
    row.stack <- matrix(unlist(row.bb), ncol = 20, byrow = TRUE) # genre stacked matrix
@@
    colnames(col.stack) <- c # naming label stacked matrix columns
-   rownames(row.stack) <- rep(r, nrow(dat2)) # naming genre stacked matrix rows
-   rownames(col.stack) <- rep(c, nrow(dat2)) # naming label stacked matrix rows
+   m <- nrow(row.stack)/20
+   rownames(row.stack) <- rep(r, m) # naming genre stacked matrix rows
+   rownames(col.stack) <- rep(c, m) # naming label stacked matrix rows
    zero.rows.r <- which(rowSums(row.stack) == 0) # which genre stacked matrix rows sum to zero?
    zero.rows.c <- which(rowSums(col.stack) == 0) # which label stacked matrix rows sum to zero?
-   names(ind.row) <- dat$id_char[-c(bad.den)]
-   names(ind.col) <- dat$id_char[-c(bad.den)]
-   names(row.bb) <- dat$id_char[-c(bad.den)]
-   names(col.bb) <- dat$id_char[-c(bad.den)]
 ```
@@
    row.stack.d <- data.frame(row.stack)
-   row.stack.d$genre <- rep(r, nrow(dat2))
-   row.stack.d$id <- rep(dat$id_char[-bad.den], each = 20)
+   row.stack.d$genre <- rep(r, m)
+   row.stack.d$id <- rep(names(row.bb), each = 20)
    CA.r <- CA(row.stack.d, graph = FALSE, row.sup = zero.rows.r, quali.sup = c(21, 22))
@@
    col.stack.d <- data.frame(col.stack)
-   col.stack.d$label <- rep(c, nrow(dat2))
-   col.stack.d$id <- rep(dat$id_char[-bad.den], each = 15)
+   col.stack.d$label <- rep(c, m)
+   col.stack.d$id <- rep(names(col.bb), each = 15)
    CA.c <- CA(col.stack.d, graph = FALSE, row.sup = zero.rows.c, quali.sup = c(16, 17))
@@
          }
+      #genre column scores data frame
       col.gen.dat <-  data.frame(CA.r$col$coord) %>% 
-         mutate(col.obj = rownames(CA.r$col$coord)) #genre column scores
+         mutate(col.obj = rownames(CA.r$col$coord)) 
+      #label column scores data frame
       col.lab.dat <-  data.frame(CA.c$col$coord) %>% 
-         mutate(col.obj = rownames(CA.c$col$coord)) #label column scores
+         mutate(col.obj = rownames(CA.c$col$coord)) 
+      #supplementary scores data frame for genres
       sup.gen.dat <- CA.r$quali.sup$coord[1:20, ] 
-      sup.lab.dat <- CA.c$quali.sup$coord[1:15, ] 
       sup.gen.dat <- data.frame(sup.gen.dat, 
                                 col.obj = gsub("genre.", "", rownames(sup.gen.dat)))
-      rownames(sup.gen.dat) <- sup.gen.dat$col.obj
+      rownames(sup.gen.dat) <- 1:nrow(sup.gen.dat)
+      #supplementary scores data frame for labels
+      sup.lab.dat <- CA.c$quali.sup$coord[1:15, ] 
       sup.lab.dat <- data.frame(sup.lab.dat, 
                                 col.obj = gsub("label.", "", rownames(sup.lab.dat)))
-      rownames(sup.lab.dat) <- sup.lab.dat$col.obj
-      row.gen.dat <- make.plot.dat(CA.r$row$coord) #genre row scores
-      row.lab.dat <- make.plot.dat(CA.c$row$coord) #label row scores
+      rownames(sup.lab.dat) <- 1:nrow(sup.lab.dat)
+      #genre row scores
+      row.gen.dat <- make.plot.dat(CA.r$row$coord) 
+      #label row scores
+      row.lab.dat <- make.plot.dat(CA.c$row$coord) 
+      #supplementary individual scores for genres
       ind.gen.sup <- CA.r$quali.sup$coord %>% 
          data.frame() %>% 
-      slice(21:nrow(CA.r$quali.sup$coord)) 
-   ind.gen.sup$id_char <- str_sub(rownames(ind.gen.sup), 4, -1)
+         slice(21:nrow(CA.r$quali.sup$coord)) %>% 
+         mutate(id_char = str_sub(rownames(CA.r$quali.sup$coord[21:nrow(CA.r$quali.sup$coord), ]), 4, -1))
+      row.names(ind.gen.sup) <- 1:nrow(ind.gen.sup)
+      #supplementary individual scores for labels
       ind.lab.sup <- CA.c$quali.sup$coord %>% 
          data.frame() %>% 
-      slice(21:nrow(CA.c$quali.sup$coord)) 
-   ind.lab.sup$id_char <- str_sub(rownames(ind.lab.sup), 4, -1)
+         slice(16:nrow(CA.c$quali.sup$coord)) %>% 
+         mutate(id_char = str_sub(rownames(CA.c$quali.sup$coord[16:nrow(CA.c$quali.sup$coord), ]), 4, -1))
+      row.names(ind.lab.sup) <- 1:nrow(ind.lab.sup)
 ```

### 2025-06-20 analysis-bb-new.qmd
whateves

@@
      tryCatch({
-         w <- sdsm(x, alpha = 0.25, narrative = FALSE)
+         w <- sdsm(x, alpha = 0.35, narrative = FALSE)
          return(w)
@@
    ind.mat.t <- lapply(ind.mat, function(x) {t(x)})
-   row.bb <- lapply(ind.mat, bb.sdsm)
-   col.bb <- lapply(ind.mat.t, bb.sdsm)
-   null.rows <- which(as.numeric(unlist(lapply(row.bb, is.null))) == 1)
-   null.cols <- which(as.numeric(unlist(lapply(col.bb, is.null))) == 1)
-   row.bb <- row.bb[-null.rows]
-   col.bb <- col.bb[-null.cols]
+   ind.row <- lapply(ind.mat, function(x) {x %*% t(x)}) # individual genre projection
+   ind.col <- lapply(ind.mat, function(x) {t(x) %*% x}) # individual label projection
+   #row.bb <- lapply(ind.mat, bb.sdsm)
+   #col.bb <- lapply(ind.mat.t, bb.sdsm)
+   #null.rows <- which(as.numeric(unlist(lapply(row.bb, is.null))) == 1)
+   #null.cols <- which(as.numeric(unlist(lapply(col.bb, is.null))) == 1)
+   #row.bb <- row.bb[-null.rows]
+   #col.bb <- col.bb[-null.cols]
+   #save(row.bb, col.bb, file = "bb.RData")
+   load(here("bb.RData"))
    row.stack <- matrix(unlist(row.bb), ncol = 20, byrow = TRUE) # genre stacked matrix
@@
    zero.rows.c <- which(rowSums(col.stack) == 0) # which label stacked matrix rows sum to zero?
+```
+
+```{r Data Examples}
+   make.aff.plot <- function(x) {
+      p <- corrplot(x, is.corr = FALSE, method = "color", 
+         tl.col = "black", tl.cex = 1, tl.srt = 45,
+         addCoef.col = "black", cl.pos = "n",
+         number.cex = 1.75, number.digits = 0, addgrid.col = "darkgray",
+         col=colorRampPalette(c("white","white","red"))(200))
+      return(p)
+      }
+   make.proj.plot <- function(x) {
+     p <- corrplot(x, is.corr = FALSE, method = "color", 
+         tl.col = "black", tl.cex = 1, tl.srt = 45,
+         addCoef.col = "black", cl.pos = "n", cl.lim = c(0, max(x)),
+         number.cex = 1.5, number.digits = 0, addgrid.col = "darkgray",
+         col=colorRampPalette(c("lightblue","pink","red"))(200))
+         return(p)
+         }
+   k = 1
+   for (id in c("id_65", "id_236", "id_1114", "id_2002")) {
+      plot.name <- paste(paste("data-ex-af", k, sep = ""), ".png", sep = "")
+      png(file = here("Plots", plot.name), width=800, height=700)
+      make.aff.plot(ind.mat[[id]])
+      dev.off()
+      plot.name <- paste(paste("data-ex-rp", k, sep = ""), ".png", sep = "")
+      png(file = here("Plots", plot.name), width=800, height=700)
+      make.proj.plot(ind.row[[id]])
+      dev.off()
+      plot.name <- paste(paste("data-ex-cp", k, sep = ""), ".png", sep = "")
+      png(file = here("Plots", plot.name), width=800, height=700)
+      make.proj.plot(ind.col[[id]])
+      dev.off()
+      plot.name <- paste(paste("data-ex-rbb", k, sep = ""), ".png", sep = "")
+      png(file = here("Plots", plot.name), width=800, height=700)
+      make.aff.plot(row.bb[[id]])
+      dev.off()
+      plot.name <- paste(paste("data-ex-cbb", k, sep = ""), ".png", sep = "")
+      png(file = here("Plots", plot.name), width=800, height=700)
+      make.aff.plot(col.bb[[id]])
+      dev.off()
+      k <- k + 1
+      }
+   a <- rbind(row.bb[["id_65"]], row.bb[["id_236"]])
+   b <- rbind(col.bb[["id_65"]], col.bb[["id_236"]])
+   png(file = here("Plots", "data-ex-stack1.png"), width=800, height=1000)
+   make.aff.plot(a)
+   dev.off()
+   png(file = here("Plots", "data-ex-stack2.png"), width=800, height=1000)
+   make.aff.plot(b)
+   dev.off()
 ```
@@
 
-```{r Data Examples}
-   make.aff.plot <- function(x) {
-      p <- corrplot(x, is.corr = FALSE, method = "color", 
-         tl.col = "black", tl.cex = 1, tl.srt = 45,
-         addCoef.col = "black", cl.pos = "n",
-         number.cex = 1.75, number.digits = 0, addgrid.col = "darkgray",
-         col=colorRampPalette(c("white","white","red"))(200))
-      return(p)
-      }
-   make.proj.plot <- function(x) {
-     p <- corrplot(x, is.corr = FALSE, method = "color", 
-         tl.col = "black", tl.cex = 1, tl.srt = 45,
-         addCoef.col = "black", cl.pos = "n", cl.lim = c(0, max(x)),
-         number.cex = 1.5, number.digits = 0, addgrid.col = "darkgray",
-         col=colorRampPalette(c("lightblue","pink","red"))(200))
-         return(p)
-         }
-   k = 1
-   for (id in c("id_65", "id_236", "id_1114", "id_2002")) {
-      plot.name <- paste(paste("data-ex-af", k, sep = ""), ".png", sep = "")
-      png(file = here("Plots", plot.name), width=800, height=700)
-      make.aff.plot(ind.mat[[id]])
-      dev.off()
-      plot.name <- paste(paste("data-ex-rp", k, sep = ""), ".png", sep = "")
-      png(file = here("Plots", plot.name), width=800, height=700)
-      make.proj.plot(ind.row[[id]])
-      dev.off()
-      plot.name <- paste(paste("data-ex-cp", k, sep = ""), ".png", sep = "")
-      png(file = here("Plots", plot.name), width=800, height=700)
-      make.proj.plot(ind.col[[id]])
-      dev.off()
-      plot.name <- paste(paste("data-ex-rbb", k, sep = ""), ".png", sep = "")
-      png(file = here("Plots", plot.name), width=800, height=700)
-      make.aff.plot(row.bb[[id]])
-      dev.off()
-      plot.name <- paste(paste("data-ex-cbb", k, sep = ""), ".png", sep = "")
-      png(file = here("Plots", plot.name), width=800, height=700)
-      make.aff.plot(col.bb[[id]])
-      dev.off()
-      k <- k + 1
-      }
-   a <- rbind(row.bb[["id_65"]], row.bb[["id_236"]])
-   b <- rbind(col.bb[["id_65"]], col.bb[["id_236"]])
-   png(file = here("Plots", "data-ex-stack1.png"), width=800, height=1000)
-   make.aff.plot(a)
-   dev.off()
-   png(file = here("Plots", "data-ex-stack2.png"), width=800, height=1000)
-   make.aff.plot(b)
-   dev.off()
-```
-
 ```{r Column Score Similarity Plots}
@@
                      seed = 125, ls = 5, 
-                     1, 2, pa = .35,  t = 3, b = 3, l = 2, r = 3,
+                     1, 2, pa = .35,  t = 3, b = 3, l = 2, r = 3, bns = 6,
                      c("Rap", "Folk", "Classical"))
@@
                      seed = 125, ls = 5,
-                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3,
+                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 6,
                      c("Alt_Rock", "Gospel", "Opera"))
@@
                      seed = 125, ls = 5,
-                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 5,
+                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 6,
                      c("Metal", "Bluegrass", "Broadway"))
@@
                      seed = 125, ls = 5,
-                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 4,
+                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3.25, bns = 6,
                      c("Jazz", "Reggae", "Blues", "Rap", "Classical"))
@@
                      seed = 125, ls = 5,
-                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 4,
+                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 6,
                      c("Country", "Bluegrass", "Classic_Rock", "Folk"))
@@
                      seed = 125, ls = 5,
-                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 4,
+                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 6,
                      c("Alt_Rock", "Contemp_Rock", "Classic_Rock", "Metal"))
@@
                      seed = 125, ls = 5,
-                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 4,
+                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 6,
                      c("Broadway", "Classical", "Opera", "Easy", "Jazz"))

### 2025-06-20 manuscript.tex

@@
 
-\begin{table}
-    \caption{.}
+\subsection*{Averaged Genre Associations}
+Figure~\ref{fig:main} shows a heatmap plot of the proportion of respondents associating each genre with each of the fifteen social labels included in the survey, reproducing one of the key results from \citet[Table 3]{lizardo2016cultural-aaa}.
+As we can see, respondents use social labels associated with gender fairly indiscriminately, associating it with each genre at a fairly high rate.
+Racial categories are used in a more discriminating manner, reproducing (on the average) standard stereotypes of genre audiences.
+Rock and traditional ``highbrow'' genre categories are associated with white audiences, Rap, Blues, R\&B, Reggae, and Gospel with Black audiences, and Latin music with Hispanic audiences.
+The category of Asian is not strongly associated with any genre.
+Both age and class/education categories also reproduce expected stereotypes.
+For instance, ,Rap and Metal are considered ``young'' genres, while Classic Rock and Country are thought of as ```middle aged.'' In the same way, Classical and Opera audiences are considered educated and Upper Class, while Bluegrass and Country audiences are considered not college educated and working or lower class).
+
+\begin{figure}[ht!]
     \centering
-    \includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Tabs/zinf-reg.png}
-    \label{tab:zinf}
-\end{table}
+    \includegraphics[trim={7cm 0cm 6cm 0cm},clip, width=0.9\textwidth]{Plots/main.png}
+    \caption{Heatmap matrix of the proportion of respondents associating each one of fifteen social labels (columns) with one of twenty musical genre categories (rows).}
+    \label{fig:main}
+\end{figure}
 
-Our methodological approach treats this rich association data as cognitive two-mode data, conceptually analogous to Krackhardt-style data used in one-mode networks \citep{batchelder1997consensus-f5c, kumbasar1994systematic-213}, where each person provides their perceived associations between musical genres and social labels.
-I use relational techniques, including Dual Projection and Backbone extraction \citep{everett2013dual-projection-c89, neal2014backbone-b29}, to distill and isolate the most significant perceived associations from the raw data.
-Subsequently, the backbone of these person-specific projected networks is jointly modeled using Stacked Correspondence Analysis and Geometric Data Analysis \citep{roux2004geometric-65c}.
+\subsection*{Cognitive Two Mode Networks}
+The data used to construct Figure ~\ref{fig:main} consists of averages of more than two thousand binary matrices---one for each respondent---of the same dimensions as~\ref{fig:main} provided by each respondent.
+As such, the averaging hides as much as it reveals, even as it produced intuitive results.
+The methodological approach taken here treats this rich disaggregated association data as cognitive two-mode data, conceptually analogous to Krackhardt-style data used in one-mode networks \citep{batchelder1997consensus-f5c, kumbasar1994systematic-213}, where each person provides their perceived associations between musical genres and social labels.
+In terms of recent work in measuring culture, each individual two-mode data table records the (explicit) schematic structure of the way individuals perceive each genre category relative to the set of social labels \citep{hunzaker2019mapping-280}.
+
+More formally, each individual provides a ``personal'' two mode network of genres by social labels with corresponding affiliation matrix $\mathbf{A}(p)$, where $a^{(p)}_{gl} = 1$ if individual $p$ associates genre $g$ with label $l$.
+Following \citet{breiger1974duality-1d0}, the personal genre projection is given by:
+
+\begin{equation}
+   \mathbf{G}(p) = \mathbf{A}(p)\mathbf{A}(p)^T 
+\end{equation}
+
+Where $g^{(p)}_{ij}$ records the $p^{th}$ individual's perceived similarity between genres $i$ and $j$ based on their shared labels and $g^{(p)}_{ii}$ records the number of times individual $p$ associates genre $i$ with a label.
+
+In the same way, the personal label projection is given by:
+
+\begin{equation}
+    \mathbf{L}(p) = \mathbf{A}(p)^T\mathbf{A}(p)
+\end{equation}
+
+Where $l^{(p)}_{kl}$ records the $p^{th}$ individual's perceived similarity between labels $k$ and $l$ based on their shared genres, and $l^{(p)}_{kk}$ records the number of times individual $p$ associates genre $i$ with a label.
+The structure of the data thus allows us to take a ``Mondo Breiger'' approach \citep{lee2018doorway-008}, where we can perform dual projections at the level of each individual.
+
+\subsection*{Individual Backbone Extraction}
+Because each dual projection is likely to over-estimate the perceived similarities between genres and labels at the level of the individual, I use backbone extraction on each individual projection---more specifically, the disparity filter \citep{serrano2009extracting-084}---to isolate the most significant genre-to-genre and label-to-label associations for each individual \citep{neal2014backbone-b29}.
+
+\begin{figure}[ht!]
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+     \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[trim={4cm 0cm 3cm 0cm},clip, width=0.9\textwidth]{Plots/data-ex-af1.png}
+            \caption{Case ID: 65}
+            \label{fig:ind-ex-aff1}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[trim={4cm 0cm 3cm 0cm},clip, width=0.9\textwidth]{Plots/data-ex-af2.png}
+            \caption{Case ID: 236}
+            \label{fig:ind-ex-aff2}
+    \end{subfigure}
+    \caption{Individual affiliation matrices of the association between musical genres and social labels.}
+    \label{fig:ind-ex-aff}
+\end{figure}
+
+For instance, Figure~\ref{fig:ind-ex-aff} shows the cognitive two-mode network matrices of the associations between genres and social labels for two individuals in the data.
+It is clear from this example that the averaged associations shown in Figure~\ref{fig:main} hide quite a lof of individual variation and idiosyncratic perceptions.
+
+\begin{figure}[ht!]
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+     \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[trim={1cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/data-ex-rp1.png}
+            \caption{Case ID: 65}
+            \label{fig:ind-ex-rp1}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[trim={1cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/data-ex-rp2.png}
+            \caption{Case ID: 236}
+            \label{fig:ind-ex-rp2}
+    \end{subfigure}
+    \caption{Individual genre projection matrices.}
+    \label{fig:ind-ex-rp}
+\end{figure}
+
+\begin{figure}[ht!]
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+     \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[trim={1cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/data-ex-cp1.png}
+            \caption{Case ID: 65}
+            \label{fig:ind-ex-cp1}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[trim={1cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/data-ex-cp2.png}
+            \caption{Case ID: 236}
+            \label{fig:ind-ex-cp2}
+    \end{subfigure}
+    \caption{Individual label projection matrices.}
+    \label{fig:ind-ex-cp}
+\end{figure}
+
+Figures~\ref{fig:ind-ex-rp} and~\ref{fig:ind-ex-cp} show the corresponding row ($\mathbf{G}(p)$) and column ($\mathbf{L}(p)$) projections for the same two individuals, while Figures~\ref{fig:ind-ex-rbb} and~\ref{fig:ind-ex-cbb} show the respective backbones of each projection for the same cases.
+As we can see the procedure extract distinct sets of significant associations between genres and labels for this two cases.
+
+\begin{figure}[ht!]
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+     \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[trim={1cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/data-ex-rbb1.png}
+            \caption{Case ID: 65}
+            \label{fig:ind-ex-rbb1}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[trim={1cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/data-ex-rbb2.png}
+            \caption{Case ID: 236}
+            \label{fig:ind-ex-rbb2}
+    \end{subfigure}
+    \caption{Individual genre backbones.}
+    \label{fig:ind-ex-rbb}
+\end{figure}
 
@@
 Ultimately, this allows me to examine heterogeneity in folk understandings by observing how multiple clouds of individuals (projected into both genre and social label spaces) distribute themselves along principal axes, providing critical insights into the variation in meaning consensus across different levels of analysis.
+
+\begin{figure}[ht!]
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+     \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[trim={1cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/data-ex-cbb1.png}
+            \caption{Case ID: 65}
+            \label{fig:ind-ex-cbb1}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[trim={1cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/data-ex-cbb2.png}
+            \caption{Case ID: 236}
+            \label{fig:ind-ex-cbb2}
+    \end{subfigure}
+    \caption{Individual label backbones.}
+    \label{fig:ind-ex-cbb}
+\end{figure}
 

### 2025-06-20 manuscript.tex

@@
     \centering
-    \includegraphics[trim={7cm 0cm 6cm 0cm},clip, width=0.9\textwidth]{Plots/main.png}
+    \includegraphics[trim={7cm 0cm 6cm 0cm},clip, width=0.6\textwidth]{Plots/main.png}
     \caption{Heatmap matrix of the proportion of respondents associating each one of fifteen social labels (columns) with one of twenty musical genre categories (rows).}
@@
 \subsection*{Individual Backbone Extraction}
-Because each dual projection is likely to over-estimate the perceived similarities between genres and labels at the level of the individual, I use backbone extraction on each individual projection---more specifically, the disparity filter \citep{serrano2009extracting-084}---to isolate the most significant genre-to-genre and label-to-label associations for each individual \citep{neal2014backbone-b29}.
+Because each dual projection is likely to over-estimate the perceived similarities between genres and labels at the level of the individual, I use backbone extraction on each individual-level projection---more specifically, the Stochastic Degree Sequence Model (SDSM)---to isolate the most significant genre-to-genre and label-to-label associations for each person \citep{neal2014backbone-b29}.
 

### 2025-06-20 analysis-bb-new.qmd
newer plots

@@
      tryCatch({
-         w <- sdsm(x, alpha = 0.35, narrative = FALSE)
+         w <- round(sdsm(x, alpha = NULL, missing.as.zero = TRUE)$Pupper, 2)
          return(w)
@@
    ind.col <- lapply(ind.mat, function(x) {t(x) %*% x}) # individual label projection
-   #row.bb <- lapply(ind.mat, bb.sdsm)
-   #col.bb <- lapply(ind.mat.t, bb.sdsm)
-   #null.rows <- which(as.numeric(unlist(lapply(row.bb, is.null))) == 1)
-   #null.cols <- which(as.numeric(unlist(lapply(col.bb, is.null))) == 1)
-   #row.bb <- row.bb[-null.rows]
-   #col.bb <- col.bb[-null.cols]
-   #save(row.bb, col.bb, file = "bb.RData")
+   # row.bb <- lapply(ind.mat, bb.sdsm)
+   # col.bb <- lapply(ind.mat.t, bb.sdsm)
+   # null.rows <- which(as.numeric(unlist(lapply(row.bb, is.null))) == 1)
+   # null.cols <- which(as.numeric(unlist(lapply(col.bb, is.null))) == 1)
+   # row.bb <- row.bb[-null.rows]
+   # col.bb <- col.bb[-null.cols]
+   # row.bb <- lapply(row.bb, function(x) {ifelse(is.nan(x), 1, x)})
+   # col.bb <- lapply(col.bb, function(x) {ifelse(is.nan(x), 1, x)})
+   # row.bb <- lapply(row.bb, function(x) {diag(x) <- 1; x})
+   # col.bb <- lapply(col.bb, function(x) {diag(x) <- 1; x})
+   # save(row.bb, col.bb, file = here("bb.RData"))
    load(here("bb.RData"))
+   row.bb <- lapply(row.bb, function(x) {(x < 0.45) * 1})
+   col.bb <- lapply(col.bb, function(x) {(x < 0.45) * 1})
    row.stack <- matrix(unlist(row.bb), ncol = 20, byrow = TRUE) # genre stacked matrix

### 2025-06-21 Old/analysis-bb-old.qmd
moving

--- 2025-05-09 analysis-bb.qmd
@@
 ```{r Creating individual matrices}
+   make.mat <- function(x) {
+      x <- matrix(as.numeric(x), 20, 15, byrow = TRUE)
+      return(x)
+   }
    row.breiger <- function(x) {
-      x %*% t(x)
+      x <- x %*% t(x)
+      return(x)
       }
    col.breiger <- function(x) {
-      t(x) %*% x
+      x <- t(x) %*% x
+      return(x)
       }
-   bb <- function(x) {
-      x <- suppressMessages(disparity(x, alpha = 0.25, narrative = FALSE))
+   bb <- function(x, a = 0.25) {
+      x <- suppressMessages(disparity(x, alpha = a, narrative = FALSE))
       return(x)
@@
    ind.list <- split(dat2, seq(nrow(dat2))) # splitting each row of data frame into list objects
-   ind.mat <- lapply(ind.list, function(x) {matrix(as.numeric(x), 20, 15, byrow = TRUE)}) # creating individual two mode network of genre by labels
+   ind.mat <- lapply(ind.list, make.mat) # creating individual two mode network of genre by labels
       r <- c("Classical", "Opera", "Jazz", "Broadway", "Easy", "Big_Band", "Classic_Rock", "Country", "Bluegrass", "Folk", "Gospel", "Latin", "Rap", "Blues", "Reggae", "Pop", "Contemp_Rock", "Alt_Rock", "Dance", "Metal")
@@
          }
+      #genre column scores data frame
       col.gen.dat <-  data.frame(CA.r$col$coord) %>% 
-         mutate(col.obj = rownames(CA.r$col$coord)) #genre column scores
+         mutate(col.obj = rownames(CA.r$col$coord)) 
+      #label column scores data frame
       col.lab.dat <-  data.frame(CA.c$col$coord) %>% 
-         mutate(col.obj = rownames(CA.c$col$coord)) #label column scores
+         mutate(col.obj = rownames(CA.c$col$coord)) 
+      #supplementary scores data frame for genres
       sup.gen.dat <- CA.r$quali.sup$coord[1:20, ] 
-      sup.lab.dat <- CA.c$quali.sup$coord[1:15, ] 
       sup.gen.dat <- data.frame(sup.gen.dat, 
                                 col.obj = gsub("genre.", "", rownames(sup.gen.dat)))
-      rownames(sup.gen.dat) <- sup.gen.dat$col.obj
+      rownames(sup.gen.dat) <- 1:nrow(sup.gen.dat)
+      #supplementary scores data frame for labels
+      sup.lab.dat <- CA.c$quali.sup$coord[1:15, ] 
       sup.lab.dat <- data.frame(sup.lab.dat, 
                                 col.obj = gsub("label.", "", rownames(sup.lab.dat)))
-      rownames(sup.lab.dat) <- sup.lab.dat$col.obj
-      row.gen.dat <- make.plot.dat(CA.r$row$coord) #genre row scores
-      row.lab.dat <- make.plot.dat(CA.c$row$coord) #label row scores
+      rownames(sup.lab.dat) <- 1:nrow(sup.lab.dat)
+      #genre row scores
+      row.gen.dat <- make.plot.dat(CA.r$row$coord) 
+      #label row scores
+      row.lab.dat <- make.plot.dat(CA.c$row$coord) 
+      #supplementary individual scores for genres
       ind.gen.sup <- CA.r$quali.sup$coord %>% 
          data.frame() %>% 
-      slice(21:nrow(CA.r$quali.sup$coord)) 
-   ind.gen.sup$id_char <- str_sub(rownames(ind.gen.sup), 4, -1)
+         slice(21:nrow(CA.r$quali.sup$coord)) %>% 
+         mutate(id_char = str_sub(rownames(ind.gen.sup), 4, -1))
+      row.names(ind.gen.sup) <- 1:nrow(ind.gen.sup)
+      #supplementary individual scores for labels
       ind.lab.sup <- CA.c$quali.sup$coord %>% 
          data.frame() %>% 
-      slice(21:nrow(CA.c$quali.sup$coord)) 
-   ind.lab.sup$id_char <- str_sub(rownames(ind.lab.sup), 4, -1)
+         slice(16:nrow(CA.c$quali.sup$coord)) %>% 
+         mutate(id_char = str_sub(rownames(ind.lab.sup), 4, -1))
+      row.names(ind.lab.sup) <- 1:nrow(ind.lab.sup)
+```
+
+```{r Cloud Variance Functions}
+   check.cloud.var <- function()
+
 ```

### 2025-06-21 analysis-bb.qmd
moving

@@
    conflicts_prefer(dplyr::select)
-   source(here("make.fuzz.plot.R"))
+   source(here("Functions", "make.fuzz.plot.R"))
+   source(here("Functions", "make.demog.plot.R"))
+   source(here("Functions", "demog.dat.R"))
+
 ```
@@
 ```{r Creating individual matrices}
-   row.breiger <- function(x) {
-      x %*% t(x)
+   make.mat <- function(x) {
+      x <- matrix(as.numeric(x), 20, 15, byrow = TRUE)
+      return(x)
       }
-   col.breiger <- function(x) {
-      t(x) %*% x
-      }
-   bb <- function(x) {
-      x <- suppressMessages(disparity(x, alpha = 0.25, narrative = FALSE))
-      return(x)
+   bb.sdsm <- function(x) {
+     tryCatch({
+         w <- round(sdsm(x, alpha = NULL, missing.as.zero = TRUE)$Pupper, 2)
+         return(w)
+            }, error = function(e) {return(NULL)})
          }
@@
    names(ind.mat) <- dat$id_char[-c(bad.den)]
-   ind.row <- lapply(ind.mat, row.breiger) # individual genre projection
-   ind.col <- lapply(ind.mat, col.breiger) # individual label projection
-   row.bb <- lapply(ind.row, bb)
-   col.bb <- lapply(ind.col, bb)
+   ind.mat.t <- lapply(ind.mat, function(x) {t(x)})
+   ind.row <- lapply(ind.mat, function(x) {x %*% t(x)}) # individual genre projection
+   ind.col <- lapply(ind.mat, function(x) {t(x) %*% x}) # individual label projection
+   # row.bb <- lapply(ind.mat, bb.sdsm)
+   # col.bb <- lapply(ind.mat.t, bb.sdsm)
+   # null.rows <- which(as.numeric(unlist(lapply(row.bb, is.null))) == 1)
+   # null.cols <- which(as.numeric(unlist(lapply(col.bb, is.null))) == 1)
+   # row.bb <- row.bb[-null.rows]
+   # col.bb <- col.bb[-null.cols]
+   # row.bb <- lapply(row.bb, function(x) {ifelse(is.nan(x), 1, x)})
+   # col.bb <- lapply(col.bb, function(x) {ifelse(is.nan(x), 1, x)})
+   # row.bb <- lapply(row.bb, function(x) {diag(x) <- 1; x})
+   # col.bb <- lapply(col.bb, function(x) {diag(x) <- 1; x})
+   # save(row.bb, col.bb, file = here("bb.RData"))
+   load(here("bb.RData"))
+   p.val <- 0.45
+   row.bb <- lapply(row.bb, function(x) {(x < p.val) * 1})
+   col.bb <- lapply(col.bb, function(x) {(x < p.val) * 1})
    row.stack <- matrix(unlist(row.bb), ncol = 20, byrow = TRUE) # genre stacked matrix
@@
    colnames(col.stack) <- c # naming label stacked matrix columns
-   rownames(row.stack) <- rep(r, nrow(dat2)) # naming genre stacked matrix rows
-   rownames(col.stack) <- rep(c, nrow(dat2)) # naming label stacked matrix rows
+   m <- nrow(row.stack)/20
+   rownames(row.stack) <- rep(r, m) # naming genre stacked matrix rows
+   rownames(col.stack) <- rep(c, m) # naming label stacked matrix rows
    zero.rows.r <- which(rowSums(row.stack) == 0) # which genre stacked matrix rows sum to zero?
    zero.rows.c <- which(rowSums(col.stack) == 0) # which label stacked matrix rows sum to zero?
-   names(ind.row) <- dat$id_char[-c(bad.den)]
-   names(ind.col) <- dat$id_char[-c(bad.den)]
-   names(row.bb) <- dat$id_char[-c(bad.den)]
-   names(col.bb) <- dat$id_char[-c(bad.den)]
-```
-
-```{r Stacked CA}
-   #genres
-   row.stack.d <- data.frame(row.stack)
-   row.stack.d$genre <- rep(r, nrow(dat2))
-   row.stack.d$id <- rep(dat$id_char[-bad.den], each = 20)
-   CA.r <- CA(row.stack.d, graph = FALSE, row.sup = zero.rows.r, quali.sup = c(21, 22))
-   #labels
-   col.stack.d <- data.frame(col.stack)
-   col.stack.d$label <- rep(c, nrow(dat2))
-   col.stack.d$id <- rep(dat$id_char[-bad.den], each = 15)
-   CA.c <- CA(col.stack.d, graph = FALSE, row.sup = zero.rows.c, quali.sup = c(16, 17))
-```
-
-```{r CA Statistics}
-   stuff <- theme(axis.text = element_text(size = 18),
-                  axis.title = element_text(size = 22))
-   png(file = here("Plots", "scree-genres.png"), width=500, height=600)
-   fviz_eig(CA.r, ncp = 6) + stuff + ggtitle("") + ylim(0, 12) + 
-      labs(y = "Explained Var. %")
-   dev.off()
-   png(file = here("Plots", "scree-labels.png"), width=500, height=600)
-   fviz_eig(CA.c, ncp = 6) + stuff + ggtitle("") + ylim(0, 12) + 
-      labs(y = "Explained Var. %")
-   dev.off()
-```
-
-```{r Plot Data}
-     make.plot.dat <- function(x) { 
-         w <-  data.frame(x) %>% 
-         mutate(col.obj = gsub("\\..*","",rownames(x))) 
-         rownames(w) <- 1:nrow(x)
-         return(w)
-         }
-      col.gen.dat <-  data.frame(CA.r$col$coord) %>% 
-         mutate(col.obj = rownames(CA.r$col$coord)) #genre column scores
-      col.lab.dat <-  data.frame(CA.c$col$coord) %>% 
-         mutate(col.obj = rownames(CA.c$col$coord)) #label column scores
-      sup.gen.dat <- CA.r$quali.sup$coord[1:20, ] 
-      sup.lab.dat <- CA.c$quali.sup$coord[1:15, ] 
-      sup.gen.dat <- data.frame(sup.gen.dat, 
-                                col.obj = gsub("genre.", "", rownames(sup.gen.dat)))
-      rownames(sup.gen.dat) <- sup.gen.dat$col.obj
-      sup.lab.dat <- data.frame(sup.lab.dat, 
-                                col.obj = gsub("label.", "", rownames(sup.lab.dat)))
-      rownames(sup.lab.dat) <- sup.lab.dat$col.obj
-      row.gen.dat <- make.plot.dat(CA.r$row$coord) #genre row scores
-      row.lab.dat <- make.plot.dat(CA.c$row$coord) #label row scores
-   ind.gen.sup <- CA.r$quali.sup$coord %>% 
-      data.frame() %>% 
-      slice(21:nrow(CA.r$quali.sup$coord)) 
-   ind.gen.sup$id_char <- str_sub(rownames(ind.gen.sup), 4, -1)
-   ind.lab.sup <- CA.c$quali.sup$coord %>% 
-      data.frame() %>% 
-      slice(21:nrow(CA.c$quali.sup$coord)) 
-   ind.lab.sup$id_char <- str_sub(rownames(ind.lab.sup), 4, -1)
 ```
@@
 
+```{r Stacked CA}
+   #genres
+   row.stack.d <- data.frame(row.stack)
+   row.stack.d$genre <- rep(r, m)
+   row.stack.d$id <- rep(names(row.bb), each = 20)
+   CA.r <- CA(row.stack.d, graph = FALSE, row.sup = zero.rows.r, quali.sup = c(21, 22))
+   #labels
+   col.stack.d <- data.frame(col.stack)
+   col.stack.d$label <- rep(c, m)
+   col.stack.d$id <- rep(names(col.bb), each = 15)
+   CA.c <- CA(col.stack.d, graph = FALSE, row.sup = zero.rows.c, quali.sup = c(16, 17))
+```
+
+```{r CA Statistics}
+   stuff <- theme(axis.text = element_text(size = 18),
+                  axis.title = element_text(size = 22))
+   png(file = here("Plots", "scree-genres.png"), width=500, height=600)
+   fviz_eig(CA.r, ncp = 6) + stuff + ggtitle("") + ylim(0, 12) + 
+      labs(y = "Explained Var. %")
+   dev.off()
+   png(file = here("Plots", "scree-labels.png"), width=500, height=600)
+   fviz_eig(CA.c, ncp = 6) + stuff + ggtitle("") + ylim(0, 12) + 
+      labs(y = "Explained Var. %")
+   dev.off()
+```
+
+```{r Plot Data}
+     make.plot.dat <- function(x) { 
+         w <-  data.frame(x) %>% 
+         mutate(col.obj = gsub("\\..*","",rownames(x))) 
+         rownames(w) <- 1:nrow(x)
+         return(w)
+         }
+      #genre column scores data frame
+      col.gen.dat <-  data.frame(CA.r$col$coord) %>% 
+         mutate(col.obj = rownames(CA.r$col$coord)) 
+      #label column scores data frame
+      col.lab.dat <-  data.frame(CA.c$col$coord) %>% 
+         mutate(col.obj = rownames(CA.c$col$coord)) 
+      #supplementary scores data frame for genres
+      sup.gen.dat <- CA.r$quali.sup$coord[1:20, ] 
+      sup.gen.dat <- data.frame(sup.gen.dat, 
+                                col.obj = gsub("genre.", "", rownames(sup.gen.dat)))
+      rownames(sup.gen.dat) <- 1:nrow(sup.gen.dat)
+      #supplementary scores data frame for labels
+      sup.lab.dat <- CA.c$quali.sup$coord[1:15, ] 
+      sup.lab.dat <- data.frame(sup.lab.dat, 
+                                col.obj = gsub("label.", "", rownames(sup.lab.dat)))
+      rownames(sup.lab.dat) <- 1:nrow(sup.lab.dat)
+      #genre row scores
+      row.gen.dat <- make.plot.dat(CA.r$row$coord) 
+      #label row scores
+      row.lab.dat <- make.plot.dat(CA.c$row$coord) 
+      #supplementary individual scores for genres
+      ind.gen.sup <- CA.r$quali.sup$coord %>% 
+         data.frame() %>% 
+         slice(21:nrow(CA.r$quali.sup$coord)) %>% 
+         mutate(id_char = str_sub(rownames(CA.r$quali.sup$coord[21:nrow(CA.r$quali.sup$coord), ]), 4, -1))
+      row.names(ind.gen.sup) <- 1:nrow(ind.gen.sup)
+      #supplementary individual scores for labels
+      ind.lab.sup <- CA.c$quali.sup$coord %>% 
+         data.frame() %>% 
+         slice(16:nrow(CA.c$quali.sup$coord)) %>% 
+         mutate(id_char = str_sub(rownames(CA.c$quali.sup$coord[16:nrow(CA.c$quali.sup$coord), ]), 4, -1))
+      row.names(ind.lab.sup) <- 1:nrow(ind.lab.sup)
+      demog.dat <- demog.dat() 
+      demog.dat <- bind_cols(tibble(id_char = paste("id", sapply(demog.dat[, 1], as.character), sep = "_")), demog.dat)
+      row.gen.dat.id <- cbind(row.gen.dat, id_char = row.stack.d$id[-zero.rows.r])
+      row.lab.dat.id <- cbind(row.lab.dat, id_char = col.stack.d$id[-zero.rows.c])
+```
+
 ```{r Column Score Similarity Plots}
@@
 ```{r Genre Cloud Plots}
-   source(here("make.fuzz.plot.R"))
    h <- 625
@@
 ```{r Label Cloud Plots}
-   source(here("make.fuzz.plot.R"))
    h <- 625
@@
    png(file = here("Plots", "label-proto-ex1.png"), width=w, height=h)
-      make.fuzz.plot(row.lab.dat, col.lab.dat, sup.lab.dat, bns = 6, ls = 6,
-                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 2,
+      make.fuzz.plot(row.lab.dat, col.lab.dat, sup.lab.dat, bns = 8, ls = 6,
+                     1, 2, pa = .35,  t = 2.5, b = 2, l = 1.5, r = 2.15,
                      c("White", "Asian", "Black", "Hispanic"))
@@
       make.fuzz.plot(row.lab.dat, col.lab.dat, sup.lab.dat, bns = 6, ls = 6,
-                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 2,
+                     1, 2, pa = .35,  t = 2.2, b = 2.2, l = 1.5, r = 2.5,
                      c("Old", "Mid_Age", "Young"))
@@
       make.fuzz.plot(row.lab.dat, col.lab.dat, sup.lab.dat, bns = 6, ls = 6,
-                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 2,
+                     1, 2, pa = .35,  t = 3, b = 2, l = 2, r = 2,
                      c("Male", "Female"))
@@
 
-```{r Demographic Data}
-      source(here("demog.dat.R"))
-      demog.dat <- demog.dat() 
-      demog.dat <- bind_cols(tibble(id_char = paste("id", sapply(demog.dat[, 1], as.character), sep = "_")), demog.dat)
-      head(demog.dat) 
-      row.gen.dat.id <- cbind(row.gen.dat, id_char = row.stack.d$id[-zero.rows.r])
-      row.lab.dat.id <- cbind(row.lab.dat, id_char = col.stack.d$id[-zero.rows.c])
+```{r Demographic Cloud-Specific Plots}
    make.demog.dat <- function(w, g, d) {
@@
       }
-```
-
-```{r Demographic Cloud-Specific Plots}
-   source(here("make.demog.plot.R"))
    w <- 900

### 2025-06-21 manuscript.tex

@@
 Figure~\ref{fig:main} shows a heatmap plot of the proportion of respondents associating each genre with each of the fifteen social labels included in the survey, reproducing one of the key results from \citet[Table 3]{lizardo2016cultural-aaa}.
-As we can see, respondents use social labels associated with gender fairly indiscriminately, associating it with each genre at a fairly high rate.
-Racial categories are used in a more discriminating manner, reproducing (on the average) standard stereotypes of genre audiences.
-Rock and traditional ``highbrow'' genre categories are associated with white audiences, Rap, Blues, R\&B, Reggae, and Gospel with Black audiences, and Latin music with Hispanic audiences.
+As we can see, respondents use social labels associated with gender fairly indiscriminately, associating them with each genre at a fairly high rate.
+Racial categories are used in a more discriminating manner, reproducing (on average) standard stereotypes of genre audiences.
+Rock and traditional ``highbrow" genre categories are associated with white audiences, while Rap, Blues, R\&B, Reggae, and Gospel are associated with Black audiences, and Latin music is associated with Hispanic audiences.
 The category of Asian is not strongly associated with any genre.
 Both age and class/education categories also reproduce expected stereotypes.
-For instance, ,Rap and Metal are considered ``young'' genres, while Classic Rock and Country are thought of as ```middle aged.'' In the same way, Classical and Opera audiences are considered educated and Upper Class, while Bluegrass and Country audiences are considered not college educated and working or lower class).
+For instance, Rap and Metal are considered ``young'' genres.
+At the same time, Classic Rock and Country are thought of as ```middle-aged.'' In the same way, Classical and Opera audiences are considered educated and Upper Class, while Bluegrass and Country audiences are considered not college educated and working or lower class.
 
@@
 The data used to construct Figure ~\ref{fig:main} consists of averages of more than two thousand binary matrices---one for each respondent---of the same dimensions as~\ref{fig:main} provided by each respondent.
-As such, the averaging hides as much as it reveals, even as it produced intuitive results.
+As such, the averaging hides as much as it reveals, even as it produces intuitive results.
 The methodological approach taken here treats this rich disaggregated association data as cognitive two-mode data, conceptually analogous to Krackhardt-style data used in one-mode networks \citep{batchelder1997consensus-f5c, kumbasar1994systematic-213}, where each person provides their perceived associations between musical genres and social labels.
-In terms of recent work in measuring culture, each individual two-mode data table records the (explicit) schematic structure of the way individuals perceive each genre category relative to the set of social labels \citep{hunzaker2019mapping-280}.
+In terms of recent work on measuring culture, each person-level two-mode data table records the (explicit) schematic structure of how individuals perceive each genre category relative to the set of social labels \citep{hunzaker2019mapping-280}.
 
@@
 Because each dual projection is likely to over-estimate the perceived similarities between genres and labels at the level of the individual, I use backbone extraction on each individual-level projection---more specifically, the Stochastic Degree Sequence Model (SDSM)---to isolate the most significant genre-to-genre and label-to-label associations for each person \citep{neal2014backbone-b29}.
+
+The SDSM works as follows: In the first step, a generalized linear model for binary outcomes is used to predict the probability of a tie between each genre and label in the two-mode network, using the number of times a genre was associated with social label and the number of times a social label was associated with a genre (the degrees of the nodes in each mode) and their interaction as predictors.
+From the predicted probabilities derived from this model (where the unit of analysis is the genre/label pair), we create an ensemble of two-mode networks, generate genre-to-genre and label-to-label projections for each, and compute the percentage of times that the projected edge weight between pairs of genres and pairs of labels is smaller than that observed in the original network.
+We then create a binary link between two genres and two labels (indicating perceived similarity) if this percentage falls below a certain threshold.
+In these data, the usual $p < 0.05$ criterion proves to be too strong (generating mostly empty backbones) for each genre-to-genre and label-to-label projection.
+Accordingly, I use a less stringent criterion of $p < 0.45$.
 

### 2025-06-21 manuscript.tex

@@
 The SDSM works as follows: In the first step, a generalized linear model for binary outcomes is used to predict the probability of a tie between each genre and label in the two-mode network, using the number of times a genre was associated with social label and the number of times a social label was associated with a genre (the degrees of the nodes in each mode) and their interaction as predictors.
-From the predicted probabilities derived from this model (where the unit of analysis is the genre/label pair), we create an ensemble of two-mode networks, generate genre-to-genre and label-to-label projections for each, and compute the percentage of times that the projected edge weight between pairs of genres and pairs of labels is smaller than that observed in the original network.
-We then create a binary link between two genres and two labels (indicating perceived similarity) if this percentage falls below a certain threshold.
+From the predicted probabilities derived from this model (where the unit of analysis is the genre/label pair), we create an ensemble of two-mode networks, generate genre-to-genre and label-to-label projections for each, and compute the proportion of times that the projected edge weight between pairs of genres and pairs of labels is smaller in the generated projection ensemble than that observed in the original network projection.
+We then assign a binary link between two genres and two labels in the corresponding backbone (indicating perceived similarity) if this percentage falls below a certain threshold.
 In these data, the usual $p < 0.05$ criterion proves to be too strong (generating mostly empty backbones) for each genre-to-genre and label-to-label projection.
@@
 
-For instance, Figure~\ref{fig:ind-ex-aff} shows the cognitive two-mode network matrices of the associations between genres and social labels for two individuals in the data.
-It is clear from this example that the averaged associations shown in Figure~\ref{fig:main} hide quite a lof of individual variation and idiosyncratic perceptions.
+Figure~\ref{fig:ind-ex-aff} shows the cognitive two-mode network matrices of the associations between genres and social labels for two individuals in the data.
+It is clear from this example that the averaged associations shown in Figure~\ref{fig:main} hide quite a lot of individual variation and idiosyncratic perceptions.
+For instance, Case ID 65 believes that Heavy Metal encompasses most types of people, regardless of gender and race (excluding Asians), but thinks that Jazz music only appeals to older white or Hispanic people with a college degree.
+Case ID 236, on the other hand, thinks that Metal fans are mostly young white men without a college degree, but the classical appeals to most people regardless of gender, race, and age.
 
@@
     \end{subfigure}
-    \caption{Individual genre projection matrices.}
+     \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[trim={1cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/data-ex-rbb1.png}
+            \caption{Case ID: 65}
+            \label{fig:ind-ex-rbb1}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[trim={1cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/data-ex-rbb2.png}
+            \caption{Case ID: 236}
+            \label{fig:ind-ex-rbb2}
+    \end{subfigure}
+    \caption{Individual genre backbones.}
+    \caption{Individual genre projection matrices and corresponding backbones.}
     \label{fig:ind-ex-rp}
 \end{figure}
+
+Figure~\ref{fig:ind-ex-rp} shows the individual row projections ($\mathbf{G}(p)$) and corresponding backbones for each of these two cases, encoding the perceived similarities between genres and social labels for each individual.
+We can see, for instance, that in accordance with their cognitive two-mode network, which sees the Metal audience as relatively undifferentiated, Case ID 65 does not strongly associate Metal with any other genre, except contemporary rock.
+In the same way, Case ID 236 sees Classical and Opera as strongly linked, and Metal as most similar to such genres as Reggae, Rap, Alt Rock, and Contemporary Rock.
+The corresponding column projections ($\mathbf{L}(p)$) and backbones for these two cases are shown in Figure~\ref{fig:ind-ex-cp}.
+Both individuals associate white people with a college degree; Case ID 65 sees the label ``Working Class'' as most similar to ``Black'' and ``Young,'' but Case ID 263 sees the same label as most similar to ``Hispanic," ``Asian,'' and people without a college education.
 
@@
     \end{subfigure}
-    \caption{Individual label projection matrices.}
-    \label{fig:ind-ex-cp}
-\end{figure}
-
-Figures~\ref{fig:ind-ex-rp} and~\ref{fig:ind-ex-cp} show the corresponding row ($\mathbf{G}(p)$) and column ($\mathbf{L}(p)$) projections for the same two individuals, while Figures~\ref{fig:ind-ex-rbb} and~\ref{fig:ind-ex-cbb} show the respective backbones of each projection for the same cases.
-As we can see the procedure extract distinct sets of significant associations between genres and labels for this two cases.
-
-\begin{figure}[ht!]
-    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
-    \centering
-     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[trim={1cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/data-ex-rbb1.png}
-            \caption{Case ID: 65}
-            \label{fig:ind-ex-rbb1}
-    \end{subfigure}
-     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[trim={1cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/data-ex-rbb2.png}
-            \caption{Case ID: 236}
-            \label{fig:ind-ex-rbb2}
-    \end{subfigure}
-    \caption{Individual genre backbones.}
-    \label{fig:ind-ex-rbb}
-\end{figure}
-
-This analytical framework generates three sets of scores: person-specific judgments of the relative similarity of genres and labels (row scores), aggregate judgments of genre and label similarity (column scores), and supplementary scores for genres and labels representing the centroid of the cloud of person-specific judgments.
-Ultimately, this allows me to examine heterogeneity in folk understandings by observing how multiple clouds of individuals (projected into both genre and social label spaces) distribute themselves along principal axes, providing critical insights into the variation in meaning consensus across different levels of analysis.
-
-\begin{figure}[ht!]
-    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
-    \centering
      \begin{subfigure}[b]{0.49\textwidth}
@@
     \end{subfigure}
-    \caption{Individual label backbones.}
-    \label{fig:ind-ex-cbb}
+    \caption{Individual label projection matrices and corresponding backbones.}
+    \label{fig:ind-ex-cp}
 \end{figure}
@@
 \section*{Workflow Illustration}
+Once we have computed the genre and label projection backbones for each individual in the survey, we stack these matrices, generating two tables of dimensions $(N \times 20) \times 20$ (for genres) and $(N \times 15) \times 20$ (for labels).
+We applied the subject of each of these to Correspondence Analysis (CA) to obtain consensus (column) scores of the similarity between genres and labels, along with individual perceptions of the placement of each genre and label in the same spaces (row scores) \citep{kumbasar1994systematic-213}.
+These scores are then analyzed using Geometric Data Analytic methods \citep{rouanet2000geometric-a44}.
+
+\begin{figure}[ht!]
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+        \includegraphics[trim={1cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{mondo-workflow.png}
+    \caption{Individual label projection matrices and corresponding backbones.}
+    \label{fig:ind-ex-cp}
+\end{figure}
+
+This analytical framework thus generates three sets of scores: person-specific judgments of the relative similarity of genres and labels (row scores), aggregate judgments of genre and label similarity (column scores), and supplementary scores for genres and labels representing the centroid of the cloud of person-specific judgments.
+Ultimately, this allows me to examine heterogeneity in folk understandings by observing how multiple clouds of individuals (projected into both genre and social label spaces) distribute themselves along principal axes, providing critical insights into the variation in meaning consensus across different levels of analysis.
+The resulting data workflow is shown in Figure
 

### 2025-06-21 Functions/sdsm.back.R
do it

@@ -1,0 +1,22 @@
+sdsm.back <- function(A, n = 100, p.val = 0.25, seed = 123) {
+   set.seed(seed)
+   r <- nrow(A)
+   c <- ncol(A)
+   P <- A %*% t(A) #row projection
+   G <- t(A) %*% A #column projection
+   y <- as.numeric(A) #vectorized affiliation matrix
+   d1 <- c(rep(rowSums(A), ncol(A))) #person degree vector
+   d2 <- c(rep(colSums(A), each = nrow(A))) #group degree vector
+   dat <- data.frame(y, d1, d2) #data frame
+   res <- glm(y ~ d1*d2, data = dat, family = "binomial")
+   pred <- predict(res, type = "response")
+   gen.aff <- function(w) {
+      return(matrix(as.numeric(w > runif(length(w))), nrow = r, ncol = c))    
+   }
+   B <- replicate(n, gen.aff(pred), simplify = FALSE)
+   P.bin <- lapply(B, function(x) {(P > x %*% t(x)) * 1})
+   G.bin <- lapply(B, function(x) {(G > t(x) %*% x) * 1})
+   P.back <- ((1 - Reduce("+", P.bin)/n) < p.val) * 1
+   G.back <- ((1 - Reduce("+", G.bin)/n) < p.val) * 1
+   return(list(P.back = P.back, G.back = G.back))
+}

### 2025-06-21 Old/analysis-bb-old.qmd
reorg

--- 2025-05-09 analysis-bb.qmd
@@
    conflicts_prefer(dplyr::select)
-   source(here("make.fuzz.plot.R"))
+   source(here("Functions", "make.fuzz.plot.R"))
+   source(here("Functions", "make.demog.plot.R"))
+   source(here("Functions", "demog.dat.R"))
+   source(here("Functions", "sdsm.back.R"))
 ```
@@
    na.omit() #removing missing values
+      r <- c("Classical", "Opera", "Jazz", "Broadway", "Easy", "Big_Band", "Classic_Rock", "Country", "Bluegrass", "Folk", "Gospel", "Latin", "Rap", "Blues", "Reggae", "Pop", "Contemp_Rock", "Alt_Rock", "Dance", "Metal")
+       c <- c("Female", "Male", "White", "Black", "Hispanic", "Asian", "College", "No_College", "Young", "Mid_Age", "Old", "Lower_Class", "Working_Class", "Middle_Class", "Upper_Class")
+```
+
+```{r Summary Table of Averaged Perceptions}
+   tab <- colSums(dat[,2:301])/nrow(dat)
+   tab <- matrix(tab, nrow = 20,  byrow = TRUE)
+   colnames(tab) <- c
+   rownames(tab) <- r
+   png(file = here("Plots", "main.png"), width=1000, height=700)
+   corrplot(tab, is.corr = FALSE, method = "color", 
+      tl.col = "black", tl.cex = 1, tl.srt = 45,
+      addCoef.col = "black", cl.pos = "n", col.lim = c(0, max(tab)),
+      number.cex = 1, number.digits = 2, addgrid.col = "darkgray",
+      col=colorRampPalette(c("lightblue","orange","red"))(200))
+   dev.off()
 ```
@@
    names(ind.mat) <- dat$id_char[-c(bad.den)]
-   ind.row <- lapply(ind.mat, row.breiger) # individual genre projection
-   ind.col <- lapply(ind.mat, col.breiger) # individual label projection
-   row.bb <- lapply(ind.row, bb)
-   col.bb <- lapply(ind.col, bb)
+   ind.mat.t <- lapply(ind.mat, function(x) {t(x)})
+   ind.row <- lapply(ind.mat, function(x) {x %*% t(x)}) # individual genre projection
+   ind.col <- lapply(ind.mat, function(x) {t(x) %*% x}) # individual label projection
+```
+   # row.bb <- lapply(ind.mat, bb.sdsm)
+   # col.bb <- lapply(ind.mat.t, bb.sdsm)
+   # null.rows <- which(as.numeric(unlist(lapply(row.bb, is.null))) == 1)
+   # null.cols <- which(as.numeric(unlist(lapply(col.bb, is.null))) == 1)
+   # row.bb <- row.bb[-null.rows]
+   # col.bb <- col.bb[-null.cols]
+   # row.bb <- lapply(row.bb, function(x) {ifelse(is.nan(x), 1, x)})
+   # col.bb <- lapply(col.bb, function(x) {ifelse(is.nan(x), 1, x)})
+   # row.bb <- lapply(row.bb, function(x) {diag(x) <- 1; x})
+   # col.bb <- lapply(col.bb, function(x) {diag(x) <- 1; x})
+   # save(row.bb, col.bb, file = here("bb.RData"))
+   load(here("bb.RData"))
+   p.val <- 0.45
+   row.bb <- lapply(row.bb, function(x) {(x < p.val) * 1})
+   col.bb <- lapply(col.bb, function(x) {(x < p.val) * 1})
    row.stack <- matrix(unlist(row.bb), ncol = 20, byrow = TRUE) # genre stacked matrix
@@
                      seed = 125, ls = 5,
-                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 4,
-                     c("Alt_Rock", "Contemp_Rock", "Classic_Rock", "Metal"))
+                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 6,
+                     c("Alt_Rock", "Contemp_Rock", "Classic_Rock", "Metal", "Broadway"))
    dev.off()

### 2025-06-21 Slides/heidelberg-slides.qmd
reorg

--- 2025-05-08 heidelberg-slides.qmd
@@
   revealjs:
+    embed-resources: true
     incremental: false 
@@
 
-- Notion of Genre Fundamental to the Sociology of Taste
-- Perennially Contested Category
+- Notion of **genre** fundamental to the Sociology of Taste
+- Key organizing principle
+- Perennially **contested** Category
 - Basic Problem:
@@
   - But our methods mostly rely on **crisp** classifications and **central tendencies**
+  - Calls to either reject or radically revise the notion
 
@@
 
-- Notion of **Genre** Fundamental to the Sociology of Taste
-- Perennially Contested Category
+- Notion of **genre** fundamental to the Sociology of Taste
+- Key organizing principle
+- Perennially **contested** Category
 - Recent work on **Measuring Culture** has begun to make headway on the issue
-  - Relational approaches applying network methods
+  - **Relational** approaches applying network methods
     - Focus on fuzziness and overlapping categories
@@
   - Measuring **Schemas** from Survey and Discourse Data
-- Folk categories are revealed by measuring "what goes with what" at the level of personal culture
-- Focus on *heterogeneity* across clusters of individuals and items
+- Folk categories are revealed by measuring **what goes with what** at the level of personal culture
+- Focus on **heterogeneity** across clusters of individuals and items
 
@@
 ## The sociology of Taste
--  Focused on the dual linkage between two systems of categories:
-  - Genre categories developed in fields of cultural production (scenes, industries)
-  - Social categories endowed with ritual potency and social validity constitutive of status orders 
+-  Focused on the objective **dual linkage** between two systems of categories:
+  - **Genre categories** developed in fields of cultural production (scenes, industries)
+  - **Social categories** endowed with ritual potency and social validity constitutive of status orders 
 - Basic intuition:
@@
   - Categories of persons are defined by the genres they choose
-- Duality!
+- Yet examining **folk construals** of these dual linkages not a common focus
 
@@
 
-## The sociology of Taste
+## Questions
 - We can apply lessons learned from the **relational**, **geometric**, and **schematic** turns in measuring culture to the problem of genre in the sociology of taste
-- Investigate folk schemas regarding the (explicit) associations between genre categories and categories of people
-- Focus on heterogeneity and the distribution of judgments across the social space
+  - From **crisp** definitions to **fuzzy** categories
+  - Focus on **heterogeneity** and the distribution of judgments across the social space
+- We can also move beyond the exclusive focus on objective linkages between genre categories (and cultural objects) and social demographic position 
+  - Investigate folk schemas regarding the **subjective folk construals** of the link between genre categories and categories of people
+  - Need data containing perceived linkages between genre and social **categories**
 
 ## Data
-- Data on cultural tastes among a weighted representative sample of Americans collected in Summer of 2012
+- Data on cultural tastes among a (weighted) representative sample of Americans collected in Summer of 2012
   - $N = 2,250$
@@
   - Persons provide *perceived* associations between **musical genres** and **social labels**
-- Use relational techniques to extract the "backbone" of the perceived associations
+- Use relational techniques to extract the **backbone** of the perceived associations isolating the most important ones:
   - Dual Projection**
-  - Backbone extraction***
+  - Binarizing and via Backbone extraction***
 
@@
   - Geometric Data Analysis of the various **clouds of individuals*****
+  - Regression, clustering and other methods
 
@@
 - Three sets of **scores**:
-  - row-scores are **person-specific** judgments of the relative similarity of genres and labels
-  - column-scores represent the **aggregate judgment** of the relative similarity of genres (with respect to labels) and labels (with respect to genres)
-  - Supplementary scores for genres and labels represent the **centroid** of the cloud of person-specific judgments
+  - **Row scores** are **person-specific** judgments of the relative similarity of genres and labels
+  - **Column scores** represent the **aggregate judgment** of the relative similarity of genres (with respect to labels) and labels (with respect to genres)
+  - **Supplementary scores** for genres and labels represent the **centroid** of the cloud of person-specific judgments
+- We can examine heterogeneity in folk understandings of genre and social categories by looking at how the multiple **cloud of individuals** distribute themselves along the **principal axes**
 
@@
 - Three sets of **scores**:
-  - row-scores are **person-specific** judgments of the relative similarity of genres and labels
-  - column-scores represent the **aggregate judgment** of the relative similarity of genres (with respect to labels) and labels (with respect to genres)
-  - Supplementary scores for genres and labels represent the **centroid** of the cloud of person-specific judgments
-- Multiple **clouds of individuals**
-  - Projected into genre space (one cloud per genre)
-  - Projected into label space (one cloud per label)
+  - **Row scores** are **person-specific** judgments of the relative similarity of genres and labels
+  - **Column scores** represent the **aggregate judgment** of the relative similarity of genres (with respect to labels) and labels (with respect to genres)
+  - **Supplementary scores** for genres and labels represent the **centroid** of the cloud of person-specific judgments
+- Multiple **clouds of individuals**:
+  - Projected into **genre space** (one cloud per genre)
+  - Projected into **social label space **(one cloud per label)
     - Individual specific clouds (across all genres and labels)
@@
 ## Mondo Breiger Approach**
-
 - Each individual provides a "personal" two mode network of genres by social labels with corresponding affiliation matrix $\mathbf{A}(p)$
@@
 
-## Ridge Plot of Genre Clouds
-![Third Dimension](Plots/genre-ridge-dim3.png)
-
 ## Ridge Plot of Label Clouds
@@
 ![Second Dimension](Plots/label-ridge-dim2.png)
-
-## Ridge Plot of Label Clouds
-![Third Dimension](Plots/label-ridge-dim3.png)
 
@@
 ::::
+
+## Group-Specific Genre Clouds
+:::: {.columns}
+::: {.column width="55%"}
+![](Plots/demog-college-educ.png)
+:::
+::: {.column width="45%"}
+![Variance of Age Clouds](Plots/demog-college-educ-var.png)
+:::
+::::
+
+## Group-Specific Genre Clouds
+:::: {.columns}
+::: {.column width="55%"}
+![](Plots/demog-nocollege-educ.png)
+:::
+::: {.column width="45%"}
+![Variance of Age Clouds](Plots/demog-nocollege-educ-var.png)
+:::
+::::
+
+## Discussion and Conclusion
+- Exploiting the sociological duality of **genres** and **social labels** to extract **associational schemas** for both
+
+- Combining **relational** and **geometric** methods to examine central tendencies (*centroids*) and heterogeneity (*variance*) simultaneously
+- Move across multiple **levels**
+  - Individual (typical/atypical)
+  - Category
+  - Group (Demographics)
+  - System
+- Examining variation in **meaning consensus** across levels
+
+## Final Slide
+
+- Thanks!
+
+:::aside
+olizardo@soc.ucla.edu
+:::
+
+## Ridge Plot of Genre Clouds
+![Third Dimension](Plots/genre-ridge-dim3.png)
+
+## Ridge Plot of Label Clouds
+![Third Dimension](Plots/label-ridge-dim3.png)

### 2025-06-21 manuscript.tex

@@
 
-The SDSM works as follows: In the first step, a generalized linear model for binary outcomes is used to predict the probability of a tie between each genre and label in the two-mode network, using the number of times a genre was associated with social label and the number of times a social label was associated with a genre (the degrees of the nodes in each mode) and their interaction as predictors.
-From the predicted probabilities derived from this model (where the unit of analysis is the genre/label pair), we create an ensemble of two-mode networks, generate genre-to-genre and label-to-label projections for each, and compute the proportion of times that the projected edge weight between pairs of genres and pairs of labels is smaller in the generated projection ensemble than that observed in the original network projection.
+The SDSM works as follows: In the first step, a generalized linear model for binary outcomes (binomial family with logit link function) is used to predict the probability of a tie between each genre and label in the two-mode network, using the number of times a genre was associated with social label and the number of times a social label was associated with a genre (the degrees of the nodes in each mode) and their interaction as predictors.
+From the predicted probabilities derived from this model (where the unit of analysis is the genre/label pair), we generate an ensemble of two-mode networks as Bernoulli draws from the vector of predicted probabilities, compute row and column projections for each, and estimate the proportion of times that the projected edge weight between pairs of genres and pairs of labels is smaller in the generated projection ensemble than that observed in the original network projection.
 We then assign a binary link between two genres and two labels in the corresponding backbone (indicating perceived similarity) if this percentage falls below a certain threshold.
-In these data, the usual $p < 0.05$ criterion proves to be too strong (generating mostly empty backbones) for each genre-to-genre and label-to-label projection.
-Accordingly, I use a less stringent criterion of $p < 0.45$.
+In these data, the usual $\alpha < 0.05$ criterion proves to be too strong (generating mostly empty backbones) for each genre-to-genre and label-to-label projection.
+Accordingly, I use a less stringent criterion of $\alpha < 0.45$.
 
-\begin{figure}[ht!]
+\begin{figure}[t]
     \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
@@
 
+\section*{Workflow Illustration}
 Figure~\ref{fig:ind-ex-aff} shows the cognitive two-mode network matrices of the associations between genres and social labels for two individuals in the data.
-It is clear from this example that the averaged associations shown in Figure~\ref{fig:main} hide quite a lot of individual variation and idiosyncratic perceptions.
+It is clear from this example that the averaged associations shown in Figure~\ref{fig:main} hide quite a lot of individual variation and idiosyncratic perceptions of what goes with what \citep{goldberg2018beyond-f2f}.
 For instance, Case ID 65 believes that Heavy Metal encompasses most types of people, regardless of gender and race (excluding Asians), but thinks that Jazz music only appeals to older white or Hispanic people with a college degree.
-Case ID 236, on the other hand, thinks that Metal fans are mostly young white men without a college degree, but the classical appeals to most people regardless of gender, race, and age.
+Case ID 236, on the other hand, suggests that Metal fans are mostly young, white, working-class men.
+However, classical music appeals to most people regardless of gender, race (excluding Asian and Hispanic populations), and age, although these individuals are not typically working-class.
 
-\begin{figure}[ht!]
+\begin{figure}[t]
     \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
@@
 Figure~\ref{fig:ind-ex-rp} shows the individual row projections ($\mathbf{G}(p)$) and corresponding backbones for each of these two cases, encoding the perceived similarities between genres and social labels for each individual.
-We can see, for instance, that in accordance with their cognitive two-mode network, which sees the Metal audience as relatively undifferentiated, Case ID 65 does not strongly associate Metal with any other genre, except contemporary rock.
+We can see, for instance, that in accordance with their cognitive two-mode network, which sees the Metal audience as relatively undifferentiated, Case ID 65 does not strongly associate Metal with any other genre, except contemporary rock and classical (the last a fairly idiosyncratic linkage).
 In the same way, Case ID 236 sees Classical and Opera as strongly linked, and Metal as most similar to such genres as Reggae, Rap, Alt Rock, and Contemporary Rock.
+
 The corresponding column projections ($\mathbf{L}(p)$) and backbones for these two cases are shown in Figure~\ref{fig:ind-ex-cp}.
-Both individuals associate white people with a college degree; Case ID 65 sees the label ``Working Class'' as most similar to ``Black'' and ``Young,'' but Case ID 263 sees the same label as most similar to ``Hispanic," ``Asian,'' and people without a college education.
+As we can see, Case ID 65 identifies the label ``white" as most similar to ``College Educated" and "=``Upper Class," whereas Case ID 236 only associates ``white" with ``Middle Class." Similarly, Case ID 65 sees the label ``Upper Class'' as most similar to ``White,'' ``Female,'' and ``Young,'' but Case ID 263 sees the same label as most similar to ``Old'' and ``Middle Class.''
 
-\begin{figure}[ht!]
+\begin{figure}[t]
     \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
@@
 
-\section*{Workflow Illustration}
 Once we have computed the genre and label projection backbones for each individual in the survey, we stack these matrices, generating two tables of dimensions $(N \times 20) \times 20$ (for genres) and $(N \times 15) \times 20$ (for labels).
-We applied the subject of each of these to Correspondence Analysis (CA) to obtain consensus (column) scores of the similarity between genres and labels, along with individual perceptions of the placement of each genre and label in the same spaces (row scores) \citep{kumbasar1994systematic-213}.
-These scores are then analyzed using Geometric Data Analytic methods \citep{rouanet2000geometric-a44}.
+We then compute the spectral decomposition of these two matrices using Correspondence Analysis (CA).
+This analytical framework thus generates three sets of scores: person-specific judgments of the relative similarity of genres and labels (row scores), aggregate or consensus judgments across all individuals of genre and label similarity (column scores), and supplementary scores for genres and labels representing the centroid of the cloud of person-specific judgments \citep{kumbasar1994systematic-213}.
+These scores are then analyzed using Geometric Data Analysis (GDA) methods \citep{rouanet2000geometric-a44}.
+Ultimately, this approach allows me to examine heterogeneity in folk understandings by observing how multiple clouds of individuals (projected into both genre and social label spaces) distribute themselves along principal axes, providing critical insights into the variation in meaning consensus across different levels of analysis.
+The resulting data workflow is shown in Figure~\ref{fig:workflow}.
 
-\begin{figure}[ht!]
+\begin{figure}[t]
     \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
     \centering
-        \includegraphics[trim={1cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{mondo-workflow.png}
-    \caption{Individual label projection matrices and corresponding backbones.}
-    \label{fig:ind-ex-cp}
+        \includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=1.0\textwidth]{Plots/mondo-workflow.png}
+    \caption{Workflow from dual projection, backbone extraction, to geometric data analysis.}
+    \label{fig:workflow}
 \end{figure}
 
-This analytical framework thus generates three sets of scores: person-specific judgments of the relative similarity of genres and labels (row scores), aggregate judgments of genre and label similarity (column scores), and supplementary scores for genres and labels representing the centroid of the cloud of person-specific judgments.
-Ultimately, this allows me to examine heterogeneity in folk understandings by observing how multiple clouds of individuals (projected into both genre and social label spaces) distribute themselves along principal axes, providing critical insights into the variation in meaning consensus across different levels of analysis.
-The resulting data workflow is shown in Figure
+\section*{Results}
+\subsection*{Consensus Scores Biplots}
+We begin by examining CA biplots of the consensus (column) scores for both genres and labels.
+Figure~\ref{fig:ca-genre-biplot12} shows the correspondence plot for genres along the first two dimensions, with the color intensity of the genre label proportional to their contribution to the first two dimensions.
+We can see that the CA results split the twenty genres into three well-separated groups.
 
-\section*{Results}
+\begin{figure}[t]
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+        \includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=0.6\textwidth]{Plots/ca-genre-col12.png}
+    \caption{Correspondence plot of consensus column scores for genres (dimensions one and two).}
+    \label{fig:ca-genre-biplot12}
+\end{figure}
+
+Along the first (horizontal) dimension, the more traditional ``highbrow'' (artistically consecrated) genres (Classical, Opera) on the right are contrasted to such genres as Metal, Rap, and Reggae on the left.
+On the second (vertical) axis, these genres are contrasted with genres such as Gospel, Folk, and Bluegrass (at the bottom), which are more traditionally associated with rural or religiously observant America.
+
+\begin{figure}[t]
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+        \includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=0.6\textwidth]{Plots/ca-genre-col13.png}
+    \caption{Correspondence plot of consensus column scores for genres (dimensions one and three).}
+    \label{fig:ca-genre-biplot13}
+\end{figure}
+
+Figure~\ref{fig:ca-genre-biplot13} shows the same biplot as Figure~\ref{fig:ca-genre-biplot12} but with the third dimension scores on the vertical axis.
+We can see that the third dimension primarily separates the cluster of ``popular culture'' genres by the perceived race of the audience, with those popular genres which are see as preferred by Black or Hispanic people (Rap, Reagge, Latin, Blues, and Gospel) toward the top, and those whose audiences are seen as overwhelmingly white toward the bottom (Metal and various flavors of Rock).
+
+\begin{figure}[t]
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+        \includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=0.6\textwidth]{Plots/ca-label-col12.png}
+    \caption{Correspondence plot of consensus column scores for social labels (dimensions one and two).}
+    \label{fig:ca-label-biplot12}
+\end{figure}
+
+Figure~\ref{fig:ca-label-biplot12} shows the corresponding consensus biplot for social labels for the first two dimensions.
+We can see that the main action happens along the first (horizontal) axis, which separates labels according to Race, Age, and Class, with working and lower class, young, Black, Hispanic, and No College on the left, and Middle Age, Old, Upper and Middle Class, and College Educated on the right.
+Gender Labels are toward the plot's origin (indicating no strong association with either dimension).
+The second dimension is just a residual axis, separating the seldom-used label of ``Asian'' from the rest.
+
+\begin{figure}[t]
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+        \includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=0.6\textwidth]{Plots/ca-label-col13.png}
+    \caption{Correspondence plot of consensus column scores for social labels (dimensions one and three).}
+    \label{fig:ca-label-biplot13}
+\end{figure}
+
+Figure~\ref{fig:ca-label-biplot13} shows the same biplot as Figure~\ref{fig:ca-label-biplot12} but with the third dimension scores on the vertical axis.
+We can see that the third dimension separates the gender labels (which are perceived by people to be similar to the racial labels of ``white" and ``middle-aged") from the rest, positioning them at the bottom of the plot.
+\subsection*{Fuzzy Biplots for Genres}
+While the consensus scores provide insightful information of the way that persons classify genres and labels \textit{on average}, as we noted at the outset, this hides as much as it reveals.
+For each of the genres and labels shown in the previous figure is actually a \textit{distribution} (a ``cloud'' of points in GDA parlance) of the audiences pertaining to each genre.
+The patterning of this distribution can be seen by plotting the clouds instead of the single consensus score in a CA biplot.
+
+\begin{figure}[t]
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+     \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/genre-proto-ex1.png}
+            \caption{}
+            \label{fig:}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/genre-proto-ex2.png}
+            \caption{}
+            \label{fig:}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/genre-proto-ex4.png}
+            \caption{}
+            \label{fig:}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/genre-proto-ex7.png}
+            \caption{}
+            \label{fig:}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/genre-proto-ex5.png}
+            \caption{}
+            \label{fig:}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/genre-proto-ex7.png}
+            \caption{}
+            \label{fig:}
+    \end{subfigure}
+    \caption{.}
+    \label{fig:}
+\end{figure}
+
+\subsection*{Fuzzy Biplots for Labels}
 

### 2025-06-21 manuscript.tex

@@
 For each of the genres and labels shown in the previous figure is actually a \textit{distribution} (a ``cloud'' of points in GDA parlance) of the audiences pertaining to each genre.
-The patterning of this distribution can be seen by plotting the clouds instead of the single consensus score in a CA biplot.
+The patterning of this distribution can be seen by plotting the \textit{clouds} instead of the single consensus score in a CA biplot.
 
@@
             \caption{}
-            \label{fig:}
+            \label{fig:genre-fuzz-a}
     \end{subfigure}
@@
             \caption{}
-            \label{fig:}
+            \label{fig:genre-fuzz-b}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/genre-proto-ex3.png}
+            \caption{}
+            \label{fig:genre-fuzz-c}
     \end{subfigure}
@@
             \caption{}
-            \label{fig:}
+            \label{fig:genre-fuzz-d}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/genre-proto-ex5.png}
+            \caption{}
+            \label{fig:genre-fuzz-e}
     \end{subfigure}
@@
             \caption{}
-            \label{fig:}
+            \label{fig:genre-fuzz-f}
+    \end{subfigure}
+    \caption{Fuzzy biplots of musical genres.}
+    \label{fig:genre-fuzz}
+\end{figure}
+
+Figure~\ref{fig:genre-fuzz} shows a series of such fuzzy biplots for selected genres.
+Each figure presents a two-dimensional density plot, with each cloud of points marked by a different color, and with darker shading corresponding to the densest regions of the plot for each cloud.
+As we can see in Figures~\ref{fig:genre-fuzz-a}-\ref{fig:genre-fuzz-c}, genres belonging to the three main clusters distributions in Figure~\ref{fig:ca-genre-biplot12} show up as fuzzy clouds of points that, while partially overlapping, exhibit strong separation.
+Meanwhile, as shown in Figures~\ref{fig:genre-fuzz-d}-\ref{fig:genre-fuzz-f}, when we plot clouds of points corresponding to genres in the same general cluster (like Rap, Reggae and blues, or Classic Rock, Country, and Folk, or Classical, Opera, and Broadway Musicals), we end up with strongly overlapping clouds.
+Some genres, such as Jazz in Figures~\ref{fig:genre-fuzz-d} and~\ref{fig:genre-fuzz-e}, occupy bridging positions, nearer the center of the plot and overlapping with otherwise distinct clusters of genres.
+This position of Jazz in the popular imagination corresponds to the historical trajectory of the genre in the field of production in the United States, which combined folk, popular, and classical music practices \citep{lopes1999diffusion-1fa}.
+\subsection*{Fuzzy Biplots for Labels}
+
+\begin{figure}[t]
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+     \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/label-proto-ex1.png}
+            \caption{}
+            \label{fig:label-fuzz-a}
     \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/genre-proto-ex5.png}
+        \includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/label-proto-ex2.png}
             \caption{}
-            \label{fig:}
+            \label{fig:label-fuzz-b}
     \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/genre-proto-ex7.png}
+        \includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/label-proto-ex3.png}
             \caption{}
-            \label{fig:}
+            \label{fig:label-fuzz-c}
     \end{subfigure}
-    \caption{.}
-    \label{fig:}
+     \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{Plots/label-proto-ex4.png}
+            \caption{}
+            \label{fig:label-fuzz-d}
+    \end{subfigure}
+    \caption{Fuzzy biplots of selected social labels.}
+    \label{fig:label-fuzz}
 \end{figure}
-
-\subsection*{Fuzzy Biplots for Labels}
 
